### 2020-01-27 exp.tex
Starting .tex and MCS
little back up before merging

\documentclass{article}
\usepackage[utf8]{inputenc}
\usepackage{amsmath} % Advanced math typesetting
\usepackage[utf8]{inputenc} % Unicode support (Umlauts etc.)
\usepackage[ngerman]{babel} % Change hyphenation rules
\usepackage{hyperref} % Add a link to your document
\usepackage{graphicx} % Add pictures to your document
\usepackage{listings} % Source code formatting and highlighting
\usepackage{bookmark}
\usepackage{natbib}

\usepackage{multicol}
\usepackage{fancyhdr}

\pagestyle{fancy}
\fancyhf{}
\fancyhead[LE,RO]{Overleaf}
\fancyhead[RE,LO]{Guides and tutorials}
\fancyfoot[CE,CO]{\leftmark}
\fancyfoot[LE,RO]{\thepage}

\title{Imm algorithm implementation for tracking}
\author{
Paiola Lorenzo 000000

Zanolli Erik 198852}
\date{January 2020}

\begin{document}

\maketitle

\section*{Introduction}
\begin{flushleft}
The porpouse of this document is the analysis and performance evaluation of an IMM algorithm's implementation in
a sensor grid tracking an object. The object can move with two different model, random walk and unicycle, governed by
 a Markov chain. The goal is evaluate the best trade-off between error on estimated position and real position and number of 
 messagesses involved in tracking
\end{flushleft}

\begin{multicols}{2}
    \section*{Backgound}
    \begin{flushleft}
        Tracking a object with a changing dynamic require propers algorithms and filters. Retriving physical data with
        observations it's not enough, models achiving the best-fit to our data is needed in order to make a prediction and estimate 
        with reduced uncertainty. Here comes to play a major role the IMM algorithm (Interacting Multiple Models): The data
        from sensor are combined with different dynamical models through the algorithm... 
        \subsection*{Kalman Filter and IMM explained}
        \subsection*{m}
    \end{flushleft}
    \section*{Simulation model implementation}
    Introduction
    \subsection*{Filter}
    \subsection*{Sensor}

    \section*{Result}
    Introduction
    \subsection*{}
\end{multicols}
\end{document}

### 2020-01-27 Functions/IMM.m

@@ -52,11 +52,11 @@ for i=1:alto
         [xpred(:,i),Ppred(:,:,i),dz(:,i),S(:,:,i)]=kalman(Mat,xmix(:,i),u,z,Pmix(:,:,i),Q,R,caso,offset,delta,i);
     end
     %% to avoid error => threshold 
-%     if det(S(:,:,i))< 1e-4
-%        L(i)=0.01;
-%     else   
+    if det(S(:,:,i))< 1e-3
+       L(i)=0.01;
+    else   
        L(i)=mvnpdf(dz(:,i),0,S(:,:,i));
-%     end
+    end
     
 end
 

### 2020-01-27 Progetto.m

@@ -1,68 +1,124 @@
 clc; clear all; close all;
 %% Dati
-
-
+rmsposall=zeros(100,1500);
+for ss=1:100
 %switch for the type of movement
 %1-> markov chain constant speed or costant acceleration
 %2-> unicycle
 
-caso=1;
+caso=2;
 %delta time
-delta=0.1;
+delta=0.5;
+%at which rate do we do the consensus ?
+rate=1;
+
+nstop=1500;
 
 %Cell matrix of various B for the input
 switch caso
+    
     case 1
-    A=[1 0 delta 0;
-       0 1 0 delta;
-       0 0 1 0;
-       0 0 0 1];    
-    G=[delta^2/2 0 delta 0;0 delta^2/2 0 delta]';       %noise matrix
-
-    ABG={A,[0 0 0 0; 0 0 0 0]',G;A,[0 0 0 0;0 delta^2/2 0 delta]',G;A,[delta^2/2 0 delta 0; 0 0 0 0]',G;A,[0 0 0 0;0 -delta^2/2 0 -delta]',G;A,[-delta^2/2 0 -delta 0; 0 0 0 0]',G};
-    
-    %number of markov states
-    ns=length(ABG);
-    %length of state vector
-    nx=size(A,1);
-    
-    %Transition Matrix of markov chain
-    p1=0.7;     %probability of constant speed while being in constant speed
-    q1=0.4;     %probability of still accelerating forward while accelerating forward
-    backcost=0.2;
-    p=(1-p1)/4;
-    q=(1-q1-backcost)/5;
-    v1=[p1 p p p p];
-    v2=[q1 2*q q 2*q];
-
-    %the matrix is "circulant" from so we can build it
-    %algorithmically
-    Transmat=zeros(ns);
-    Transmat(1,:)=v1;
-    Transmat(2:end,1)=ones(4,1).*backcost;
-    for i=2:ns
-        Transmat(i,2:end)=[v2(end+3-i:end),v2(1:end+2-i)];
-    end
-    
-    %initial 2D position, velocity and acceleration
-    x0=zeros(nx,1);
-    x0([1,2,4])=0.5;
-    
-    %Power spectra density of process noise
-    Q=diag([0.2,0.2]);  
-    %magnitude of acceleration
-    acc=[1;1].*1;
-    
+        %
+        %
+        %markov chain random walk with 5 states
+        %Linear Model
+        %
+        %
+        
+        
[…]

### 2020-01-27 Functions/IMM.m
Somenthing wrong with idle state
sensors don't turn to idle state or off properly

@@ -52,11 +52,14 @@ for i=1:alto
         [xpred(:,i),Ppred(:,:,i),dz(:,i),S(:,:,i)]=kalman(Mat,xmix(:,i),u,z,Pmix(:,:,i),Q,R,caso,offset,delta,i);
     end
     %% to avoid error => threshold 
-%     if det(S(:,:,i))< 1e-4
+%     if det(S(:,:,i))< 1e-3
 %        L(i)=0.01;
 %     else   
-       L(i)=mvnpdf(dz(:,i),0,S(:,:,i));
-%     end
+    if  any(eig(S(:,:,i))<0.1)
+        L(i)=0.01;
+    else
+        L(i)=mvnpdf(dz(:,i),0,S(:,:,i));
+    end
     
 end
 

### 2020-01-27 Plot_sensors.m

@@ -1,0 +1,10 @@
+%% plot the Sensor
+for i=1:n-2 
+for u=1:size(Pos_sens_on,2)
+        if size(Pos_sens_on{i+1,u}) == [0,0];
+            Pos_sens_on{i+1,u} = Pos_sens_on{i,u};
+            Pos_sens_grid{i+1,u} =Pos_sens_grid{i+1,u};
+        else
+        end
+ end
+end

### 2020-01-27 Progetto.m

@@ -1,68 +1,133 @@
 clc; clear all; close all;
 %% Dati
-
-
+rmsposall=zeros(100,1500);
+for ss=1:100
 %switch for the type of movement
 %1-> markov chain constant speed or costant acceleration
 %2-> unicycle
 
-caso=1;
+caso=2;
 %delta time
-delta=0.1;
+delta=0.5;
+%at which rate do we do the consensus ?
+rate=1;
+
+nstop=1500;
 
 %Cell matrix of various B for the input
 switch caso
+    
     case 1
-    A=[1 0 delta 0;
-       0 1 0 delta;
-       0 0 1 0;
-       0 0 0 1];    
-    G=[delta^2/2 0 delta 0;0 delta^2/2 0 delta]';       %noise matrix
-
-    ABG={A,[0 0 0 0; 0 0 0 0]',G;A,[0 0 0 0;0 delta^2/2 0 delta]',G;A,[delta^2/2 0 delta 0; 0 0 0 0]',G;A,[0 0 0 0;0 -delta^2/2 0 -delta]',G;A,[-delta^2/2 0 -delta 0; 0 0 0 0]',G};
-    
-    %number of markov states
-    ns=length(ABG);
-    %length of state vector
-    nx=size(A,1);
-    
-    %Transition Matrix of markov chain
-    p1=0.7;     %probability of constant speed while being in constant speed
-    q1=0.4;     %probability of still accelerating forward while accelerating forward
-    backcost=0.2;
-    p=(1-p1)/4;
-    q=(1-q1-backcost)/5;
-    v1=[p1 p p p p];
-    v2=[q1 2*q q 2*q];
-
-    %the matrix is "circulant" from so we can build it
-    %algorithmically
-    Transmat=zeros(ns);
-    Transmat(1,:)=v1;
-    Transmat(2:end,1)=ones(4,1).*backcost;
-    for i=2:ns
-        Transmat(i,2:end)=[v2(end+3-i:end),v2(1:end+2-i)];
-    end
-    
-    %initial 2D position, velocity and acceleration
-    x0=zeros(nx,1);
-    x0([1,2,4])=0.5;
-    
-    %Power spectra density of process noise
-    Q=diag([0.2,0.2]);  
-    %magnitude of acceleration
-    acc=[1;1].*1;
-    
+        %
+        %
+        %markov chain random walk with 5 states
+        %Linear Model
+        %
+        %
+        
+        
[…]

### 2020-01-27 Progetto2.m

@@ -81,24 +81,33 @@ switch caso
         nx=4;
         
         %Transition Matrix of markov chain
-        p1=0.7;     %probability of constant speed while being in constant speed
-        q1=0.4;     %probability of still accelerating forward while accelerating forward
+        p1=0.8;     %probability of constant speed while being in constant speed
+        q1=0.5;     %probability of still accelerating forward while accelerating forward
         backcost=0.2;
         p=(1-p1)/4;
-        q=(1-q1-backcost)/5;
+        %q=(1-q1-backcost)/5;
+        q=q1/2;
         v1=[p1 p p p p];
-        v2=[q1 2*q q 2*q];
-        
+%         v2=[q1 2*q q 2*q];
+%         
         ns=length(v1);
-        
-        %the matrix is "circulant" from so we can build it
-        %algorithmically
+%         
+%         %the matrix is "circulant" from so we can build it
+%         %algorithmically
+%         Transmat=zeros(ns);
+%         Transmat(1,:)=v1;
+%         Transmat(2:end,1)=ones(4,1).*backcost;
+%         for i=2:ns
+%             Transmat(i,2:end)=[v2(end+3-i:end),v2(1:end+2-i)];
+%         end
+
+        % Hardcoded
         Transmat=zeros(ns);
         Transmat(1,:)=v1;
-        Transmat(2:end,1)=ones(4,1).*backcost;
-        for i=2:ns
-            Transmat(i,2:end)=[v2(end+3-i:end),v2(1:end+2-i)];
-        end
+        Transmat(2,:)=[q q1 q 0 0]; 
+        Transmat(3,:)=[q q q1 0 0]; 
+        Transmat(4,:)=[q 0 0 q1 q]; 
+        Transmat(5,:)=[q 0 0 q q1];
         %initial 2D position, velocity and acceleration
         x0=zeros(nx,1);
         x0([1,2])=0.5;
@@ -381,9 +390,10 @@ while (~(isempty(onindices))&&n<nstop)
 
[…]

### 2020-01-27 Sensor.m

@@ -13,7 +13,8 @@ classdef Sensor<handle
        neighboors {}            %cell array with indices of listeners/sources
        activevertex{}           %active graph indices
        
-       change {}                
+       change {} 
+       color {}                 % for plot
        %token that should be -1 if a neighboor has gone from ON to IDLE,
        % 1 if it has gone from IDLE to ON, 0 in any other case
        
@@ -73,7 +74,15 @@ classdef Sensor<handle
                 obj.sensed=[sqrt(vector*vector');actualangle]+randn(2,1).*arrayfun(@(a)sqrt(a),diag(obj.R));
             end
         end
-        
+        function obj=plotsensor(obj)
+            if obj.state=="on"
+                plot(obj.position(1),obj.position(2),'*g');
+            elseif obj.state=="idle"
+                plot(obj.position(1),obj.position(2),'*y');
+            elseif obj.state=="off"
+                plot(obj.position(1),obj.position(2),'*r');
+            end
+        end
         function obj=checkchange(obj)
             %checks events nearby
             if obj.change==1

### 2020-01-27 Functions/IMM.m
On skype

@@ -55,8 +55,8 @@ for i=1:alto
 %     if det(S(:,:,i))< 1e-3
 %        L(i)=0.01;
 %     else   
-    if  any(eig(S(:,:,i))<0.1)
-        L(i)=0.01;
+    if  any(eig(S(:,:,i))<0.01)
+        L(i)=0.001;
     else
         L(i)=mvnpdf(dz(:,i),0,S(:,:,i));
     end

### 2020-01-27 Functions/tellyourfriends.m

@@ -10,6 +10,7 @@ if message=="Can"
     n=length(amici);
     for k=1:n
         gigi=amici{k};
+        grid{gigi(1),gigi(2)}.activevertex=sensor.activevertex;
         grid{gigi(1),gigi(2)}.change=1;
         grid{gigi(1),gigi(2)}.checkchange;
     end
@@ -18,6 +19,7 @@ elseif message=="Cannot"
     n=length(amici);
     for k=1:n
         gigi=amici{k};
+        grid{gigi(1),gigi(2)}.activevertex=sensor.activevertex;
         grid{gigi(1),gigi(2)}.change=-1;
         grid{gigi(1),gigi(2)}.checkchange;
     end

### 2020-01-27 Progetto2.m

@@ -8,9 +8,10 @@ clc; clear all; close all;
 
 caso=2;
 %delta time
-delta=0.5;
+delta=0.4;
 %at which rate do we do the consensus ?
-rate=5;
+rate=3;
+
 
 nstop=1500;
 
@@ -262,7 +263,6 @@ ygrid=xgrid;
 %     plot(xgrid,ones(1,nq+1).*ygrid(i),'*r')
 % end
 
-
 while (~(isempty(onindices))&&n<nstop)
     x=move(stato(:,n),acc,mode(n),Q,caso,delta,ABG);
     mode(n+1)=markchange(s,Transmat);
@@ -363,6 +363,8 @@ while (~(isempty(onindices))&&n<nstop)
             sensors{kk,ll}.xcons=statocons(:,ncons+1);
             sensors{kk,ll}.Pcons=Pcons(:,:,ncons+1);
             sensors{kk,ll}.mu=mucons(:,ncons+1);
+            %pick xcons of all on sensors
+            %
         end
         
         for i=1:ns
@@ -387,13 +389,11 @@ while (~(isempty(onindices))&&n<nstop)
             sensors{kk,ll}.xconskalm=sensors{kk,ll}.xpred;
             sensors{kk,ll}.Pconskalm=sensors{kk,ll}.Ppred;
             sensors{kk,ll}.mu=sensors{kk,ll}.mu';
-
-            Pos_sens_on{n,i}=sensors{kk,ll}.position;
-            Pos_sens_grid{n,i}=sensors{kk,ll}.ingrid;
-           
+            % %pick xcons of all on sensors
+            %
         end
     end
-     Idle_range_n{n}=idlerange;
+    
     if rem(n+1,rate)==0
         [ell_x,ell_y] =plotellipse(Pcons(1:2,1:2,ncons),statocons(1:2,ncons),0);
         ellx(:,ncons)=ell_x(:);
@@ -403,6 +403,7 @@ while (~(isempty(onindices))&&n<nstop)
     for q=1:size(onindices,2)
         saveon{n,q}=onindices{q};
     end
+    
     
     xsens=[];
     Psens=[];
@@ -530,12 +531,11 @@ for i=0:n-3
 %         end
 %     end
 %     fourth
-for lt1=1:size(sensors,1)
-    for lt2=1:size(sensors,2)
-        if sensors.
[…]

### 2020-01-27 Progetto2.m
post skype

@@ -256,12 +256,18 @@ Pksens=cell(1,lon);
 
 xgrid=-range*nq/2:range:range*nq/2;
 ygrid=xgrid;
+curve1 = animatedline('Color','r');
+curve2= animatedline;
 
-% hold on
-% figure(1)
-% for i=1:nq+1
-%     plot(xgrid,ones(1,nq+1).*ygrid(i),'*r')
-% end
+curve3= animatedline('Color','b');
+curve4= animatedline('Marker','*','Color','g');
+hold on
+hhh=figure(1)
+% axis tight manual
+filename = 'testAnimated.gif';
+for i=1:nq+1
+    plot(xgrid,ones(1,nq+1).*ygrid(i),'*r')
+end
 
 while (~(isempty(onindices))&&n<nstop)
     x=move(stato(:,n),acc,mode(n),Q,caso,delta,ABG);
@@ -273,7 +279,9 @@ while (~(isempty(onindices))&&n<nstop)
         for j=idlerange(2,1):idlerange(2,2)
             sensors{i,j}.inRange(stato(1:2,n+1));
             check=checkvertex(onindices,[i,j]);
+            % sensors{i,j}.plotsensor; % first try here 
             if sensors{i,j}.inrange
+ 
                 %add to onindices if it's in range and not already in the
                 %list
                 if ~any(check,'all')
@@ -318,6 +326,7 @@ while (~(isempty(onindices))&&n<nstop)
     for i=idlerange(1,1):idlerange(1,2)
         for j=idlerange(2,1):idlerange(2,2)
             sensors{i,j}.activevertex=onindices;
+            sensors{i,j}.plotsensor;
         end
     end
     
@@ -389,15 +398,17 @@ while (~(isempty(onindices))&&n<nstop)
             sensors{kk,ll}.xconskalm=sensors{kk,ll}.xpred;
             sensors{kk,ll}.Pconskalm=sensors{kk,ll}.Ppred;
             sensors{kk,ll}.mu=sensors{kk,ll}.mu';
+           
             % %pick xcons of all on sensors
             %
         end
     end
     
     if rem(n+1,rate)==0
[…]

### 2020-01-28 Functions/IMM.m
Code cleanup and thinghs
After the talk with fontanelli

@@ -54,8 +54,11 @@ for i=1:alto
     %% to avoid error => threshold 
 %     if det(S(:,:,i))< 1e-3
 %        L(i)=0.01;
-%     else   
-    if  any(eig(S(:,:,i))<0.01)
+%     else
+if min(eig(S(:,:,i))) < 1e-9
+        aaa = 10;
+    end
+    if  any(eig(S(:,:,i))<(2*pi/360)^2/2) % Smallest of diag(R)
         L(i)=0.001;
     else
         L(i)=mvnpdf(dz(:,i),0,S(:,:,i));

### 2020-01-28 Functions/WLS.m

@@ -1,7 +1,9 @@
 function [xLS,PLS] = WLS(z,C,H)
 %Weighted least min squared
 PLS=inv(H'/C*H);
-    
+    if rcond(PLS)<=1e-8
+        AAA=10
+    end
 xLS=PLS*H'/C*z;
 end
 

### 2020-01-28 Functions/kalman.m

@@ -18,6 +18,9 @@ function [xk1,Pk1,dz,S] = kalman(Mat,x,u,z,Pk,Q,R,caso,offset,delta,s)
     dz=z-hx(xpri,caso,offset);
     dz=aggiusta(dz);
     S=H*Ppri*H'+R;  %covariance update
+    if min(eig(S)) < 1e-9
+        aaa = 10;
+    end
     W=Ppri*H'/S;    %kalman weight
     %update
     xk1=xpri+W*dz;

### 2020-01-28 Functions/plotellipse.m

@@ -52,7 +52,7 @@ r_ellipse = [ellipse_x_r;ellipse_y_r]' * R;
 
 % Draw the error ellipse
 if onoff ==1
-%plot(r_ellipse(:,1) + X0,r_ellipse(:,2) + Y0,'-')
+    plot(r_ellipse(:,1) + X0,r_ellipse(:,2) + Y0,'-')
 end
 outputArg1 = r_ellipse(:,1) + X0;
 outputArg2 = r_ellipse(:,2) + Y0;

### 2020-01-28 Progetto2.m

@@ -1,20 +1,21 @@
 clc; clear all; close all;
 %% Dati
 
-
 %switch for the type of movement
 %1-> markov chain constant speed or costant acceleration
 %2-> unicycle
 
 caso=2;
 %delta time
-delta=0.4;
+delta=0.5;
 %at which rate do we do the consensus ?
-rate=3;
-
-
-nstop=1500;
-
+rate=5;
+%Maximum number of iteration
+nstop=800;
+%% Plot
+videon = 1;
+ploton =1;
+plotallsenson=1;
 %Cell matrix of various B for the input
 switch caso
     
@@ -92,16 +93,6 @@ switch caso
 %         v2=[q1 2*q q 2*q];
 %         
         ns=length(v1);
-%         
-%         %the matrix is "circulant" from so we can build it
-%         %algorithmically
-%         Transmat=zeros(ns);
-%         Transmat(1,:)=v1;
-%         Transmat(2:end,1)=ones(4,1).*backcost;
-%         for i=2:ns
-%             Transmat(i,2:end)=[v2(end+3-i:end),v2(1:end+2-i)];
-%         end
-
         % Hardcoded
         Transmat=zeros(ns);
         Transmat(1,:)=v1;
@@ -254,19 +245,27 @@ muijsens=[];
 xksens=[];
 Pksens=cell(1,lon);
 
-xgrid=-range*nq/2:range:range*nq/2;
-ygrid=xgrid;
-curve1 = animatedline('Color','r');
-curve2= animatedline;
+% xgrid=-range*nq/2:range:range*nq/2;
+% ygrid=xgrid;
 
-curve3= animatedline('Color','b');
-curve4= animatedline('Marker','*','Color','g');
+curve1 = animatedline('Color','r');
+curve2= animatedline('Color','b');
+curve3= animatedline('Color','y');
+
+curvesens1= animatedline('Color','m');
+curvesens2= animatedline('Color','c');
+curvesens3= animatedline('Color','k');
+curvesens4= animatedline('Color','y');
+
+if ploton ==1    
 hold on
 hhh=figure(1)
-% axis tight manual
-filename = 'testAnimated.gif';
-for i=1:nq+1
-    plot(xgrid,ones(1,nq+1).*ygrid(i),'*r')
+%filename = 'testAnimated.gif';
+for i=1:nq % initializate the plot grid
+    for j=1:nq
[…]

### 2020-01-28 Progetto2.m
Auto stash before merge of "no_speed_jumps" and "origin/no_speed_jumps"

@@ -283,13 +283,11 @@ while (~(isempty(onindices))&&n<nstop)
                 %add to onindices if it's in range and not already in the
                 %list
                 if ~any(check,'all')
-                    
                     sensors{i,j}.activevertex=onindices;
                     sensors{i,j}.initializefromidle(sensors);
                     %the sensors doesn't have anything to compute the IMM,
                     %we initialize them getting everything from their
                     %neighboors that are on
-                    
                     onindices{end+1}=[i,j];
                     sensors{i,j}.activevertex=onindices;
                     %send your neighboors a message that you are now on
@@ -321,8 +319,8 @@ while (~(isempty(onindices))&&n<nstop)
     
     idlerange=[mini,maxi;minj,maxj];
     %give updated onsensors list
-    for i=idlerange(1,1):idlerange(1,2)
-        for j=idlerange(2,1):idlerange(2,2)
+    for i=(idlerange(1,1)-1):(idlerange(1,2)+1)
+        for j=(idlerange(2,1)-1):(idlerange(2,2)+1)
             sensors{i,j}.activevertex=onindices;
         end
     end
@@ -374,7 +372,7 @@ while (~(isempty(onindices))&&n<nstop)
     %Here we have a dynamic (vertexes can go in and out) fully connected
     %graph
     
-    if rem(n,rate)==0 % qui c'era un n+1 perchè ?
+    if rem(n,rate)==0 % qui c'era un n+1 perchï¿½ ?
         [statocons(:,ncons+1),Pcons(:,:,ncons+1)]=WLS(xsens,Psens,Hsens);
         [mucons(:,ncons+1),muijcons(:,:,ncons+1)]=WLS(musens,muijsens,Hmu);
         %check when do we have to do consensus
@@ -424,7 +422,6 @@ while (~(isempty(onindices))&&n<nstop)
     end
     
    
-    
     
     
     xsens=[];

### 2020-01-29 Latex/exp.tex

\documentclass{article}
\usepackage[utf8]{inputenc}
\usepackage{amsmath} % Advanced math typesetting
\usepackage[utf8]{inputenc} % Unicode support (Umlauts etc.)
\usepackage[ngerman]{babel} % Change hyphenation rules
\usepackage{hyperref} % Add a link to your document
\usepackage{graphicx}[final] % Add pictures to your document
\usepackage{listings} % Source code formatting and highlighting
\usepackage{bookmark}
\usepackage{natbib}
\usepackage{geometry}
\usepackage{multicol}
\usepackage{fancyhdr}
\usepackage[document]{ragged2e}

\pagestyle{fancy}
\fancyhf{}
\fancyhead[LE,RO]{Overleaf}
\fancyhead[RE,LO]{Guides and tutorials}
\fancyfoot[CE,CO]{\leftmark}
\fancyfoot[LE,RO]{\thepage}
\graphicspath{{Immagini/}}

\geometry{
 a4paper,
 total={170mm,257mm},
 left=20mm,
 top=20mm,
 }

\title{Imm algorithm implementation for tracking}
\author{
Paiola Lorenzo 000000

Zanolli Erik 198852}
\date{January 2020}

\begin{document}

\maketitle

\section*{Introduction}
\justify
The porpouse of this document is the analysis and performance evaluation of an IMM algorithm's implementation in
a sensor grid tracking an object. The object can move with two different model, random walk and unicycle, governed by
 a Markov chain. The goal is evaluate the best trade-off between error on estimated position and real position and number of 
 messagesses involved in tracking

\begin{multicols}{2}
    \section*{Backgound}
    \justify
        Tracking a object with a changing dynamic require propers algorithms and filters. Retriving physical data with
        observations it's not enough, models achiving the best-fit to our data is needed in order to make a prediction and estimate 
        with reduced uncertainty. Here comes to play a major role the IMM algorithm (Interacting Multiple Models): The data
        from sensor are combined with different dynamical models through the algorithm... 
        \subsection*{Simulation Model}
            The target can move with random movement described by a Markov chain and accordingly two different models of movement
            The tracking are performed with grid of sensors. In order to perform a proper simulation the sensor has assumed to have a limited
            range for the tracking and we cannot retrive any information if target is out. It also took in consideration the power consumption 
            for a possible physical system: to model a more enegy efficient system the sensor can switch to 3 different working condition: On,Off,Idle.
            To achive this goal the sensor is working as a state machine as showned in the figure below:

            Sensors can communicate with the sensors in their neighboorhoods and exchange signal named CanSense and CantSense that regulate the transition
            between differents state.

            {How the sensors works}

            The measurment acquired by eachs sensors are then combined through the theory of linear consensus
            The filter choosed are the WSL

            Sensors in the simulations are Radar and the H matrix that reprent the measurment:

        \subsection*{m}

    \section*{Simulation model implementation}
    Introduction
    \subsection*{Filter}
    \subsection*{Sensor}
    The sensor grid are is composed by a set of sensor that can communicate with each others creating a fully connected graphic
    The single sensor works as a state machine, and change its state accordingly with the signal exchanged with the neighboors.
    \begin{figure}[htp]
        \centering
        \includegraphics[width=2cm, height=2cm]{UntitledDiagram.png}
        \caption{An image of a galaxy}
        \label{fig:galaxy}
    \end{figure}
    \subsection*{Random walk and Unycicle model}
    The target in this simulation can move accordingly to two model: random walk and Unycicle. The genaral expression of the two process it
    \begin{equation}
    X^{+}=\begin{bmatrix} A \\ \end{bmatrix}X(k)+\begin{bmatrix} B \\ \end{bmatrix}u(k) + \begin{bmatrix} G \\ \end{bmatrix}w(k)
    \end{equation}
    State,state and noise matrix associate to the random walk has showned below:
    $$
    X=\begin{bmatrix} x \\ y \\ \dot{x} \\ \dot{y} \\ \end{bmatrix}
    $$

    $$
    A=\begin{bmatrix}
    1&0&\delta&0\\
    0&1&0&\delta\\
    0&0&1&0\\
    0&0&0&1\\
    \end{bmatrix}
    $$

    $$
    G=\begin{bmatrix}
    \delta^2/2&0\\
    0&delta^2/2\\
    \delta&0\\
    0&\delta\\
    \end{bmatrix}
    $$

    $$
    B= \begin{bmatrix}
        \delta^2/2&0\\
        0&delta^2/2\\
        \delta&0\\
        0&\delta\\
    \end{bmatrix}
    $$
   The unycicle model state representation employed has showned below

    \section*{Result}
    The performance evaluation of the system are evaluted by computing the RMS of the predicted trajectory eith the respect to the actual one 
    choosing different rate of performind the WSL. The final result are listed in the table below

\begin{center}
    \begin{tabular}{||c c c c||} 
    \hline
    1 step & 2 step & 3 step & 4 step \\ [0.5ex] 
    \hline\hline
    1 & 6 & 87837 & 787 \\ 
    \hline
    2 & 7 & 78 & 5415 \\
    \hline
    3 & 545 & 778 & 7507 \\
    \hline
    4 & 545 & 18744 & 7560 \\
    \hline
    5 & 88 & 788 & 6344 \\ [1ex] 
    \hline
   \end{tabular}
   \end{center}

    \subsection*{}
\end{multicols}
\end{document}

### 2020-01-29 Functions/Hk.m
Trying to debug

@@ -1,6 +1,5 @@
 function H=Hk(xprior,caso,offset)
-%xprior-> row vector containing the prediction of the state (6 elements
-%[x,y,vx,vy,ax,ay]
+%xprior-> row vector containing the prediction of the state 
 %h(xprior) should be the cartesian transform aka
 %rho=sqrt(x^2+y^2)
 %theta=atan2(y/x)

### 2020-01-29 Functions/IMM.m

@@ -52,13 +52,7 @@ for i=1:alto
         [xpred(:,i),Ppred(:,:,i),dz(:,i),S(:,:,i)]=kalman(Mat,xmix(:,i),u,z,Pmix(:,:,i),Q,R,caso,offset,delta,i);
     end
     %% to avoid error => threshold 
-%     if det(S(:,:,i))< 1e-3
-%        L(i)=0.01;
-%     else
-if min(eig(S(:,:,i))) < 1e-9
-        aaa = 10;
-    end
-    if  any(eig(S(:,:,i))<(2*pi/360)^2/2) % Smallest of diag(R)
+    if  rcond(S(:,:,i)
         L(i)=0.001;
     else
         L(i)=mvnpdf(dz(:,i),0,S(:,:,i));
@@ -76,5 +70,8 @@ xkk=xpred*muk1';
 Pkk=zeros(largo);
 for i=1:alto
     Pkk=Pkk+(Ppred(:,:,i)+(xkk-xpred(:,i))*(xkk-xpred(:,i))')*muk1(i);
+end
+if rcond(Pkk)<0.0001
+    "OMEGALUL"
 end
 end

### 2020-01-29 Functions/WLS.m

@@ -1,9 +1,9 @@
 function [xLS,PLS] = WLS(z,C,H)
 %Weighted least min squared
 PLS=inv(H'/C*H);
-    if rcond(PLS)<=1e-8
-        AAA=10
-    end
+if rcond(PLS)<=1e-8
+    "AAAAA"
+end
 xLS=PLS*H'/C*z;
 end
 

### 2020-01-29 Functions/fx.m

@@ -1,8 +1,8 @@
 function x1 = fx(x,u,delta,s,r)
 A=[1 0 delta*cos(x(4)) 0;
-            0 1 delta*sin(x(4)) 0;
-            0 0 1 0
-            0 0 0 1];
+    0 1 delta*sin(x(4)) 0;
+    0 0 1 0
+    0 0 0 1];
 B={[0 0 0 0;0 0 0 0]',[delta^2/2*cos(x(4))*r delta^2/2*sin(x(4))*r delta*r 0;0 0 0 0]',...
     [-delta^2/2*cos(x(4))*r -delta^2/2*sin(x(4))*r delta*r 0;0 0 0 0]',[0 0 0 0;0 0 0 delta]',[0 0 0 0;0 0 0 -delta]'};
 x1=A*x+B{s}*u;

### 2020-01-29 Functions/kalman.m

@@ -18,11 +18,13 @@ function [xk1,Pk1,dz,S] = kalman(Mat,x,u,z,Pk,Q,R,caso,offset,delta,s)
     dz=z-hx(xpri,caso,offset);
     dz=aggiusta(dz);
     S=H*Ppri*H'+R;  %covariance update
-    if min(eig(S)) < 1e-9
-        aaa = 10;
+    if rcond(S)<0.001
+        "ayayaya"
+    elseif det(S)>100
+        "oyoyoyo"
     end
-    W=Ppri*H'/S;    %kalman weight
+    W=(Ppri*H')/S;    %kalman weight
     %update
     xk1=xpri+W*dz;
-    Pk1=Ppri-W*S*W';
+    Pk1=(eye(length(x))-W*H)*Ppri;
 end

### 2020-01-29 Functions/move.m

@@ -1,5 +1,5 @@
 %% output: x1-> position + speed; s->next markov state;
-%% input:  x-> position + speed + ; a->acceleration magnitude; s-> state of markov chain, Mat->cell array of all B matrices;
+%% input:  x-> position + speed + ; a->acceleration magnitude; s-> state of markov chain, Mat->cell array of all B matrices/radius id case==2;
 %%         T-> transition Matrix 
 
 function x1=move(x,a,s,Q,caso,delta,Mat)

### 2020-01-29 Progetto2.m

@@ -5,18 +5,17 @@ clc; clear all; close all;
 %1-> markov chain constant speed or costant acceleration
 %2-> unicycle
 
-caso=2;
+caso=1;
 %delta time
-delta=0.5;
+delta=0.01;
 %at which rate do we do the consensus ?
-rate=5;
+rate=1;
 %Maximum number of iteration
 nstop=800;
-%% Plot
-videon = 1;
-ploton =1;
-plotallsenson=1;
-%Cell matrix of various B for the input
+%Plot
+videon = 0;
+ploton =0;
+plotallsenson=0;
 switch caso
     
     case 1
@@ -81,24 +80,20 @@ switch caso
         
         %length of state vector
         nx=4;
+        ns=5;
         
         %Transition Matrix of markov chain
-        p1=0.8;     %probability of constant speed while being in constant speed
-        q1=0.5;     %probability of still accelerating forward while accelerating forward
-        backcost=0.2;
+        p1=0.6;     %probability of constant speed while being in constant speed
+        q1=1/3;     %probability of still accelerating forward while accelerating forward
         p=(1-p1)/4;
-        %q=(1-q1-backcost)/5;
-        q=q1/2;
-        v1=[p1 p p p p];
-%         v2=[q1 2*q q 2*q];
-%         
-        ns=length(v1);
+        q=(1-q1)/2;
+        
         % Hardcoded
         Transmat=zeros(ns);
-        Transmat(1,:)=v1;
-        Transmat(2,:)=[q q1 q 0 0]; 
-        Transmat(3,:)=[q q q1 0 0]; 
-        Transmat(4,:)=[q 0 0 q1 q]; 
+        Transmat(1,:)=[p1 p p p p];
+        Transmat(2,:)=[q q1 q 0 0];
+        Transmat(3,:)=[q q q1 0 0];
+        Transmat(4,:)=[q 0 0 q1 q];
         Transmat(5,:)=[q 0 0 q q1];
         %initial 2D position, velocity and acceleration
         x0=zeros(nx,1);
@@ -107,10 +102,10 @@ switch caso
         %radius, called like this for reasons
         ABG=0.3;
         %Power spectra density of process noise
-        Q=diag([0.2,0.2]);
+        Q=diag([0.1,0.1]);
         %magnitude of acceleration
         acc=[2;1].*0.1;
-        P0=diag([0.1,0.1,0.5,0.5]);
[…]

### 2020-01-29 Functions/IMM.m
sbaglio

@@ -52,10 +52,12 @@ for i=1:alto
         [xpred(:,i),Ppred(:,:,i),dz(:,i),S(:,:,i)]=kalman(Mat,xmix(:,i),u,z,Pmix(:,:,i),Q,R,caso,offset,delta,i);
     end
     %% to avoid error => threshold 
-    if  rcond(S(:,:,i)
+    if  rcond(S(:,:,i))<1e-6
         L(i)=0.001;
-    else
+    elseif all(eig(S(:,:,i))>1e-6)
         L(i)=mvnpdf(dz(:,i),0,S(:,:,i));
+    else
+        "HOW"
     end
     
 end

### 2020-01-29 Progetto2.m

@@ -7,11 +7,11 @@ clc; clear all; close all;
 
 caso=1;
 %delta time
-delta=0.01;
+delta=0.05;
 %at which rate do we do the consensus ?
 rate=1;
 %Maximum number of iteration
-nstop=800;
+nstop=2000;
 %Plot
 videon = 0;
 ploton =0;

### 2020-01-29 Functions/IMM.m
Sensed plot
Some

@@ -52,7 +52,7 @@ for i=1:alto
         [xpred(:,i),Ppred(:,:,i),dz(:,i),S(:,:,i)]=kalman(Mat,xmix(:,i),u,z,Pmix(:,:,i),Q,R,caso,offset,delta,i);
     end
     %% to avoid error => threshold 
-    if  rcond(S(:,:,i)
+    if  rcond(S(:,:,i))<=0.00000001
         L(i)=0.001;
     else
         L(i)=mvnpdf(dz(:,i),0,S(:,:,i));

### 2020-01-29 Progetto2.m

@@ -7,15 +7,16 @@ clc; clear all; close all;
 
 caso=1;
 %delta time
-delta=0.01;
+delta=0.9;
 %at which rate do we do the consensus ?
 rate=1;
 %Maximum number of iteration
-nstop=800;
+nstop=400;
 %Plot
 videon = 0;
-ploton =0;
+ploton =1;
 plotallsenson=0;
+plotallsensed=1;
 switch caso
     
     case 1
@@ -245,10 +246,18 @@ curve3= animatedline('Color','y');
 
 curvesens1= animatedline('Color','m');
 curvesens2= animatedline('Color','c');
-curvesens3= animatedline('Color','k');
-curvesens4= animatedline('Color','y');
+curvesens3= animatedline('Color','y');
+curvesens4= animatedline('Color','k');
+
+
+curvesens5= animatedline('Color','m','Marker','*');
+curvesens6= animatedline('Color','c');
+curvesens7= animatedline('Color','y');
+curvesens8= animatedline('Color','k','Marker','*');
+
 
 if ploton ==1
+plotS=cell(nq,nq);
     hold on
     hhh=figure(1)
     filename = 'testAnimated.gif';
@@ -258,7 +267,8 @@ if ploton ==1
         end
     end
 end
-
+xconsallsensor=cell(nstop,4);
+sensed=cell(nstop,4);
 while (~(isempty(onindices))&&n<nstop)
     x=move(stato(:,n),acc,mode(n),Q,caso,delta,ABG);
     mode(n+1)=markchange(s,Transmat);
@@ -337,6 +347,7 @@ while (~(isempty(onindices))&&n<nstop)
         ll=onindices{i}(2);
         %take a measurement
         sensors{kk,ll}.sense(stato(1:2,n+1));
+        sensed{n,i}=[sensors{kk,ll}.position(1)+sensors{kk,ll}.sensed(1)*cos(sensors{kk,ll}.sensed(2)),sensors{kk,ll}.position(2)+sensors{kk,ll}.sensed(1)*sin(sensors{kk,ll}.sensed(2))];
         %IMM for each sensor on
         
         [sensors{kk,ll}.xmix,sensors{kk,ll}.Pmix...
@@ -455,6 +466,28 @@ while (~(isempty(onindices))&&n<nstop)
             if lon>=4
                 addpoints(curvesens4,xconsallsensor{n,4}(1),xconsallsensor{n,4}(2));
                 drawnow
+            end
+        end
+        if plotallsensed==1
+            if lon>=1
[…]

### 2020-01-29 Latex/exp.tex
tex update

@@
             for a possible physical system: to model a more enegy efficient system the sensor can switch to 3 different working condition: On,Off,Idle.
-            To achive this goal the sensor is working as a state machine as showned in the figure below:
-
+            To achive this goal the sensor is working as a state machine as showned in the figure below: \begin{figure}[htp]
+                \centering
+                \includegraphics[scale=0.1]{UntitledDiagram.png}
+                \caption{An image of a galaxy}
+                \label{fig:galaxy}
+                \end{figure}
             Sensors can communicate with the sensors in their neighboorhoods and exchange signal named CanSense and CantSense that regulate the transition
-            between differents state.
+            between differents state. Thus implies that not all the sensors receive all the messagge, but only from their Neighboors. The sensors in On state
+            create a fully connected graph. The nodes composing the graph changes dynamically with iterations according with the movements of target. The numbers of
+            sensors turned on depends on working range choosed and position of target.
 
@@
         \centering
-        \includegraphics[width=2cm, height=2cm]{UntitledDiagram.png}
+        \includegraphics[scale=0.1]{UntitledDiagram.png}
         \caption{An image of a galaxy}
@@
     \begin{equation}
-    X^{+}=\begin{bmatrix} A \\ \end{bmatrix}X(k)+\begin{bmatrix} B \\ \end{bmatrix}u(k) + \begin{bmatrix} G \\ \end{bmatrix}w(k)
+    X^{+}= \textbf{A}X(k) + \textbf{B}u(k) + \textbf{G}w(k)
     \end{equation}
     State,state and noise matrix associate to the random walk has showned below:
-    $$
-    X=\begin{bmatrix} x \\ y \\ \dot{x} \\ \dot{y} \\ \end{bmatrix}
-    $$
-
-    $$
-    A=\begin{bmatrix}
+    \[ X=\begin{bmatrix} x \\ y \\ \dot{x} \\ \dot{y} \\ \end{bmatrix}  A=\begin{bmatrix}
         1&0&\delta&0\\
@@
         \end{bmatrix}
-    $$
-
-    $$
         G=\begin{bmatrix}
             \delta^2/2&0\\
-    0&delta^2/2\\
+            0&\delta^2/2\\
             \delta&0\\
@@
             \end{bmatrix}
-    $$
-
-    $$
-    B= \begin{bmatrix}
-        \delta^2/2&0\\
-        0&delta^2/2\\
-        \delta&0\\
-        0&\delta\\
+        \]
+        The \textbf{B} input matrix change accordingly with the acceleration input
+    \[
+        B=\begin{bmatrix}
+            \delta^2/2 & 0\\
+            0 & 0  \\
+            \delta & 0 \\
+            0 & 0 \\
             \end{bmatrix}
-    $$
+            B=\begin{bmatrix}
+                0 & 0 \\
+             0 & \delta^2/2 \\
+            0 & 0 \\
+            0 & \delta \\
+            \end{bmatrix}
+  \]
    The unycicle model state representation employed has showned below

### 2020-01-29 Latex/exp.tex
Update

@@
 \usepackage{hyperref} % Add a link to your document
-\usepackage{graphicx}[final] % Add pictures to your document
+\usepackage[final]{graphicx} % Add pictures to your document
 \usepackage{listings} % Source code formatting and highlighting
@@
 \fancyfoot[LE,RO]{\thepage}
-\graphicspath{{Immagini/}}
-
+\graphicspath{{Immagini//}}
+%C:\Users\erikz\OneDrive\Desktop\PaioPaio2\IMM-Sensors-Network\Latex\Immagini
 \geometry{
@@
         from sensor are combined with different dynamical models through the algorithm... 
-        \subsection*{Simulation Model}
+        \subsection*{Sensor in simulation model}
             The target can move with random movement described by a Markov chain and accordingly two different models of movement
@@
             for a possible physical system: to model a more enegy efficient system the sensor can switch to 3 different working condition: On,Off,Idle.
-            To achive this goal the sensor is working as a state machine as showned in the figure below: \begin{figure}[htp]
+            To achive this goal the sensor is working as a state machine as showned in the figure below: 
+                \begin{figure}[h!]
                 \centering
-                \includegraphics[scale=0.1]{UntitledDiagram.png}
-                \caption{An image of a galaxy}
+                \includegraphics[scale=0.05]{UntitledDiagram.png}
+                \caption{State machine sensor}
                 \label{fig:galaxy}
@@
             create a fully connected graph. The nodes composing the graph changes dynamically with iterations according with the movements of target. The numbers of
-            sensors turned on depends on working range choosed and position of target.
+            sensors turned on depends on working range choosed and position of target. The mechanism that regulate the transition from sensors state 
+            relay on the information exchanged with nearby sensor. Different state can receive and send different messagesses. A sensor in On state has the moving 
+            object in his range and send a CanSense to the nearby and when trackin moving away from the operating range send a CantSense turning itself to Idle. 
+            Sensors that receive a CanSense and are not already On turn in Idle state; during the Idle state sensors check
+            if object appears in range sensors turn to On and send a CanSense, if nothing trigger the range it send to the nearby a CantSense signal.
+            A sensor that is in Idle and during the information exchange receive only CantSense from the nearby turn itself Off and stop to check if somenthing is in range and
+            can be turned again to Idle via a CanSense. This scheme implies that a sensors can never switch to On from Off except for the initialization step. 
+            When a sensor have the target in range it does a measure operation each timestep. the sensor works a radar in this model and remembering
+            \begin{equation}
+                z(k)=H(k)x(k)+\textbf{R}
+            \end{equation}
+            where the \textbf{H} is 
+            \begin{equation}
+                H= \begin{bmatrix}
+                    dopo & la \\
+                    scr & vo \\
+                \end{bmatrix}
+            \end{equation} 
+        \subsection*{Imm and Linear Consensu}
+               The IMM algorithm is based on the
 
-            {How the sensors works}
+    \section*{Model used}
+    Introduction
 
-            The measurment acquired by eachs sensors are then combined through the theory of linear consensus
-            The filter choosed are the WSL
-
-            Sensors in the simulations are Radar and the H matrix that reprent the measurment:
-
-        \subsection*{m}
-
-    \section*{Simulation model implementation}
-    Introduction
-    \subsection*{Filter}
-    \subsection*{Sensor}
-    The sensor grid are is composed by a set of sensor that can communicate with each others creating a fully connected graphic
-    The single sensor works as a state machine, and change its state accordingly with the signal exchanged with the neighboors.
-    \begin{figure}[htp]
-        \centering
-        \includegraphics[scale=0.1]{UntitledDiagram.png}
-        \caption{An image of a galaxy}
-        \label{fig:galaxy}
-    \end{figure}
     \subsection*{Random walk and Unycicle model}
-    The target in this simulation can move accordingly to two model: random walk and Unycicle. The genaral expression of the two process it
+    The target in this simulation can move accordingly to two model: random walk and Unycicle. Each of this model has a Markov chain that 
+    regulate how the given input goes in the system. For the random walk we have 5 state: costant velocity, positive or negative acceleration
+     on x direction and positive or negative deceleration on y direction. So the input are $\ddot{x}$ and $\ddot{y}$. The Markov chain associate is a circulant matrix as showned below
+     $$\begin{vmatrix}
+         0.8 & 0.025 & 0.025 & 0.025 & 0.025 // 
+     \end{vmatrix}$$
+     The equation regulating the state of the system is as well know
     \begin{equation}
@@
     \end{equation}
-    State,state and noise matrix associate to the random walk has showned below:
+    The Random walk model has is a linear model. State,state and noise matrix associate to the random walk has showned below:
     \[ X=\begin{bmatrix} x \\ y \\ \dot{x} \\ \dot{y} \\ \end{bmatrix}  A=\begin{bmatrix}
@@
   \]
-   The unycicle model state representation employed has showned below
+  It can be noticed that the \textbf{G} matrix of error can be seen as a sum of positive \textbf{B} rescaled by a random factor.
+
+  The unycicle model has different input and state description. The inputare represente by the angular acceleration of the wheel and the steering angle acceleration.
+  possible state are 5: constant angular velocity, acceleration and deceleration of the wheel and positice or negative acceleration of the steering angle.
+  The associate Markov chain for this case is  
+   $$\begin{vmatrix}
+         0.8 & 0.025 & 0.025 & 0.025 & 0.025 // 
+     \end{vmatrix}$$
+   Unycicle model instead is a Non-linear model. Thus is necessary to use a linearization in the Kalman filter implementation
+   The matrix that represent the state of system for this case are
+    \[ X=\begin{bmatrix} x \\ y \\ \dot{x} \\ \dot{y} \\ \end{bmatrix}  A=\begin{bmatrix}
+   1&0&\delta&0\\
+   0&1&0&\delta\\
+   0&0&1&0\\
+   0&0&0&1\\
+   \end{bmatrix}
+   G=\begin{bmatrix}
+       \delta^2/2&0\\
+       0&\delta^2/2\\
+       \delta&0\\
+       0&\delta\\
+       \end{bmatrix}
+   \]
+    \subsection*{Data's simulation}
 

### 2020-01-30 Latex/exp.tex
zzzz

@@
 \author{
-Paiola Lorenzo 000000
+Paiola Lorenzo 198573
 
@@
 \justify
-The porpouse of this document is the analysis and performance evaluation of an IMM algorithm's implementation in
-a sensor grid tracking an object. The object can move with two different model, random walk and unicycle, governed by
- a Markov chain. The goal is evaluate the best trade-off between error on estimated position and real position and number of 
- messagesses involved in tracking
+The purpouse of this project is to analyze and evaluate the performance of an IMM algorithm's implementation in a distributed environment for
+agent's traking. The agent switches between linked models of movement by the means of a Markov chain. The goal is evaluate the best trade-off
+between error on estimated position and real position and number of messagesses involved in the tracking.
 
 \begin{multicols}{2}
-    \section*{Backgound}
+    \section*{Setting}
     \justify
-        Tracking a object with a changing dynamic require propers algorithms and filters. Retriving physical data with
-        observations it's not enough, models achiving the best-fit to our data is needed in order to make a prediction and estimate 
+    NON CAPISCO COSA VUOI DIRE, IN QUALSIASI CASO QUA AGGIUNGI CHE PARLIAMO DI FILTRI DA DISCRETE-DISCRETE
+    \\
+    Tracking an object with a switching dynamic require proper algorithms and filters.Retriving physical data with
+    observations it's not enough in the case of Markov processes that switch between modes and we need to
+    , models achiving the best-fit to our data is needed in order to make a prediction and estimate
     with reduced uncertainty. Here comes to play a major role the IMM algorithm (Interacting Multiple Models): The data
     from sensor are combined with different dynamical models through the algorithm...
-        \subsection*{Sensor in simulation model}
-            The target can move with random movement described by a Markov chain and accordingly two different models of movement
-            The tracking are performed with grid of sensors. In order to perform a proper simulation the sensor has assumed to have a limited
-            range for the tracking and we cannot retrive any information if target is out. It also took in consideration the power consumption 
-            for a possible physical system: to model a more enegy efficient system the sensor can switch to 3 different working condition: On,Off,Idle.
-            To achive this goal the sensor is working as a state machine as showned in the figure below: 
+    \subsection*{Sensor's model}
+    The sensors chosen are radars measuring the relative polar cordinates at which the agent is collocated at the timestep and
+    are disposed as a uniform grid. In order to simulate the real workings of a sensor, we have limited the range of measurement to the distance
+    between one sensor and the following one in any direction in the grid, as soon as the agent exceed the range the device will stop sensing.
+    This property of the sensor grid, coupled by its geometry, ensures that no more than 4 sensors can measure the agent position at the time,
+    so it made sense to let sensor switch between 3 different states that we named ON, OFF and IDLE. This can be justified as a way to make the system
+    more power efficient and to avoid useless data stream towards sensors that aren't currently in range.
+    The sensor is modeled as a state machine as shown.
+    \\
+    AGGIUSTA FIGURA CHE E' SBAGLIATA E NON CI SONO GLI INRANGE, I CANSENSE/CANNOT SONO I SEGNALI MANDATI, NON LE ROBE CHE FANNO CAMBIARE STATO 
     \begin{figure}[h!]
@@
     \end{figure}
-            Sensors can communicate with the sensors in their neighboorhoods and exchange signal named CanSense and CantSense that regulate the transition
-            between differents state. Thus implies that not all the sensors receive all the messagge, but only from their Neighboors. The sensors in On state
-            create a fully connected graph. The nodes composing the graph changes dynamically with iterations according with the movements of target. The numbers of
+    \\
+    TABELLA CON LE FUNZIONI DEGLI STATI (mettere di fianco al paragrafo sotto una immagine che fa  vederecosa intendiamo con neighboors (gli 8 
+    sensori circostanti))
+    \\
+    Sensors can communicate with the devices adjacent to them (Neighboorhood) and exchange with them signals named CanSense and CantSense
+    which state respectively whenever the agent gets in or goes out of the communicating sensor's range. This check is done through the 
+    function inRange() that also serves as a switch between the states of the sensor, as already shown by the figure before.
+    \\
+    QUESTO METTILO NEL CONSENSUS, NON HA SENSO PARLARNE QUI
+    \\
+    The set of active sensors is dynamic, as vertices keep getting added and popped. However it has to be noticed, as stated before, that no 
+    more than 4 sensors will be ON at any point of time and they will all be adjacent to each other, this let us model the graph of the active 
+    sensors as fully-connected, since the distance between them is short and they are directly linked.
+    \\
+    The nodes composing the graph changes dynamically with iterations according with the movements of target. The numbers of
     sensors turned on depends on working range choosed and position of target. The mechanism that regulate the transition from sensors state
@@
     \subsection*{Random walk and Unycicle model}
-    The target in this simulation can move accordingly to two model: random walk and Unycicle. Each of this model has a Markov chain that 
+    The target in this simulation can move accordingly to two families of models, both are Markov processes.
+    \\
+    TABELLA CON DA UNA PARTE LE MODES DI UNO E DELL'ALTRO AL POSTO DI SPIEGARLO A PAROLE
+    \\
+    Each of this model has a Markov chain that
     regulate how the given input goes in the system. For the random walk we have 5 state: costant velocity, positive or negative acceleration
-     on x direction and positive or negative deceleration on y direction. So the input are $\ddot{x}$ and $\ddot{y}$. The Markov chain associate is a circulant matrix as showned below
+    on x direction and positive or negative deceleration on y direction. So the input are $\ddot{x}$ and $\ddot{y}$. The Transition matrix 
+    associated with the Markov's chain is shown below
     $$\begin{vmatrix}
@@
         \end{vmatrix}$$
-     The equation regulating the state of the system is as well know
+    The linear system describing the evolution of the state is 
     \begin{equation}
@@
     \end{equation}
-    The Random walk model has is a linear model. State,state and noise matrix associate to the random walk has showned below:
+    State,state and noise matrix associate to the random walk has shown below:
     \[ X=\begin{bmatrix} x \\ y \\ \dot{x} \\ \dot{y} \\ \end{bmatrix}  A=\begin{bmatrix}
-        1&0&\delta&0\\
-        0&1&0&\delta\\
-        0&0&1&0\\
-        0&0&0&1\\
+            1 & 0 & \delta & 0      \\
+            0 & 1 & 0      & \delta \\
+            0 & 0 & 1      & 0      \\
+            0 & 0 & 0      & 1      \\
         \end{bmatrix}
         G=\begin{bmatrix}
-            \delta^2/2&0\\
-            0&\delta^2/2\\
-            \delta&0\\
-            0&\delta\\
+            \delta^2/2 & 0          \\
+            0          & \delta^2/2 \\
+            \delta     & 0          \\
+            0          & \delta     \\
         \end{bmatrix}
     \]
-        The \textbf{B} input matrix change accordingly with the acceleration input
+    With $\delta$ time step of the simulation.
+    The \textbf{B} input matrix change accordingly with the acceleration input (of what we suppose we know only the magnitude)
     \[
-        B=\begin{bmatrix}
-            \delta^2/2 & 0\\
+        B=\begin{Bmatrix}
+            \begin{bmatrix}
+                0 & 0 \\
+                0          & 0 \\
+                0     & 0 \\
+                0          & 0 \\
+            \end{bmatrix}
+            \begin{bmatrix}
+                \delta^2/2 & 0 \\
                 0          & 0 \\
@@
             \end{bmatrix}
-            B=\begin{bmatrix}
+            \begin{bmatrix}
+                -\delta^2/2 & 0 \\
+                0          & 0 \\
+                -\delta     & 0 \\
+                0          & 0 \\
+            \end{bmatrix}
+            \begin{bmatrix}
                 0 & 0          \\
@@
             \end{bmatrix}
+            \begin{bmatrix}
+                0 & 0          \\
+                0 & -\delta^2/2 \\
+                0 & 0          \\
+                0 & -\delta     \\
+            \end{bmatrix}
+        \end{Bmatrix}
     \]
-  It can be noticed that the \textbf{G} matrix of error can be seen as a sum of positive \textbf{B} rescaled by a random factor.
+    The \textbf{G} matrix is a merge between the "positive" matrices .
 
@@
     \[ X=\begin{bmatrix} x \\ y \\ \dot{x} \\ \dot{y} \\ \end{bmatrix}  A=\begin{bmatrix}
-   1&0&\delta&0\\
-   0&1&0&\delta\\
-   0&0&1&0\\
-   0&0&0&1\\
+            1 & 0 & \delta & 0      \\
+            0 & 1 & 0      & \delta \\
+            0 & 0 & 1      & 0      \\
+            0 & 0 & 0      & 1      \\
         \end{bmatrix}
         G=\begin{bmatrix}
-       \delta^2/2&0\\
-       0&\delta^2/2\\
-       \delta&0\\
-       0&\delta\\
+            \delta^2/2 & 0          \\
+            0          & \delta^2/2 \\
+            \delta     & 0          \\
+            0          & \delta     \\
         \end{bmatrix}

### 2020-01-30 Progetto2.m

@@ -5,18 +5,18 @@ clc; clear all; close all;
 %1-> markov chain constant speed or costant acceleration
 %2-> unicycle
 
-caso=1;
+caso=2;
 %delta time
-delta=0.05;
+delta=0.3;
 %at which rate do we do the consensus ?
 rate=1;
 %Maximum number of iteration
-nstop=2000;
+nstop=100;
 %Plot
 videon = 0;
-ploton =1;
+ploton =0;
 plotallsenson=0;
-plotallsensed=1;
+plotallsensed=0;
 switch caso
     
     case 1
@@ -98,12 +98,13 @@ switch caso
         Transmat(5,:)=[q 0 0 q q1];
         %initial 2D position, velocity and acceleration
         x0=zeros(nx,1);
-        x0([1,2])=0.5;
-        x0(4)=pi/2;
+        x0([1,2])=[-1;-1]+2.*rand(2,1);
+        x0(3)=0.3;
+        x0(4)=pi/3;
         %radius, called like this for reasons
         ABG=0.3;
         %Power spectra density of process noise
-        Q=diag([0.1,0.1]);
+        Q=diag([0.01,0.01]);
         %magnitude of acceleration
         acc=[2;1].*0.1;
         P0=diag([1,1,1,1]);
@@ -143,7 +144,7 @@ mu(:,1)=mu1'; %first state is constant velocity for design and we suppose we kno
 %%
 
 %initialize sensor Grid
-nq=20;      %grid's size (even number plez)
+nq=10;      %grid's size (even number plez)
 sensors=num2cell(zeros(nq));
 %basic sensor proprieties
 for i=1:nq

### 2020-01-30 Latex/exp.tex
sssss

@@
 The purpouse of this project is to analyze and evaluate the performance of an IMM algorithm's implementation in a distributed environment for
-agent's traking. The agent switches between linked models of movement by the means of a Markov chain. The goal is evaluate the best trade-off
+agent's tracking. The agent switches between linked models of movement by the means of a Markov chain. The goal is evaluate the best trade-off
 between error on estimated position and real position and number of messagesses involved in the tracking.
@@
     \subsection*{Sensor's model}
-    The sensors chosen are radars measuring the relative polar cordinates at which the agent is collocated at the timestep and
+    The sensors chosen are radars measuring the relative polar cordinates at which the agent is collocated at the timestep, and
     are disposed as a uniform grid. In order to simulate the real workings of a sensor, we have limited the range of measurement to the distance
-    between one sensor and the following one in any direction in the grid, as soon as the agent exceed the range the device will stop sensing.
+    between one sensor and the following one in any direction of the grid, as soon as the agent exceed the imposed maxiumum distance from the sensor,
+    the device will stop sensing.
     This property of the sensor grid, coupled by its geometry, ensures that no more than 4 sensors can measure the agent position at the time,
     so it made sense to let sensor switch between 3 different states that we named ON, OFF and IDLE. This can be justified as a way to make the system
-    more power efficient and to avoid useless data stream towards sensors that aren't currently in range.
+    more power efficient and to avoid useless data stream towards sensors that aren't currently in range and sensing.
     The sensor is modeled as a state machine as shown.
@@
     which state respectively whenever the agent gets in or goes out of the communicating sensor's range. This check is done through the 
-    function inRange() that also serves as a switch between the states of the sensor, as already shown by the figure before.
+    function inRange() that also serves as a switch between the states of the sensor, as already shown by the figure above.
     \\
@@
     \\
-    The set of active sensors is dynamic, as vertices keep getting added and popped. However it has to be noticed, as stated before, that no 
+    The set of active sensors inside the grid is dynamic, as vertices keep getting added and popped. However it has to be noticed, as stated before, that no 
     more than 4 sensors will be ON at any point of time and they will all be adjacent to each other, this let us model the graph of the active 
@@
     \\
-    The nodes composing the graph changes dynamically with iterations according with the movements of target. The numbers of
-    sensors turned on depends on working range choosed and position of target. The mechanism that regulate the transition from sensors state
-    relay on the information exchanged with nearby sensor. Different state can receive and send different messagesses. A sensor in On state has the moving
+    Different state can receive and send different messagesses. A sensor in On state has the moving
     object in his range and send a CanSense to the nearby and when trackin moving away from the operating range send a CantSense turning itself to Idle.
@@
     can be turned again to Idle via a CanSense. This scheme implies that a sensors can never switch to On from Off except for the initialization step.
+    \\
     When a sensor have the target in range it does a measure operation each timestep. the sensor works a radar in this model and remembering
     \begin{equation}
-        z(k)=H(k)x(k)+\textbf{R}
+        z(k)=h(x(k))+v(k)
     \end{equation}
+    where $h(x)$ is the polar to cartesian cordinates transfor
+    \begin{equation*}
+        \begin{bmatrix}
+            \rho\\ \alpha
+        \end{bmatrix}=
+    \end{equation*}
     where the \textbf{H} is
@@
         H= \begin{bmatrix}
-            dopo & la \\
-            scr  & vo \\
+            \frac{x}{(x^{2}+y^{2})^{1/2}} & \frac{y}{(x^{2}+y^{2})^{1/2}}& 0& 0 \\
+            \frac{-y}{(x^{2}+y^{2})}  & \frac{x}{(x^{2}+y^{2})}& 0& 0 \\
         \end{bmatrix}
@@
     \\
-    Each of this model has a Markov chain that
-    regulate how the given input goes in the system. For the random walk we have 5 state: costant velocity, positive or negative acceleration
-    on x direction and positive or negative deceleration on y direction. So the input are $\ddot{x}$ and $\ddot{y}$. The Transition matrix 
+
+    In the case of the random walk we choosen to have 5 states: costant velocity, positive or negative acceleration
+    on x direction and positive or negative deceleration on y direction. The Transition matrix 
     associated with the Markov's chain is shown below
-    $$\begin{vmatrix}
+    \begin{equation*}
+        \begin{bmatrix}
             0.8 & 0.025 & 0.025 & 0.025 & 0.025 //
-        \end{vmatrix}$$
+        \end{bmatrix}
+    \end{equation*}
     The linear system describing the evolution of the state is 
     \begin{equation}
-        X^{+}= \textbf{A}X(k) + \textbf{B}u(k) + \textbf{G}w(k)
+        x(k+1)= Ax(k) + B(s)u(k) + Gw(k)
     \end{equation}
+    Where $x(k)$ is the state at the current timestep, $u(t)$ is the input and $w(k)$ is the process noise.
+    In this case the state is a vector of the cartesian cordinates and their relative speed, while the input 
+    is the acceleration which the noise will influence. 
     State,state and noise matrix associate to the random walk has shown below:
-    \[ X=\begin{bmatrix} x \\ y \\ \dot{x} \\ \dot{y} \\ \end{bmatrix}  A=\begin{bmatrix}
+    \[ x=\begin{bmatrix} x \\ y \\ \dot{x} \\ \dot{y} \\ \end{bmatrix}  A=\begin{bmatrix}
             1 & 0 & \delta & 0      \\
@@
     With $\delta$ time step of the simulation.
-    The \textbf{B} input matrix change accordingly with the acceleration input (of what we suppose we know only the magnitude)
+    \\
+    We hypothesize that the input is unknown in direction but known in magnitude. This set according to the current state at which the markov process is at the timestep.
+    This is modeled though the switch between a set of matrices $B(s)$ that change according to the chain's state $s$.
     \[
-        B=\begin{Bmatrix}
+        B(s)=\begin{Bmatrix}
             \begin{bmatrix}
@@
     \]
-    The \textbf{G} matrix is a merge between the "positive" matrices .
+    It can be noticed that the matrix $G$ is a merge between the second and the fourth matrices found in the set $B(s)$ as the noise will act
+    randomly in direction and magnitude at every time-step.
 

### 2020-01-30 Latex/exp.tex
.Tex Willer
Bang Bang

@@
-\documentclass{article}
+\documentclass[twocolumn]{article}
 \usepackage[utf8]{inputenc}
@@
 \usepackage[utf8]{inputenc} % Unicode support (Umlauts etc.)
-\usepackage[ngerman]{babel} % Change hyphenation rules
+\usepackage[english]{babel} % Change hyphenation rules
 \usepackage{hyperref} % Add a link to your document
-\usepackage[final]{graphicx} % Add pictures to your document
+\usepackage{graphicx} % Add pictures to your document
 \usepackage{listings} % Source code formatting and highlighting
@@
 \usepackage{geometry}
-\usepackage{multicol}
+%\usepackage{multicol}
 \usepackage{fancyhdr}
 \usepackage[document]{ragged2e}
-
-\pagestyle{fancy}
-\fancyhf{}
-\fancyhead[LE,RO]{Overleaf}
-\fancyhead[RE,LO]{Guides and tutorials}
-\fancyfoot[CE,CO]{\leftmark}
-\fancyfoot[LE,RO]{\thepage}
-\graphicspath{{Immagini//}}
+\usepackage{adjustbox}
+\usepackage{subcaption}
+% \pagestyle{fancy}
+% \fancyhf{}
+% \fancyhead[LE,RO]{Overleaf}
+% \fancyhead[RE,LO]{Guides and tutorials}
+% \fancyfoot[CE,CO]{\leftmark}
+% \fancyfoot[LE,RO]{\thepage}
+\graphicspath{ {Immagini/} }
 %C:\Users\erikz\OneDrive\Desktop\PaioPaio2\IMM-Sensors-Network\Latex\Immagini
@@
 
-\begin{multicols}{2}
     \section*{Setting}
@@
     The sensors chosen are radars measuring the relative polar cordinates at which the agent is collocated at the timestep, and
-    are disposed as a uniform grid. In order to simulate the real workings of a sensor, we have limited the range of measurement to the distance
+    are disposed as a uniform grid. In order to simulate the real workings of a sensor, range of measuremnt has been limited to the distance
     between one sensor and the following one in any direction of the grid, as soon as the agent exceed the imposed maxiumum distance from the sensor,
@@
     This property of the sensor grid, coupled by its geometry, ensures that no more than 4 sensors can measure the agent position at the time,
-    so it made sense to let sensor switch between 3 different states that we named ON, OFF and IDLE. This can be justified as a way to make the system
+    so it made sense to let sensor switch between 3 different states named ON, OFF and IDLE. This can be justified as a way to make the system
     more power efficient and to avoid useless data stream towards sensors that aren't currently in range and sensing.
@@
     \\
-    AGGIUSTA FIGURA CHE E' SBAGLIATA E NON CI SONO GLI INRANGE, I CANSENSE/CANNOT SONO I SEGNALI MANDATI, NON LE ROBE CHE FANNO CAMBIARE STATO 
     \begin{figure}[h!]
         \centering
-        \includegraphics[scale=0.05]{UntitledDiagram.png}
+        \includegraphics[width=\columnwidth]{sensor_state_machine.png}
         \caption{State machine sensor}
@@
     \\
+Every sensor accordingly with its state can perform some action and send information following the rules listed in the table below
+\\ 
+    \begin{center}
+        \begin{adjustbox}{max width=0.45\textwidth}
+        \begin{tabular}{||c c c c||}
+            \hline
+              & On & 3 Idle & Off \\ [0.5ex]
+            \hline\hline
+            InRange()==      & True      & False  & False    \\
+            \hline
+            Message sent      & CanSense      & CantSense     & X   \\
+            \hline
+            Functions      & measurement    & ready to switch to On    & X   \\
+            \hline
+
+            \hline
+        \end{tabular}
+    \end{adjustbox}
+    \end{center}
+
     TABELLA CON LE FUNZIONI DEGLI STATI (mettere di fianco al paragrafo sotto una immagine che fa  vederecosa intendiamo con neighboors (gli 8 
@@
     function inRange() that also serves as a switch between the states of the sensor, as already shown by the figure above.
+    \begin{figure}[h!]
+        \centering
+        \includegraphics[width=0.3\textwidth]{Immagini/Neighboors.png}
+        \caption{Neighboors for a sensors are the one immediately adiacent. The purples ones represent the neighboors of green sensor}
+        \label{fig:galaxy}
+    \end{figure}
     \\
-    QUESTO METTILO NEL CONSENSUS, NON HA SENSO PARLARNE QUI
-    \\
-    The set of active sensors inside the grid is dynamic, as vertices keep getting added and popped. However it has to be noticed, as stated before, that no 
-    more than 4 sensors will be ON at any point of time and they will all be adjacent to each other, this let us model the graph of the active 
-    sensors as fully-connected, since the distance between them is short and they are directly linked.
+    % QUESTO METTILO NEL CONSENSUS, NON HA SENSO PARLARNE QUI
+    % \\
+    % The set of active sensors inside the grid is dynamic, as vertices keep getting added and popped. However it has to be noticed, as stated before, that no 
+    % more than 4 sensors will be ON at any point of time and they will all be adjacent to each other, this let us model the graph of the active 
+    % sensors as fully-connected, since the distance between them is short and they are directly linked.
     \\
@@
     \\
-    When a sensor have the target in range it does a measure operation each timestep. the sensor works a radar in this model and remembering
+    When a sensor have the target in range it does a measure operation each timestep. the sensor works as a radar in this model and remembering
     \begin{equation}
@@
     \end{equation}
-    where $h(x)$ is the polar to cartesian cordinates transfor
+    where $h(x)$ is the polar to cartesian cordinates transform and $v(k)$ is the noise associated to the measurement's operation.
+
     \begin{equation*}
@@
         \end{bmatrix}=  
+        \begin{bmatrix}
+            x^2+y^2\\ atan2(y/x)
+        \end{bmatrix} 
     \end{equation*}
-    where the \textbf{H} is
+   for sake of use in the extended Kalman filter, a linearization of $h(x)$ must be performed.
+   The WLS problem associate becomes
+   \begin{equation*}
+       x^{WSL}(k)=arg min(Z^{k}-h(x)W(Z^{k}-h(x))^{T})= argmin J(x,k)
+   \end{equation*}
+   and we have to found 
+   \begin{equation*}
+     \frac{dJ(x,k)}{dx}=0
+\end{equation*}
+After a bit of management we can compute 
+\begin{equation*}
+    J(x,k)=Z^{k}
+\end{equation*}
+        and than it follows that
+        \begin{equation*}
+            \frac{dJ(x,k)}{dx}=-H(x)^{T}W(Z^{K}-h(x))=0
+        \end{equation*}
+        where $H(x)=\frac{dh(x)}{dx}$ So in this particular case:
     \begin{equation}
@@
     \end{equation}
-    \subsection*{Imm and Linear Consensu}
-    The IMM algorithm is based on the
+    \subsection*{Imm and Linear Consensus}
+    In order to reach a more accurate prediction of the trajectory a IMM algorithm is implemented in the sensors's grid. The working principles 
+    involves a general knowledge or hypothesis of the model of agent's movement. Every model is used in a Kalman filter stage that use the same measurement and make
+    a prediction: the one with the smaller uncertainty is choose as the model for our agent at that timestep. A general scheme of the working principles is shown here (image?)
 
@@
     Introduction
-
-    \subsection*{Random walk and Unycicle model}
-    The target in this simulation can move accordingly to two families of models, both are Markov processes.
+    Discrete Wiener Process Acceleration Model
+    \subsection*{ Discrete Wiener Process Acceleration Model and Unycicle model}
+    The target in this simulation can move accordingly to two families of models, both are Markov processes: 
+    The Discrete Wienerprocess acceleration model and The Unycle model. The main caratheristic of both are represented in the table below
     \\
-    TABELLA CON DA UNA PARTE LE MODES DI UNO E DELL'ALTRO AL POSTO DI SPIEGARLO A PAROLE
+    % \begin{tabular}{ |c|c|c|c|c|c| }
+    % \multicolumn{6}{|c|}{Models} \\
+    \begin{tabular}{||c |c  | c  |c|c|c|c|c c c c c||}%{|width=\columnwidth|}
+        \hline
+         & DPWA && Unycicle \\
+        \hline
+             & Modes & Input & Modes & Inputs\\ [0.5ex]
+        \hline\hline
+        state 1 & costant velocity      & $\ddot{x},\ddot{y}=0$ & constant angular velocity &  $\ddot{\omega},\ddot{\alpha}=0$   \\
+        \hline
+        state 2  & north acceleration      & $\ddot{x}=\delta$  &  angular acceleration &  $\ddot{\omega}=\delta$ \\
+        \hline
+        state 3  & south acceleration    & $\ddot{x}=-\delta$   &  angular deceleration  & $\ddot{\omega}=-\delta$ \\
+        \hline
+        state 4  & east acceleration    & $\ddot{y}=\delta$    & acceleration steering (CW) & $\ddot{\omega}=\delta$ \\
+        \hline
+        state 5  & west acceleration     & $\ddot{y}=-\delta$  &  acceleration steering (CCW) & $\ddot{\omega}=-\delta$ \\ [1ex]
+        \hline
+    \end{tabular}
     \\
 
-    In the case of the random walk we choosen to have 5 states: costant velocity, positive or negative acceleration
-    on x direction and positive or negative deceleration on y direction. The Transition matrix 
+    In the case of the DWPA we choosen to have 5 states: costant velocity, positive or negative acceleration
+    on x direction and positive or negative deceleration on y direction.
+    \begin{tabular}{||c c c||}%[width=\columnwidth]
+        \hline
+        state 1 & costant velocity      & $\ddot{x},\ddot{y}=0$     \\
+        \hline
+        state 2  & north acceleration      & $\ddot{x}=\delta$        \\
+        \hline
+        state 3  & south acceleration    & $\ddot{x}=-\delta$        \\
+        \hline
+        state 4  & east acceleration    & $\ddot{y}=\delta$     \\
+        \hline
+        state 5  & west acceleration     & $\ddot{y}=-\delta$       \\ [1ex]
+        \hline
+    \end{tabular} The Transition matrix 
     associated with the Markov's chain is shown below
@@
     is the acceleration which the noise will influence. 
-    State,state and noise matrix associate to the random walk has shown below:
+    State,state and noise matrix associate to the DWPA has shown below:
     \[ x=\begin{bmatrix} x \\ y \\ \dot{x} \\ \dot{y} \\ \end{bmatrix}  A=\begin{bmatrix}
@@
     This is modeled though the switch between a set of matrices $B(s)$ that change according to the chain's state $s$.
-    \[
-        B(s)=\begin{Bmatrix}
+    \begin{equation*}%[width=\columnwidth]
+        \resizebox{.9 \columnwidth}{!}{
+        $B(s)=\begin{Bmatrix}
             \begin{bmatrix}
@@
             \end{bmatrix}
-        \end{Bmatrix}
-    \]
+        \end{Bmatrix} $ 
+        }
+    \end{equation*}
+
     It can be noticed that the matrix $G$ is a merge between the second and the fourth matrices found in the set $B(s)$ as the noise will act
@@
 
-    The unycicle model has different input and state description. The inputare represente by the angular acceleration of the wheel and the steering angle acceleration.
+    The unycicle model has different input and state description. The input are represented by the angular acceleration of the wheel and the steering angle acceleration.
     possible state are 5: constant angular velocity, acceleration and deceleration of the wheel and positice or negative acceleration of the steering angle.
     The associate Markov chain for this case is
+    \begin{tabular}{||c c c c||}
+        \hline
+        state 1 & 6      & 87837  & 787    \\
+        \hline
+        state 2  & 7      & 78     & 5415   \\
+        \hline
+        state 3      & 545    & 778    & 7507   \\
+        \hline
+        state 4      & 545    & 18744  & 7560   \\
+        \hline
+        state 5      & 88     & 788    & 6344   \\ [1ex]
+        \hline
+    \end{tabular}
     $$\begin{vmatrix}
@@
     \subsection*{}
-\end{multicols}
+
 \end{document}

### 2020-01-30 Progetto2.m

@@ -5,9 +5,9 @@ clc; clear all; close all;
 %1-> markov chain constant speed or costant acceleration
 %2-> unicycle
 
-caso=2;
+caso=1;
 %delta time
-delta=0.3;
+delta=0.05;
 %at which rate do we do the consensus ?
 rate=1;
 %Maximum number of iteration

### 2020-01-31 Latex/exp.tex
Problems on measure
I think problems come from the nonlinearity of the measure model, gonna work on that, attempts with low R tend to yield better results (obviously)

@@
     \\
-    When a sensor have the target in range it does a measure operation each timestep. the sensor works as a radar in this model and remembering
-    \begin{equation}
-        z(k)=h(x(k))+v(k)
-    \end{equation}
+    Whenever the target is in range of a sensor, the device takes a measurement at each timestep.
+    The model we choose for our measurement device is a radar and as such the measurement function 
+    $z(k)=h(x(k))+v(k)$ associated with it is the cartesian to polar transformation, as shown below
+    \begin{align*}
+        &z(k)=h(x(k))+v(k)\\
+        &\begin{bmatrix}
+            \rho(k)\\ \alpha(k)
+        \end{bmatrix}=  
+        \begin{bmatrix}
+            \sqrt{x(k)^2+y(k)^2}\\ atan2(y(k)/x(k))
+        \end{bmatrix} +
+        \begin{bmatrix}
+            v_{1}(k)\\v_{2}(k)
+        \end{bmatrix}
+    \end{align*}
     where $h(x)$ is the polar to cartesian cordinates transform and $v(k)$ is the noise associated to the measurement's operation.

### 2020-01-31 Functions/IMM.m

@@ -51,13 +51,17 @@ for i=1:alto
     else
         [xpred(:,i),Ppred(:,:,i),dz(:,i),S(:,:,i)]=kalman(Mat,xmix(:,i),u,z,Pmix(:,:,i),Q,R,caso,offset,delta,i);
     end
-    %% to avoid error => threshold 
-    if  rcond(S(:,:,i))<1e-6
+    % to avoid error => threshold 
+    if  rcond(S(:,:,i))<1e-7
         L(i)=0.001;
     elseif all(eig(S(:,:,i))>1e-6)
         L(i)=mvnpdf(dz(:,i),0,S(:,:,i));
+        if L(i)==0
+            "Likelihood=0 perchè dz troppo grande e S piccolina"
+            L(i)=0.001;
+        end
     else
-        "HOW"
+        "S negative definite o qualcosa che non so spiegare"
     end
     
 end
@@ -73,7 +77,7 @@ Pkk=zeros(largo);
 for i=1:alto
     Pkk=Pkk+(Ppred(:,:,i)+(xkk-xpred(:,i))*(xkk-xpred(:,i))')*muk1(i);
 end
-if rcond(Pkk)<0.0001
-    "OMEGALUL"
+if rcond(Pkk)<1e-7
+    "P risultato IMM troppo piccola"
 end
 end

### 2020-01-31 Functions/WLS.m

@@ -2,7 +2,7 @@ function [xLS,PLS] = WLS(z,C,H)
 %Weighted least min squared
 PLS=inv(H'/C*H);
 if rcond(PLS)<=1e-8
-    "AAAAA"
+    "WLS con P troppo piccola"
 end
 xLS=PLS*H'/C*z;
 end

### 2020-01-31 Sensor.m

@@ -136,8 +136,7 @@ classdef Sensor<handle
                 %all the kalman estimates
                 xpred1=[xpred1;sensorgrid{kk,ll}.xpred];
                 wantPpred{i}(:,:,:)=sensorgrid{kk,ll}.Ppred;
-                mu1=[mu1;sensorgrid{kk,ll}.mu];
-                muijg=blkdiag(muijg,sensorgrid{kk,ll}.muij);
+                mu1=[mu1,sensorgrid{kk,ll}.mu];
                 Hcons=[Hcons;eye(lungstato)];
                 Hmu=[Hmu;eye(nummarkov)];
             end
@@ -147,7 +146,7 @@ classdef Sensor<handle
             %H is gonna be a stacked matrix of identities since our measure
             %is exactly zmix
             [obj.xcons,obj.Pcons]=WLS(xcons1,covmix,Hcons);
-            [obj.mu,obj.muij]=WLS(mu1,muijg,Hmu);
+            obj.mu=mean(mu1,2);
             %kalman
             for j=1:nummarkov
                 Cpred=[];

### 2020-01-31 Latex/exp.tex
Update
update

@@
     \\
-Every sensor accordingly with its state can perform some action and send information following the rules listed in the table below
-\\ 
-    \begin{center}
-        \begin{adjustbox}{max width=0.45\textwidth}
-        \begin{tabular}{||c c c c||}
-            \hline
-              & On & 3 Idle & Off \\ [0.5ex]
-            \hline\hline
-            InRange()==      & True      & False  & False    \\
-            \hline
-            Message sent      & CanSense      & CantSense     & X   \\
-            \hline
-            Functions      & measurement    & ready to switch to On    & X   \\
-            \hline
+The functions and operations that the sensors can do are:
+\begin{itemize}
+    \item InRange() : function that verify the presence of the target in its working area 
+    \item CanSense : messagge sent by a sensor switching from Idle to On triggered by a positive result from InRange() function
+    \item CantSense : message sent by a sensor switching from On to Idle triggered by a negative result from InRange() function
+    \end{itemize}
+    Every sensor accordingly with its state can perform some action and send information following the rules listed below:
+\begin{itemize}
+    \item On: participate in the measurement process while InRange() stay with positive result. 
+    It retrieve data on position and perform a IMM algorithm and with a selected rate perform a linear consensus calculation 
+    \item Idle : perform a InRange() verification each timestep to verify if it have to switch in On. If triggered to On 
+    initialization starts using data from the others sensors as a starting point.
+    if it receive a CantSense from all the neighboors it turn itself off.
+    \item Off : no measurment function or involvement. Triggered to Idle when receive one CanSense by the neighboors
+    \end{itemize}
 
-            \hline
-        \end{tabular}
-    \end{adjustbox}
-    \end{center}
+    % \begin{center}
+    %     \begin{adjustbox}{max width=0.45\textwidth}
+    %     \begin{tabular}{||c| c| c |c||}
+    %         \hline
+    %           & On & 3 Idle & Off \\ [0.5ex]
+    %         \hline\hline
+    %         InRange()==      & True      & False  & False    \\
+    %         \hline
+    %         Message sent      & CanSense      & CantSense     & X   \\
+    %         \hline
+    %         Functions      & measurement    & ready to switch to On    & X   \\
+    %         \hline
 
-    TABELLA CON LE FUNZIONI DEGLI STATI (mettere di fianco al paragrafo sotto una immagine che fa  vederecosa intendiamo con neighboors (gli 8 
-    sensori circostanti))
-    \\
-    Sensors can communicate with the devices adjacent to them (Neighboorhood) and exchange with them signals named CanSense and CantSense
+    %         \hline
+    %     \end{tabular}
+    % \end{adjustbox}
+    % \end{center}
+    So sensors can communicate with the devices adjacent to them (Neighboorhood), as represented in the figure below, and exchange with them signals named CanSense and CantSense
     which state respectively whenever the agent gets in or goes out of the communicating sensor's range. This check is done through the 
     function inRange() that also serves as a switch between the states of the sensor, as already shown by the figure above.
+    \\
     \begin{figure}[h!]
         \centering
-        \includegraphics[width=0.3\textwidth]{Immagini/Neighboors.png}
+        \includegraphics[width=0.2\textwidth]{Immagini/2sensor.png}
         \caption{Neighboors for a sensors are the one immediately adiacent. The purples ones represent the neighboors of green sensor}
@@
     \\
-    % QUESTO METTILO NEL CONSENSUS, NON HA SENSO PARLARNE QUI
+    Defing the range of the sensors equal to their spacing on the grid it follows, depending on agent's position, only a maximum of 4 sensors can be turned on. 
+    It follows a figure that show the idea with a 4-sensors grid
+    \begin{figure}[h!]
+        \centering
+        \includegraphics[width=0.23\textwidth]{Immagini/4sensor.png}
+        \caption{}
+        \label{fig:galaxy}
+    \end{figure}
+    \begin{itemize}
+        \item blue : 1 sensors On 
+        \item yellow : 2 sensors On 
+        \item orange : 3 sensors On 
+        \item red : 4 sensors On 
+        \end{itemize}
+    % Different state can receive and send different messagesses. A sensor in On state has the moving
+    % object in his range and send a CanSense to the nearby and when trackin moving away from the operating range send a CantSense turning itself to Idle.
+    % Sensors that receive a CanSense and are not already On turn in Idle state; during the Idle state sensors check
+    % if object appears in range sensors turn to On and send a CanSense, if nothing trigger the range it send to the nearby a CantSense signal.
+    % A sensor that is in Idle and during the information exchange receive only CantSense from the nearby turn itself Off and stop to check if somenthing is in range and
+    % can be turned again to Idle via a CanSense. This scheme implies that a sensors can never switch to On from Off except for the initialization step.
     % \\
-    % The set of active sensors inside the grid is dynamic, as vertices keep getting added and popped. However it has to be noticed, as stated before, that no 
-    % more than 4 sensors will be ON at any point of time and they will all be adjacent to each other, this let us model the graph of the active 
-    % sensors as fully-connected, since the distance between them is short and they are directly linked.
-    \\
-    Different state can receive and send different messagesses. A sensor in On state has the moving
-    object in his range and send a CanSense to the nearby and when trackin moving away from the operating range send a CantSense turning itself to Idle.
-    Sensors that receive a CanSense and are not already On turn in Idle state; during the Idle state sensors check
-    if object appears in range sensors turn to On and send a CanSense, if nothing trigger the range it send to the nearby a CantSense signal.
-    A sensor that is in Idle and during the information exchange receive only CantSense from the nearby turn itself Off and stop to check if somenthing is in range and
-    can be turned again to Idle via a CanSense. This scheme implies that a sensors can never switch to On from Off except for the initialization step.
-    \\
     Whenever the target is in range of a sensor, the device takes a measurement at each timestep.
@@
    for sake of use in the extended Kalman filter, a linearization of $h(x)$ must be performed.
-   The WLS problem associate becomes
+   The LS problem associate becomes
    \begin{equation*}
-       x^{WSL}(k)=arg min(Z^{k}-h(x)W(Z^{k}-h(x))^{T})= argmin J(x,k)
+       x^{SL}(k)=arg min(Z^{k}-h(x)W(Z^{k}-h(x))^{T})= argmin J(x,k)
    \end{equation*}
@@
     \end{equation}
-    \subsection*{Imm and Linear Consensus}
-    In order to reach a more accurate prediction of the trajectory a IMM algorithm is implemented in the sensors's grid. The working principles 
-    involves a general knowledge or hypothesis of the model of agent's movement. Every model is used in a Kalman filter stage that use the same measurement and make
-    a prediction: the one with the smaller uncertainty is choose as the model for our agent at that timestep. A general scheme of the working principles is shown here (image?)
-
     \section*{Model used}
-    Introduction
-    Discrete Wiener Process Acceleration Model
-    \subsection*{ Discrete Wiener Process Acceleration Model and Unycicle model}
-    The target in this simulation can move accordingly to two families of models, both are Markov processes: 
-    The Discrete Wienerprocess acceleration model and The Unycle model. The main caratheristic of both are represented in the table below
+    To models the movement of the target has been employed two models: The discrete Wienerprocess acceleration model (DWPA) (reference) and the unicycle model
+    Both are Markov process.
+    \subsection*{ Discrete Wiener Process Acceleration Model}
+    The Discrete Wienerprocess acceleration model choose are described by 5 different mode
     \\
@@
     % \multicolumn{6}{|c|}{Models} \\
-    \begin{tabular}{||c |c  | c  |c|c|c|c|c c c c c||}%{|width=\columnwidth|}
+    % \begin{tabular}{||c |c  | c  |c|c|c|c|c c c c c||}%{|width=\columnwidth|}
+    %     \hline
+    %      & DPWA && Unycicle \\
+    %     \hline
+    %          & Modes & Input & Modes & Inputs\\ [0.5ex]
+    %     \hline\hline
+    %     state 1 & costant velocity      & $\ddot{x},\ddot{y}=0$ & constant angular velocity &  $\ddot{\omega},\ddot{\alpha}=0$   \\
+    %     \hline
+    %     state 2  & north acceleration      & $\ddot{x}=\delta$  &  angular acceleration &  $\ddot{\omega}=\delta$ \\
+    %     \hline
+    %     state 3  & south acceleration    & $\ddot{x}=-\delta$   &  angular deceleration  & $\ddot{\omega}=-\delta$ \\
+    %     \hline
+    %     state 4  & east acceleration    & $\ddot{y}=\delta$    & acceleration steering (CW) & $\ddot{\omega}=\delta$ \\
+    %     \hline
+    %     state 5  & west acceleration     & $\ddot{y}=-\delta$  &  acceleration steering (CCW) & $\ddot{\omega}=-\delta$ \\ [1ex]
+    %     \hline
+    % \end{tabular}
+    \begin{center}
+    \begin{tabular}{||c||c |c |c| |}%{|width=\columnwidth|}
         \hline
-         & DPWA && Unycicle \\
+         DPWA  \\
+        \hline\hline
+         Modes & Description & Input \\ [0.5ex]
+        \hline\hline
+        mode 1 & costant velocity      & $u(k)=0$    \\
         \hline
-             & Modes & Input & Modes & Inputs\\ [0.5ex]
-        \hline\hline
-        state 1 & costant velocity      & $\ddot{x},\ddot{y}=0$ & constant angular velocity &  $\ddot{\omega},\ddot{\alpha}=0$   \\
+        mode 2  & north acceleration      & $u(k)=a $  \\
         \hline
-        state 2  & north acceleration      & $\ddot{x}=\delta$  &  angular acceleration &  $\ddot{\omega}=\delta$ \\
+        mode 3  & south acceleration    & $u(k)=-a $   \\
         \hline
-        state 3  & south acceleration    & $\ddot{x}=-\delta$   &  angular deceleration  & $\ddot{\omega}=-\delta$ \\
+        mode 4  & east acceleration    & $u(k)=a $    \\
         \hline
-        state 4  & east acceleration    & $\ddot{y}=\delta$    & acceleration steering (CW) & $\ddot{\omega}=\delta$ \\
-        \hline
-        state 5  & west acceleration     & $\ddot{y}=-\delta$  &  acceleration steering (CCW) & $\ddot{\omega}=-\delta$ \\ [1ex]
+        mode 5  & west acceleration     & $u(k)=-a $   \\ [1ex]
         \hline
     \end{tabular}
-    \\
-
+\end{center}
     In the case of the DWPA we choosen to have 5 states: costant velocity, positive or negative acceleration
     on x direction and positive or negative deceleration on y direction.
-    \begin{tabular}{||c c c||}%[width=\columnwidth]
-        \hline
-        state 1 & costant velocity      & $\ddot{x},\ddot{y}=0$     \\
-        \hline
-        state 2  & north acceleration      & $\ddot{x}=\delta$        \\
-        \hline
-        state 3  & south acceleration    & $\ddot{x}=-\delta$        \\
-        \hline
-        state 4  & east acceleration    & $\ddot{y}=\delta$     \\
-        \hline
-        state 5  & west acceleration     & $\ddot{y}=-\delta$       \\ [1ex]
-        \hline
-    \end{tabular} The Transition matrix 
-    associated with the Markov's chain is shown below
-    \begin{equation*}
-        \begin{bmatrix}
-            0.8 & 0.025 & 0.025 & 0.025 & 0.025 //
-        \end{bmatrix}
-    \end{equation*}
+    % \begin{tabular}{||c c c||}%[width=\columnwidth]
+    %     \hline
+    %     state 1 & costant velocity      & $\ddot{x},\ddot{y}=0$     \\
+    %     \hline
+    %     state 2  & north acceleration      & $\ddot{x}=\delta$        \\
+    %     \hline
+    %     state 3  & south acceleration    & $\ddot{x}=-\delta$        \\
+    %     \hline
+    %     state 4  & east acceleration    & $\ddot{y}=\delta$     \\
+    %     \hline
+    %     state 5  & west acceleration     & $\ddot{y}=-\delta$       \\ [1ex]
+    %     \hline
+    % \end{tabular} The Transition matrix 
+    % associated with the Markov's chain is shown below
+    % \begin{equation*}
+    %     \begin{bmatrix}
+    %         0.8 & 0.025 & 0.025 & 0.025 & 0.025 //
+    %     \end{bmatrix}
+    % \end{equation*}
     The linear system describing the evolution of the state is 
@@
     \end{equation*}
-
+    \\
     It can be noticed that the matrix $G$ is a merge between the second and the fourth matrices found in the set $B(s)$ as the noise will act
     randomly in direction and magnitude at every time-step.
-
+\subsection*{Unicycle mode}
     The unycicle model has different input and state description. The input are represented by the angular acceleration of the wheel and the steering angle acceleration.
-    possible state are 5: constant angular velocity, acceleration and deceleration of the wheel and positice or negative acceleration of the steering angle.
-    The associate Markov chain for this case is
-    \begin{tabular}{||c c c c||}
+    possible modes are 5: constant angular velocity, acceleration and deceleration of the wheel and positice or negative acceleration of the steering angle.
+    \begin{center}
+        \resizebox{.99\columnwidth}{!}{ $
+        \begin{tabular}{||c||c |c |c| |}%{|width=\columnwidth|}
             \hline
-        state 1 & 6      & 87837  & 787    \\
+             Unicycle  \\
+            \hline\hline
+             Modes & & Input \\ [0.5ex]
+            \hline\hline
+            mode 1 & costant angular velocity      & $u(k)=0$    \\
             \hline
-        state 2  & 7      & 78     & 5415   \\
+            mode 2  & angular acceleration      & $u(k)=a $  \\
             \hline
-        state 3      & 545    & 778    & 7507   \\
+            mode 3  & angular deceleration    & $u(k)=-a $   \\
             \hline
-        state 4      & 545    & 18744  & 7560   \\
+            mode 4  & steer angle acceleration (CW)    & $u(k)=a $    \\
             \hline
-        state 5      & 88     & 788    & 6344   \\ [1ex]
+            mode 5  & steer angle acceleration (CCW)     & $u(k)=-a $   \\ [1ex]
             \hline
-    \end{tabular}
-    $$\begin{vmatrix}
-            0.8 & 0.025 & 0.025 & 0.025 & 0.025 //
-        \end{vmatrix}$$
-    Unycicle model instead is a Non-linear model. Thus is necessary to use a linearization in the Kalman filter implementation
+        \end{tabular} $}
+    \end{center}
+    Unycicle model instead is a Non-linear model. The  %Thus is necessary to use a linearization in the Kalman filter implementation
+    \begin{equation}
+        x(k+1)= Ax(k) + B(s)u(k) + Gw(k)
+    \end{equation}
     The matrix that represent the state of system for this case are
-    \[ X=\begin{bmatrix} x \\ y \\ \dot{x} \\ \dot{y} \\ \end{bmatrix}  A=\begin{bmatrix}
-            1 & 0 & \delta & 0      \\
-            0 & 1 & 0      & \delta \\
+    \begin{equation*}      
+     \resizebox{.99\columnwidth}{!}{ $ X=\begin{bmatrix} x \\ y \\ \theta \\ \omega \\ \end{bmatrix}  A=\begin{bmatrix}
+            1 & 0 & \delta cos(\dot{\theta}) & 0      \\
+            0 & 1 & 0      & \delta sin(\dot{\theta}) \\
             0 & 0 & 1      & 0      \\
@@
          G=\begin{bmatrix}
-            \delta^2/2 & 0          \\
-            0          & \delta^2/2 \\
-            \delta     & 0          \\
+            \delta^2/2 cos(\theta)r & 0  \\
+            \delta^2/2 sin(\theta)r & 0 \\
+            \delta r    & 0          \\
             0 & \delta     \\
         \end{bmatrix}
-    \]
+    $ } \end{equation*}
+
+    We hypothesize that the input is unknown in direction but known in magnitude. This set according to the current state at which the markov process is at the timestep.
+    This is modeled though the switch between a set of matrices $B(s)$ that change according to the chain's state $s$.
+    \begin{equation*}%[width=\columnwidth]
+        \resizebox{.99 \columnwidth}{!}{
+        $B(s)=\begin{Bmatrix}
+            \begin{bmatrix}
+                0 & 0 \\
+                0          & 0 \\
+                0     & 0 \\
+                0          & 0 \\
+            \end{bmatrix}
+            \begin{bmatrix}
+                \delta^2/2 cos(\theta)r & 0 \\
+                \delta^2/2 sin(\theta)r & 0 \\
+                \delta r    & 0 \\
+                0          & 0 \\
+            \end{bmatrix}
+            \begin{bmatrix}
+                -\delta^2/2 cos(\theta)r & 0 \\
+                -\delta^2/2 sin(\theta)r & 0 \\
+                -\delta r    & 0 \\
+                0          & 0 \\
+            \end{bmatrix}
+            \begin{bmatrix}
+                0 & 0          \\
+                0 & 0 \\
+                0 & 0          \\
+                0 & \delta     \\
+            \end{bmatrix}
+            \begin{bmatrix}
+                0 & 0          \\
+                0 & 0 \\
+                0 & 0          \\
+                0 & -\delta     \\
+            \end{bmatrix}
+        \end{Bmatrix} $ 
+        }
+    \end{equation*}
+    \\
+    Also in this case it's possible to notice that $G(s)$ is a merge of $B(s)$
+    Therefore in the EKF a linearised model is needed
+    and som
+    \begin{equation*}
+        A(k)
+    \end{equation*} 
     \subsection*{Data's simulation}
 
+    \section*{Imm and Linear Consensus}
+    In order to reach a more accurate prediction of the trajectory a IMM algorithm is implemented in the sensors's grid. The working principles 
+    involves a general knowledge or hypothesis of the model of agent's movement. Every model is used in a Kalman filter stage that use the same measurement and make
+    a prediction: the one with the smaller uncertainty is choose as the model for our agent at that timestep. A general scheme of the working principles is shown here (image?)
+    \\
+    The set of active sensors inside the grid is dynamic, as vertices keep getting added and popped. However it has to be noticed, as stated before, that no 
+     more than 4 sensors will be ON at any point of time and they will all be adjacent to each other, this let us model the graph of the active 
+     sensors as fully-connected, since the distance between them is short and they are directly linked.
+    \\
     \section*{Result}

### 2020-01-31 Functions/IMM.m
Everything Works v2
Now set up with montecarlo

@@ -53,12 +53,17 @@ for i=1:alto
     end
     % to avoid error => threshold 
     if  rcond(S(:,:,i))<1e-7
-        L(i)=0.001;
+        L(i)=0.0001;        %this does not happen anymore, better leavethe exception tho
     elseif all(eig(S(:,:,i))>1e-6)
-        L(i)=mvnpdf(dz(:,i),0,S(:,:,i));
-        if L(i)==0
-            "Likelihood=0 perchè dz troppo grande e S piccolina"
-            L(i)=0.001;
+        St=chol(S(:,:,i));
+        dzinv=dz(:,i)'/St;
+        logsqr=sum(log(diag(St)));
+        L(i)=exp(-(sum(dzinv.^2,2))/2-logsqr-2*log(2*pi)/2);
+%         L(i)=mvnpdf(dz(:,i),0,S(:,:,i)); %this causes errors cause matlab
+%         sucks
+        if L(i)<0.0001
+            %"Likelihood=0 perchè dz troppo grande e S piccolina"
+            L(i)=0.0001;
         end
     else
         "S negative definite o qualcosa che non so spiegare"

### 2020-01-31 Functions/kalman.m

@@ -18,12 +18,12 @@ function [xk1,Pk1,dz,S] = kalman(Mat,x,u,z,Pk,Q,R,caso,offset,delta,s)
     dz=z-hx(xpri,caso,offset);
     dz=aggiusta(dz);
     if norm(dz)>3
-        "dz sbagliato"
+ %       "dz sbagliato"
     end
     S=H*Ppri*H'+R;  %covariance update
     if rcond(S)<1e-8
         "S troppo piccola"
-    elseif det(S)>100
+    elseif det(S)>1000
         "S troppo grande"
     end
     W=(Ppri*H')/S;    %kalman weight

### 2020-01-31 Progetto2.m

@@ -7,14 +7,17 @@ clc; clear all; close all;
 
 caso=2;
 %delta time
-delta=0.1;
+delta=0.05;
 %at which rate do we do the consensus ?
-rate=1;
+rate=5;
 %Maximum number of iteration
 nstop=1000;
+%iterations montecarlo
+nmonte=100;
 %Plot
 videon = 0;
 ploton =0;
+plotresults=1;
 plotallsenson=0;
 plotallsensed=0;
 switch caso
@@ -60,14 +63,12 @@ switch caso
             Transmat(i,2:end)=[v2(end+3-i:end),v2(1:end+2-i)];
         end
         
-        %initial 2D position, velocity and acceleration
-        x0=zeros(nx,1);
-        x0([1,2,4])=0.5;
+        
         
         %Power spectra density of process noise
-        Q=diag([0.2,0.2]);
+        Q=diag([1,1]);
         %magnitude of acceleration
-        acc=[1;1].*1;
+        acc=[1;1].*5;
         P0=diag([1,1,0.5,0.5]);
         %
         %
@@ -102,28 +103,23 @@ switch caso
         x0(3)=0.3;
         x0(4)=pi/3;
         %radius, called like this for reasons
-        ABG=0.3;
+        ABG=0.5;
         %Power spectra density of process noise
-        Q=diag([0.01,0.01]);
+        Q=diag([0.2,0.2]);
         %magnitude of acceleration
-        acc=[1;2].*1;
+        acc=[1;2].*3;
         P0=diag([1,1,1,1]);
 end
 %state of markov chain
-% s=randi([1,ns]);
 howconfident=0.95;
 s=1;
 
 %Senosors
 range=10;
-R=diag([0.01,(2*pi/360)^2]);               %sensor covariance
+R=diag([0.1,(2*pi/180)^2]);               %sensor covariance
 
-%real state and mode
-stato=zeros(nx,10); %vector of the real state of the moving object
-mode=zeros(1,10);   %vector of the real mode of the moving object
-stato(:,1)=x0;
-mode(1)=s;
-
+rmserr=[];
+maxerr=[];
 
 %mu1 is the starting vector of probabilities for the imm
 mu1=zeros(ns,1);
@@ -135,15 +131,8 @@ for i=1:ns
     end
 end
 
-%model probabilities
-mu=zeros(ns,10);
-mu(:,1)=mu1'; %first state is constant velocity for design and we suppose we know
 
-
-
-%%
-
[…]

### 2020-02-01 Progetto2.m
Post Merging Editind
Gitkraken si è offeso e se tu fai un alto commit mi tocca rifarlo

@@ -5,15 +5,15 @@ clc; clear all; close all;
 %1-> markov chain constant speed or costant acceleration
 %2-> unicycle
 
-caso=2;
+caso=1;
 %delta time
 delta=0.05;
 %at which rate do we do the consensus ?
 rate=5;
 %Maximum number of iteration
-nstop=100;
+nstop=1000;
 %iterations montecarlo
-nmonte=10;
+nmonte=100;
 %Plot
 videon = 0;
 ploton =0;
@@ -391,11 +391,6 @@ for y=1:nmonte
             xksens=[xksens;sensors{kk,ll}.xpred];
             Pksens{i}(:,:,:)=sensors{kk,ll}.Ppred;
             muijsens=blkdiag(muijsens,sensors{kk,ll}.muij);
-
-            for a=1:5
-            senprederr{n,i,a}=norm(sensors{kk,ll}.xpred(1:2,a)-stato(1:2,n+1));
-            end
-            meansenprederr(n)=rms(senprederr{n,i});
         end
         
         %WLS can be seen as 2 linear consensus algorithms running in parallel
@@ -607,11 +602,11 @@ if plotresults==1
     ylabel('|dx| [m]')
     xlabel('Consensus number [k]')
     
-    figure(4)
-    plot(rmspos)
-    title('IMM Prediction Error Norm on Position')
-    ylabel('|dx| [m]')
-    xlabel('Consensus number [k]')
+%     figure(4)
+%     plot(rmspos)
+%     title('IMM Prediction Error Norm on Position')
+%     ylabel('|dx| [m]')
+%     xlabel('Consensus number [k]')
     
     figure(5)
     switch caso

### 2020-02-01 Progetto2.m
OK
Sensato

@@ -11,9 +11,9 @@ delta=0.05;
 %at which rate do we do the consensus ?
 rate=5;
 %Maximum number of iteration
-nstop=100;
+nstop=1000;
 %iterations montecarlo
-nmonte=10;
+nmonte=100;
 %Plot
 videon = 0;
 ploton =0;
@@ -362,7 +362,6 @@ for y=1:nmonte
         end
         %compute IMM for all the sensors that are on
         rmsimm=[];
-        maximm=0;
         for i=1:lon
             %get indices from onindices cell array
             kk=onindices{i}(1);
@@ -386,7 +385,7 @@ for y=1:nmonte
             Hmu=[Hmu;eye(ns)];
             musens=[musens,sensors{kk,ll}.mu'];
             rmsimm(end+1)=norm(sensors{kk,ll}.xmix(1:2)-stato(1:2,n+1));
-            maximm=max(maximmnocons,rmsimm(i));
+            maximmnocons=max(maximmnocons,rmsimm(i));
             xksens=[xksens;sensors{kk,ll}.xpred];
             Pksens{i}(:,:,:)=sensors{kk,ll}.Ppred;
             muijsens=blkdiag(muijsens,sensors{kk,ll}.muij);
@@ -439,7 +438,7 @@ for y=1:nmonte
                 end
             end
             meanimmnocons(end+1)=norm(stato(1:2,n+1)-statocons(1:2,ncons+1));
-            maximm=max(maximmnocons,norm(stato(1:2,n+1)-statocons(1:2,ncons+1)));
+            maximmnocons=max(maximmnocons,norm(stato(1:2,n+1)-statocons(1:2,ncons+1)));
             ncons=ncons+1;
         else
             %addpoints(curve2,statocons(1,n-1),statocons(2,n-1));
@@ -565,7 +564,7 @@ for y=1:nmonte
     maxerr(y)=max(rmspos);
     rmssenserr(y)=rms(meanerrsensed);
     maxnsenserr(y)=maxerrsens;
-    maxerrnocons(y)=maximm;
+    maxerrnocons(y)=maximmnocons;
     rmsnocons(y)=rms(meanimmnocons);
 end
 

### 2020-02-01 Progetto2.m
Latex

@@ -418,7 +418,11 @@ for y=1:nmonte
                 ll=onindices{i}(2);
                 sensors{kk,ll}.xcons=statocons(:,ncons+1);
                 sensors{kk,ll}.Pcons=Pcons(:,:,ncons+1);
+                if rate > 3
                 sensors{kk,ll}.mu=mucons(:,ncons+1);
+                else
+                sensors{kk,ll}.mu=sensors{kk,ll}.mu';
+                end
                 %             sensors{kk,ll}.mu=sensors{kk,ll}.mu';
                 %pick xcons of all on sensors
                 %
@@ -600,12 +604,6 @@ if plotresults==1
     title('Consensus IMM Error Norm on Position')
     ylabel('|dx| [m]')
     xlabel('Consensus number [k]')
-    
-%     figure(4)
-%     plot(rmspos)
-%     title('IMM Prediction Error Norm on Position')
-%     ylabel('|dx| [m]')
-%     xlabel('Consensus number [k]')
     
     figure(5)
     switch caso

### 2020-02-01 Latex/exp.tex

@@
 \usepackage{geometry}
+\usepackage{bbm}
 %\usepackage{multicol}
@@
 
-\title{Imm algorithm implementation for tracking}
+\title{Report and analysis on implementation of IMM algorithm for multiple-model dynamics tracking}
 \author{
@@
 The purpouse of this project is to analyze and evaluate the performance of an IMM algorithm's implementation in a distributed environment for
-agent's tracking. The agent switches between linked models of movement by the means of a Markov chain. The goal is evaluate the best trade-off
-between error on estimated position and real position and number of messagesses involved in the tracking.
+multiple-model dynamics tracking as the tracked agent switches between linked models of movement by the means of a Markov chain. The goal 
+is to evaluate the best trade-off between error on estimated position and real position and number of messages regarding consensus involved in the tracking.
 
@@
     \justify
-    NON CAPISCO COSA VUOI DIRE, IN QUALSIASI CASO QUA AGGIUNGI CHE PARLIAMO DI FILTRI DA DISCRETE-DISCRETE
+    The general objective of this report is to provide a robust tracking that works in a distributed way, for some object that can move 
+    in a number of different ways (modelized as a set of dynamical systems $\mathbbm{M}$). The environment in which this object moves is 
+    one of a large room that contains multiple sensors that can talk to each other.
     \\
-    Tracking an object with a switching dynamic require proper algorithms and filters.Retriving physical data with
-    observations it's not enough in the case of Markov processes that switch between modes and we need to
-    , models achiving the best-fit to our data is needed in order to make a prediction and estimate
-    with reduced uncertainty. Here comes to play a major role the IMM algorithm (Interacting Multiple Models): The data
-    from sensor are combined with different dynamical models through the algorithm...
     \subsection*{Sensor's model}

### 2020-02-01 Latex/exp.tex
Images and Graph
Giusto per

@@
     \justify
-    The general objective of this report is to provide a robust tracking that works in a distributed way, for some object that can move 
+    The general objective of this report is to provide a robust tracking that works in a distributed manner for some object that can move 
     in a number of different ways (modelized as a set of dynamical systems $\mathbbm{M}$). The environment in which this object moves is 
@@
     \subsection*{Sensor's model}
-    The sensors chosen are radars measuring the relative polar cordinates at which the agent is collocated at the timestep, and
-    are disposed as a uniform grid. In order to simulate the real workings of a sensor, range of measuremnt has been limited to the distance
+    The sensors chosen are radars measuring the polar cordinates relative to themselves at which the agent is collocated at the timestep, and
+    are disposed in a uniform square grid. In order to simulate the real workings of a sensor, range of measuremnt has been limited to the distance
     between one sensor and the following one in any direction of the grid, as soon as the agent exceed the imposed maxiumum distance from the sensor,
     the device will stop sensing.
-    This property of the sensor grid, coupled by its geometry, ensures that no more than 4 sensors can measure the agent position at the time,
-    so it made sense to let sensor switch between 3 different states named ON, OFF and IDLE. This can be justified as a way to make the system
+    This property of the sensor grid, coupled by its geometry, ensures that no more than 4 sensors can measure the agent position at any time,
+    so it made sense to let the sensors switch between 3 different states named ON, OFF and IDLE. This can be justified as a way to make the system
     more power efficient and to avoid useless data stream towards sensors that aren't currently in range and sensing.
-    The sensor is modeled as a state machine as shown.
+    The sensor is modeled as a state machine as shown in figure \ref{fig:statemachine}
     \\
@@
         \caption{State machine sensor}
-        \label{fig:galaxy}
+        \label{fig:statemachine}
     \end{figure}
     \\
-The functions and operations that the sensors can do are:
+Sensors in different states differ between each other by the actions that are allowed in the state they are currently in.
+\\
+Here we enumerate such allowed actions:
 \begin{itemize}
-    \item InRange() : function that verify the presence of the target in its working area 
-    \item CanSense : messagge sent by a sensor switching from Idle to On triggered by a positive result from InRange() function
-    \item CantSense : message sent by a sensor switching from On to Idle triggered by a negative result from InRange() function
+    \item ON: at each time-step checks if it is still in range with the function inRange(), takes a measurement, computes the IMM algorithm and 
+             at a tunable rate computes the consensus with the other nearby ON sensors. If it's not in range anymore then turns IDLE.
+    \item IDLE : checks if it is now in range with the function inRange(), if it is then initialize itself with the data from nearby sensors 
+                that are ON. If it recieves a CantSense signal, it checks if at least one of its neighboors is still ON, else it turns OFF itself.
+    \item OFF : does nothing but waits for a CanSense signal sent by a neighboor and turns IDLE in the case it has received one (this means that 
+                a nearby sensor has turned ON).
 \end{itemize}
-    Every sensor accordingly with its state can perform some action and send information following the rules listed below:
+    So sensors can communicate with the devices adjacent to them (Neighboorhood), as represented in the figure \ref{fig:neighboors} below, 
+    and exchange with them signals named CanSense and CantSense which state respectively whenever the agent gets in or goes out of the 
+    communicating sensor's range. This check is done through the function inRange() that also serves as a switch between the states of the 
+    sensor, as already shown by the figure \ref{fig:statemachine} above.
+    The messages that the sensors exchange with their Neighboorhood are
 \begin{itemize} 
-    \item On: participate in the measurement process while InRange() stay with positive result. 
-    It retrieve data on position and perform a IMM algorithm and with a selected rate perform a linear consensus calculation 
-    \item Idle : perform a InRange() verification each timestep to verify if it have to switch in On. If triggered to On 
-    initialization starts using data from the others sensors as a starting point.
-    if it receive a CantSense from all the neighboors it turn itself off.
-    \item Off : no measurment function or involvement. Triggered to Idle when receive one CanSense by the neighboors
+    \item CanSense : message sent by a sensor switching from IDLE to ON triggered by a positive result from InRange() function
+    \item CantSense : message sent by a sensor switching from ON to IDLE triggered by a negative result from InRange() function
 \end{itemize}
-
-    % \begin{center}
-    %     \begin{adjustbox}{max width=0.45\textwidth}
-    %     \begin{tabular}{||c| c| c |c||}
-    %         \hline
-    %           & On & 3 Idle & Off \\ [0.5ex]
-    %         \hline\hline
-    %         InRange()==      & True      & False  & False    \\
-    %         \hline
-    %         Message sent      & CanSense      & CantSense     & X   \\
-    %         \hline
-    %         Functions      & measurement    & ready to switch to On    & X   \\
-    %         \hline
-
-    %         \hline
-    %     \end{tabular}
-    % \end{adjustbox}
-    % \end{center}
-    So sensors can communicate with the devices adjacent to them (Neighboorhood), as represented in the figure below, and exchange with them signals named CanSense and CantSense
-    which state respectively whenever the agent gets in or goes out of the communicating sensor's range. This check is done through the 
-    function inRange() that also serves as a switch between the states of the sensor, as already shown by the figure above.
-    \\
     \begin{figure}[h!]
@@
         \includegraphics[width=0.2\textwidth]{Immagini/2sensor.png}
-        \caption{Neighboors for a sensors are the one immediately adiacent. The purples ones represent the neighboors of green sensor}
-        \label{fig:galaxy}
+        \caption{The neighboors of a sensors are the one immediately adiacent, represented as purple in this image}
+        \label{fig:neighboors}
     \end{figure}
-    \\
-    Defing the range of the sensors equal to their spacing on the grid it follows, depending on agent's position, only a maximum of 4 sensors can be turned on. 
-    It follows a figure that show the idea with a 4-sensors grid
+    By defing the range of the sensors equal to their spacing on the grid it follows that only a maximum of 4 sensors can be turned on. 
+    This fact is shown in the following picture that illustrates the different cases
     \begin{figure}[h!]
@@
         \caption{}
-        \label{fig:galaxy}
+        \label{fig:number}
     \end{figure}
     \begin{itemize}
-        \item blue : 1 sensors On 
-        \item yellow : 2 sensors On 
-        \item orange : 3 sensors On 
-        \item red : 4 sensors On 
+        \item blue : 1 sensors ON, happens only at the conrners of the grid
+        \item yellow : 2 sensors ON 
+        \item orange : 3 sensors ON 
+        \item red : 4 sensors ON 
     \end{itemize}
-    % Different state can receive and send different messagesses. A sensor in On state has the moving
-    % object in his range and send a CanSense to the nearby and when trackin moving away from the operating range send a CantSense turning itself to Idle.
-    % Sensors that receive a CanSense and are not already On turn in Idle state; during the Idle state sensors check
-    % if object appears in range sensors turn to On and send a CanSense, if nothing trigger the range it send to the nearby a CantSense signal.
-    % A sensor that is in Idle and during the information exchange receive only CantSense from the nearby turn itself Off and stop to check if somenthing is in range and
-    % can be turned again to Idle via a CanSense. This scheme implies that a sensors can never switch to On from Off except for the initialization step.
-    % \\
-    Whenever the target is in range of a sensor, the device takes a measurement at each timestep.
-    The model we choose for our measurement device is a radar and as such the measurement function 
-    $z(k)=h(x(k))+v(k)$ associated with it is the cartesian to polar transformation, as shown below
+    Whenever the target is in range of a sensor at given timestep, the device takes a measurement.
+    The model choosen for our sensor is a Radar, and as such the non-linear measurement function
+     associated to it is the cartesian to polar transformation at timestep $k$, as shown below
     \begin{align*}
@@
         &\begin{bmatrix}
-            \rho(k)\\ \alpha(k)
+            \rho(k)\\ \theta (k)(k)
         \end{bmatrix}=  
         \begin{bmatrix}
-            \sqrt{x(k)^2+y(k)^2}\\ atan2(y(k)/x(k))
+            \sqrt{x_{1}(k)^2+x_{2}(k)^2}\\ atan2(x_{2}(1)/x_{1}(k))
         \end{bmatrix} +
@@
     \end{align*}
-    where $h(x)$ is the polar to cartesian cordinates transform and $v(k)$ is the noise associated to the measurement's operation.
-
+    where $h(x)$ is the polar to cartesian cordinates transform that takes in $x(k)$ that is the state (of which the first 2 elements are the cartesian
+    cordinates relative to the sensor), $z(k)$ is the measure and $v(k)$ is the noise associated to the measurement's operation. The measurement noise $w(k)$ is associated 
+    to a diagonal power spectral density matrix $R$.
     \begin{equation*}
-        \begin{bmatrix}
-            \rho\\ \alpha
-        \end{bmatrix}=  
-        \begin{bmatrix}
-            x^2+y^2\\ atan2(y/x)
+        R=\begin{bmatrix}
+            \sigma^{2}_{\rho}&0\\
+            0&\sigma^{2}_{\theta (k)}
         \end{bmatrix}
     \end{equation*}
-   for sake of use in the extended Kalman filter, a linearization of $h(x)$ must be performed.
-   The LS problem associate becomes
+    \\
+   The matrix $H^{k}=(\nabla_{x} h(x))_{|x=x(k)}$ used in the linearized model with $v(k)=0$, necessary in the IMM filter at each timestep $k$,
+   computes to 
     \begin{equation*}
-       x^{SL}(k)=arg min(Z^{k}-h(x)W(Z^{k}-h(x))^{T})= argmin J(x,k)
+        H^{k}= \begin{bmatrix}
+            \frac{x_{1}}{\sqrt{x_{1}^{2}+x_{2}^{2}}} & \frac{x_{2}}{\sqrt{x_{1}^{2}+x_{2}^{2}}}& 0 \dots\\
+            \frac{-x_{2}}{x_{1}^{2}+x_{2}^{2}}  & \frac{x_{1}}{x_{1}^{2}+x_{2}^{2}}& 0 \dots\\
+        \end{bmatrix}_{|x(k)}
     \end{equation*}
-   and we have to found 
-   \begin{equation*}
-     \frac{dJ(x,k)}{dx}=0
-\end{equation*}
-After a bit of management we can compute 
-\begin{equation*}
-    J(x,k)=Z^{k}
-\end{equation*}
-        and than it follows that
-        \begin{equation*}
-            \frac{dJ(x,k)}{dx}=-H(x)^{T}W(Z^{K}-h(x))=0
-        \end{equation*}
-        where $H(x)=\frac{dh(x)}{dx}$ So in this particular case:
-    \begin{equation}
-        H= \begin{bmatrix}
-            \frac{x}{(x^{2}+y^{2})^{1/2}} & \frac{y}{(x^{2}+y^{2})^{1/2}}& 0& 0 \\
-            \frac{-y}{(x^{2}+y^{2})}  & \frac{x}{(x^{2}+y^{2})}& 0& 0 \\
-        \end{bmatrix}
-    \end{equation}
+    Where $0\dots$ is a vector of zeroes for all the other states that do not influence the measurement function.
+
     \section*{Model used}
-    To models the movement of the target has been employed two models: The discrete Wienerprocess acceleration model (DWPA) (reference) and the unicycle model
-    Both are Markov process.
-    \subsection*{ Discrete Wiener Process Acceleration Model}
-    The Discrete Wienerprocess acceleration model choose are described by 5 different mode
-    \\
-    % \begin{tabular}{ |c|c|c|c|c|c| }
-    % \multicolumn{6}{|c|}{Models} \\
-    % \begin{tabular}{||c |c  | c  |c|c|c|c|c c c c c||}%{|width=\columnwidth|}
-    %     \hline
-    %      & DPWA && Unycicle \\
-    %     \hline
-    %          & Modes & Input & Modes & Inputs\\ [0.5ex]
-    %     \hline\hline
-    %     state 1 & costant velocity      & $\ddot{x},\ddot{y}=0$ & constant angular velocity &  $\ddot{\omega},\ddot{\alpha}=0$   \\
-    %     \hline
-    %     state 2  & north acceleration      & $\ddot{x}=\delta$  &  angular acceleration &  $\ddot{\omega}=\delta$ \\
-    %     \hline
-    %     state 3  & south acceleration    & $\ddot{x}=-\delta$   &  angular deceleration  & $\ddot{\omega}=-\delta$ \\
-    %     \hline
-    %     state 4  & east acceleration    & $\ddot{y}=\delta$    & acceleration steering (CW) & $\ddot{\omega}=\delta$ \\
-    %     \hline
-    %     state 5  & west acceleration     & $\ddot{y}=-\delta$  &  acceleration steering (CCW) & $\ddot{\omega}=-\delta$ \\ [1ex]
-    %     \hline
-    % \end{tabular}
+    As mentioned already, the agent we want to track has a variable-model dynamic that can switch between different elements in a set 
+    of models that we denote as $\mathbbm{M}$. We will consider 2 families of such sets that we will call: Random Accellerated Walk $\mathbbm{M}_{1}$ 
+    and Random Unicycle Turning $\mathbbm{M}_{2}$. Every element of said families is a discrete Markovian process, as all are influenced by a white 
+    noise on their inputs.
+    \subsection*{Random Accellerated Walk}
+    For the Random Accellerated Walk we consider the set $\mathbbm{M}_{1}$ to be 5 elements large. 
+    Here the elements are described
     \begin{center}
-    \begin{tabular}{||c||c |c |c| |}%{|width=\columnwidth|}
+        \begin{tabular}{||c||c |c |}%{|width=\columnwidth|}
             \hline
-         DPWA  \\
+             Random Walk  \\
             \hline\hline
-         Modes & Description & Input \\ [0.5ex]
+             Mode & Behaviour  \\ [0.5ex]
             \hline\hline
-        mode 1 & costant velocity      & $u(k)=0$    \\
+            Mode 1 & Constant Speed \\
             \hline
-        mode 2  & north acceleration      & $u(k)=a $  \\
+            Mode 2  & Positive Acceleration in x  \\
             \hline
-        mode 3  & south acceleration    & $u(k)=-a $   \\
+            Mode 3  & Negative Acceleration in x  \\
             \hline
-        mode 4  & east acceleration    & $u(k)=a $    \\
+            Mode 4  & Positive Acceleration in y  \\
             \hline
-        mode 5  & west acceleration     & $u(k)=-a $   \\ [1ex]
+            Mode 5  & Negative Acceleration in y   \\ [1ex]
             \hline
@@
     \end{center}
-    In the case of the DWPA we choosen to have 5 states: costant velocity, positive or negative acceleration
-    on x direction and positive or negative deceleration on y direction.
-    % \begin{tabular}{||c c c||}%[width=\columnwidth]
-    %     \hline
-    %     state 1 & costant velocity      & $\ddot{x},\ddot{y}=0$     \\
-    %     \hline
-    %     state 2  & north acceleration      & $\ddot{x}=\delta$        \\
-    %     \hline
-    %     state 3  & south acceleration    & $\ddot{x}=-\delta$        \\
-    %     \hline
-    %     state 4  & east acceleration    & $\ddot{y}=\delta$     \\
-    %     \hline
-    %     state 5  & west acceleration     & $\ddot{y}=-\delta$       \\ [1ex]
-    %     \hline
-    % \end{tabular} The Transition matrix 
-    % associated with the Markov's chain is shown below
-    % \begin{equation*}
-    %     \begin{bmatrix}
-    %         0.8 & 0.025 & 0.025 & 0.025 & 0.025 //
-    %     \end{bmatrix}
-    % \end{equation*}
-    The linear system describing the evolution of the state is 
+
+    Every member of the set has the same structure 
+    to describe their dynamics, in state space this their shared linear model
     \begin{equation}
-        x(k+1)= Ax(k) + B(s)u(k) + Gw(k)
+        x(k+1)= Ax(k) + B(s)u + Gw(k)
     \end{equation}
-    Where $x(k)$ is the state at the current timestep, $u(t)$ is the input and $w(k)$ is the process noise.
-    In this case the state is a vector of the cartesian cordinates and their relative speed, while the input 
-    is the acceleration which the noise will influence. 
-    State,state and noise matrix associate to the DWPA has shown below:
+    where $A$ is the state matrix, $B(s)$ the input matrix function of the mode/index $s$ that indicates the element picked of $\mathbbm{M}_{1}$, 
+    $u$ is the input that stays constant at all timesteps $k$ and in all modes $s$, $G$ the noise matrix and $w(k)$ the process noise at timestep
+     $k$ with associated $Q_{1}$ diagonal power spectral density matrix.
+     \begin{equation*}
+        Q_{1}=\begin{bmatrix}
+            \sigma^{2}_{a_{x}}&0\\
+            0&\sigma^{2}_{a_{y}}
+        \end{bmatrix}
+    \end{equation*}
+     Below we show the constant matrices and how the state is structured
     \[ x=\begin{bmatrix} x \\ y \\ \dot{x} \\ \dot{y} \\ \end{bmatrix}  A=\begin{bmatrix}
@@
     G=\begin{bmatrix}
-            \delta^2/2 & 0          \\
-            0          & \delta^2/2 \\
+        \frac{\delta^{2}}{2} & 0          \\
+        0          & \frac{\delta^{2}}{2} \\
         \delta     & 0          \\
@@
 \]
-    With $\delta$ time step of the simulation.
-    \\
-    We hypothesize that the input is unknown in direction but known in magnitude. This set according to the current state at which the markov process is at the timestep.
-    This is modeled though the switch between a set of matrices $B(s)$ that change according to the chain's state $s$.
+Where $x$ and $y$ are the cartesian coordinates in the absolute reference frame and $\delta$ is the duration of each timestep $k$.
+To model different behaviours of the agent/elements in the set $\mathbbm{M}_{1}$ we use switching matrices $B(s)$ while keeping the vector $u$ 
+constant. The input $u$ here is a vector of acceleration in $x$ and $y$ that the noise $w(k)$ will influence.
+We hypothesize that the input is always known in magnitude and constant. Here is the set $B(s)$ of input matrices.
     \begin{equation*}%[width=\columnwidth]
@@
             \begin{bmatrix}
-                \delta^2/2 & 0 \\
+                \frac{\delta^{2}}{2} & 0 \\
                 0          & 0 \\
@@
             \begin{bmatrix}
-                -\delta^2/2 & 0 \\
+                -\frac{\delta^{2}}{2} & 0 \\
                 0          & 0 \\
@@
                 0 & 0          \\
-                0 & \delta^2/2 \\
+                0 & \frac{\delta^{2}}{2} \\
                 0 & 0          \\
@@
                 0 & 0          \\
-                0 & -\delta^2/2 \\
+                0 & -\frac{\delta^{2}}{2} \\
                 0 & 0          \\
@@
     \\
-    It can be noticed that the matrix $G$ is a merge between the second and the fourth matrices found in the set $B(s)$ as the noise will act
-    randomly in direction and magnitude at every time-step.
-\subsection*{Unicycle mode}
-    The unycicle model has different input and state description. The input are represented by the angular acceleration of the wheel and the steering angle acceleration.
-    possible modes are 5: constant angular velocity, acceleration and deceleration of the wheel and positice or negative acceleration of the steering angle.
+    It is to note that the matrix $G$ is a merge between the second and the fourth matrices found in the set $B(s)$ as we hyphotesized that 
+     the noise will act randomly in direction and magnitude at every time-step.
+\\
+The jump between behaviours is modeled by a Markov chain that has a constant stochastic transition matrix $T$.
+In the simulations the matrix is fixed at
+\begin{equation*}
+    T=\begin{bmatrix}
+        p_{0}&p&p&p&p\\
+        b&q_{0}&2q&q&2q\\
+        b&2q&q_{0}&2q&q\\
+        b&q&2q&q_{0}&2q\\
+        b&2q&q&2q&q_{0}\\
+    \end{bmatrix}
+\end{equation*}
+Where $p_{0}$, $q_{0}$ and $b$ are fixed while $p$ and $q$ are computed so that the matrix is stochastic.
+\subsection*{Random Unicycle Turning}
+In the case of the Random Unicycle Turning we also consider the set $\mathbbm{M}_{2}$ to be 5 elements large, but the states are changed.
     \begin{center}
-        \resizebox{.99\columnwidth}{!}{ $
-        \begin{tabular}{||c||c |c |c| |}%{|width=\columnwidth|}
+        \begin{tabular}{||c||c |c |}%{|width=\columnwidth|}
             \hline
-             Unicycle  \\
+             Unycicle  \\
             \hline\hline
-             Modes & & Input \\ [0.5ex]
+            Mode & Behaviour  \\ [0.5ex]
             \hline\hline
-            mode 1 & costant angular velocity      & $u(k)=0$    \\
+            Mode 1 & Constant Tangential Velocity and Angle \\
             \hline
-            mode 2  & angular acceleration      & $u(k)=a $  \\
+            Mode 2  & Positive Angular Wheel Acceleration  \\
             \hline
-            mode 3  & angular deceleration    & $u(k)=-a $   \\
+            Mode 3  & Negative Angular Wheel Acceleration \\
             \hline
-            mode 4  & steer angle acceleration (CW)    & $u(k)=a $    \\
+            Mode 4  & Positive Yaw Rate  \\
             \hline
-            mode 5  & steer angle acceleration (CCW)     & $u(k)=-a $   \\ [1ex]
+            Mode 5  & Negative Yaw Rate   \\ [1ex]
             \hline
-        \end{tabular} $}
+        \end{tabular}
     \end{center}
-    Unycicle model instead is a Non-linear model. The  %Thus is necessary to use a linearization in the Kalman filter implementation
+Here all the elements in the set $\mathbbm{M}_{2}$ are non-linear models $x(k+1)=f(x(k),u(k),w(k),s)$, but if we can still organize them in such a way
     \begin{equation}
-        x(k+1)= Ax(k) + B(s)u(k) + Gw(k)
+        x(k+1)= A(x(k))x(k) + B(s,x(k))u(k) + G(x(k))w(k)
     \end{equation}
-    The matrix that represent the state of system for this case are
+By defining
     \begin{equation*}      
-     \resizebox{.99\columnwidth}{!}{ $ X=\begin{bmatrix} x \\ y \\ \theta \\ \omega \\ \end{bmatrix}  A=\begin{bmatrix}
-            1 & 0 & \delta cos(\dot{\theta}) & 0      \\
-            0 & 1 & 0      & \delta sin(\dot{\theta}) \\
+     \resizebox{.99\columnwidth}{!}{ $ x=\begin{bmatrix} x(k) \\ y(k) \\ v_{t}(k) \\ \alpha(k) \\ \end{bmatrix}  
+        A(x(k))=\begin{bmatrix}
+            1 & 0 & \delta cos(\dot{\alpha (k)}) & 0      \\
+            0 & 1 & 0      & \delta sin(\dot{\alpha (k)}) \\
             0 & 0 & 1      & 0      \\
@@
         \end{bmatrix}
-         G=\begin{bmatrix}
-            \delta^2/2 cos(\theta)r & 0  \\
-            \delta^2/2 sin(\theta)r & 0 \\
+         G(x(k))=\begin{bmatrix}
+            \frac{\delta^{2}}{2} cos(\alpha (k))r & 0  \\
+            \frac{\delta^{2}}{2} sin(\alpha (k))r & 0 \\
             \delta r    & 0          \\
@@
     $ } \end{equation*}
-
-    We hypothesize that the input is unknown in direction but known in magnitude. This set according to the current state at which the markov process is at the timestep.
-    This is modeled though the switch between a set of matrices $B(s)$ that change according to the chain's state $s$.
+and 
 \begin{equation*}%[width=\columnwidth]
     \resizebox{.99 \columnwidth}{!}{
-        $B(s)=\begin{Bmatrix}
+    $B(s,k)=\begin{Bmatrix}
         \begin{bmatrix}
@@
         \begin{bmatrix}
-                \delta^2/2 cos(\theta)r & 0 \\
-                \delta^2/2 sin(\theta)r & 0 \\
+            \frac{\delta^{2}}{2} cos(\alpha (k))r & 0 \\
+            \frac{\delta^{2}}{2} sin(\alpha (k))r & 0 \\
             \delta r    & 0 \\
@@
         \begin{bmatrix}
-                -\delta^2/2 cos(\theta)r & 0 \\
-                -\delta^2/2 sin(\theta)r & 0 \\
+            -\frac{\delta^{2}}{2} cos(\alpha (k))r & 0 \\
+            -\frac{\delta^{2}}{2} sin(\alpha (k))r & 0 \\
             -\delta r    & 0 \\
@@
 \end{equation*}
+where $\delta$ is the length of the timestep $k$, $r$ the radius of the unicycle's wheel, $x(k)$ and $y(k)$ absolute cartesian cordinates of the unicycle, 
+$v_{t}(k)$ tangential velocity and $\alpha$ yaw angle.
+The input $u$ is a vector of the angular acceleration of the wheel $\omega$ and yaw rate $\Omega$ with
+\begin{equation*}
+    Q_{2}=\begin{bmatrix}
+        \sigma^{2}_{\omega}&0\\
+        0&\sigma^{2}_{\Omega}
+    \end{bmatrix}
+\end{equation*}
+Just as in $\mathbbm{M}_{1}$, $G$ is build on the hypothesis that the process noise $w(k)$ influences both inputs at any timestep $k$.
 \\
-    Also in this case it's possible to notice that $G(s)$ is a merge of $B(s)$
-    Therefore in the EKF a linearised model is needed
-    and som
+The stochastic transition matrix in this case will be 
 \begin{equation*}
-        A(k)
+    T=\begin{bmatrix}
+        p_{0}&p&p&p&p\\
+        q&q_{0}&q&0&0\\
+        q&q&q_{0}&0&0\\
+        q&0&0&q_{0}&q\\
+        q&0&0&q&q_{0}
+    \end{bmatrix}
 \end{equation*}
-    \subsection*{Data's simulation}
-
-    \section*{Imm and Linear Consensus}
+where $p_{0}$ and $q_{0}$ are fixed while $p$ and $q$ are computed to make the matrix stochastic.
+\section*{IMM}
     In order to reach a more accurate prediction of the trajectory a IMM algorithm is implemented in the sensors's grid. The working principles 
@@
     \\
+
+    \section*{Consensus}
     The set of active sensors inside the grid is dynamic, as vertices keep getting added and popped. However it has to be noticed, as stated before, that no 

### 2020-02-01 Progetto2.m

@@ -5,11 +5,11 @@ clc; clear all; close all;
 %1-> markov chain constant speed or costant acceleration
 %2-> unicycle
 
-caso=1;
+caso=2;
 %delta time
 delta=0.05;
 %at which rate do we do the consensus ?
-rate=2;
+rate=20;
 %Maximum number of iteration
 nstop=1000;
 %iterations montecarlo
@@ -116,7 +116,7 @@ s=1;
 
 %Senosors
 range=10;
-R=diag([0.01,(2*pi/360)^2]);               %sensor covariance
+R=diag([0.1,(2*pi/180)^2]);               %sensor covariance
 
 rmserr=[];
 maxerr=[];
@@ -488,7 +488,7 @@ for y=1:nmonte
             
             addpoints(curve1,stato(1,n),stato(2,n))
             drawnow
-            if plotallsenson==1g
+            if plotallsenson==1
                 if lon>=1
                     addpoints(curvesens1,xconsallsensor{n,1}(1),xconsallsensor{n,1}(2));
                     drawnow

### 2020-02-01 Progetto2.m
All Images here
and completed the google drive table

@@ -105,7 +105,7 @@ switch caso
         %radius, called like this for reasons
         ABG=0.5;
         %Power spectra density of process noise
-        Q=diag([0.2,0.2]);
+        Q=diag([1,1]);
         %magnitude of acceleration
         acc=[1;2].*3;
         P0=diag([1,1,1,1]);
@@ -626,7 +626,7 @@ fig5.WindowState = 'maximized';
             title('Consensus IMM Error Norm on Tangential Speed')
             ylabel('|dv| [m/s]')
             xlabel('Consensus number [k]')
-            figure(6)
+           fig6= figure(6)
 fig6.WindowState = 'maximized';
             plot(rmsang);
             title('Consensus IMM Error Norm on Yaw Angle')
@@ -685,6 +685,7 @@ maxmaxnocons=max(maxerrnocons)
 
 saveas(fig4,'errpos.png')
 saveas(fig5,'errorspeed.png')
+saveas(fig6,'erroryaw.png')
 saveas(fig8,'maxIMM.png')
 saveas(fig3,'errnocons.png')
 saveas(fig11,'maxnocons.png')

### 2020-02-01 Latex/draft.tex
Auto stash before merge of "no_speed_jumps" and "origin/no_speed_jumps"

\documentclass[twocolumn]{article}
\usepackage[utf8]{inputenc}
\usepackage{amsmath} % Advanced math typesetting
\usepackage[utf8]{inputenc} % Unicode support (Umlauts etc.)
\usepackage[english]{babel} % Change hyphenation rules
\usepackage{hyperref} % Add a link to your document
\usepackage{graphicx} % Add pictures to your document
\usepackage{listings} % Source code formatting and highlighting
\usepackage{bookmark}
\usepackage{natbib}
\usepackage{geometry}
\usepackage{bbm}
%\usepackage{multicol}
\usepackage{fancyhdr}
\usepackage[document]{ragged2e}
\usepackage{adjustbox}
\usepackage{subcaption}
% \pagestyle{fancy}
% \fancyhf{}
% \fancyhead[LE,RO]{Overleaf}
% \fancyhead[RE,LO]{Guides and tutorials}
% \fancyfoot[CE,CO]{\leftmark}
% \fancyfoot[LE,RO]{\thepage}
\graphicspath{ {Immagini/} }
%C:\Users\erikz\OneDrive\Desktop\PaioPaio2\IMM-Sensors-Network\Latex\Immagini
\geometry{
 a4paper,
 total={170mm,257mm},
 left=20mm,
 top=20mm,
 }

\title{Report and analysis on implementation of IMM algorithm for multiple-model dynamics tracking}
\author{
Paiola Lorenzo 198573

Zanolli Erik 198852}
\date{January 2020}

\begin{document}

\maketitle

\section*{Introduction}
\justify
The purpouse of this project is to analyze and evaluate the performance of an IMM algorithm's implementation in a distributed environment for
multiple-model dynamics tracking as the tracked agent switches between linked models of movement by the means of a Markov chain. The goal 
is to evaluate the best trade-off between error on estimated position and real position and number of messages regarding consensus involved in the tracking.

    \section*{Setting}
    \justify
    The general objective of this report is to provide a robust tracking that works in a distributed manner for some object that can move 
    in a number of different ways (modelized as a set of dynamical systems $\mathbbm{M}$). The environment in which this object moves is 
    one of a large room that contains multiple sensors that can talk to each other.
    \\
    \subsection*{Sensor's model}
    The sensors chosen are radars measuring the polar cordinates relative to themselves at which the agent is collocated at the timestep, and
    are disposed in a uniform square grid. In order to simulate the real workings of a sensor, range of measuremnt has been limited to the distance
    between one sensor and the following one in any direction of the grid, as soon as the agent exceed the imposed maxiumum distance from the sensor,
    the device will stop sensing.
    This property of the sensor grid, coupled by its geometry, ensures that no more than 4 sensors can measure the agent position at any time,
    so it made sense to let the sensors switch between 3 different states named ON, OFF and IDLE. This can be justified as a way to make the system
    more power efficient and to avoid useless data stream towards sensors that aren't currently in range and sensing.
    The sensor is modeled as a state machine as shown in figure \ref{fig:statemachine}
    \\
    \begin{figure}[h!]
        \centering
        \includegraphics[width=\columnwidth]{sensor_state_machine.png}
        \caption{State machine sensor}
        \label{fig:statemachine}
    \end{figure}
    \\
Sensors in different states differ between each other by the actions that are allowed in the state they are currently in.
\\
Here we enumerate such allowed actions:
\begin{itemize}
    \item ON: at each time-step checks if it is still in range with the function inRange(), takes a measurement, computes the IMM algorithm and 
             at a tunable rate computes the consensus with the other nearby ON sensors. If it's not in range anymore then turns IDLE.
    \item IDLE : checks if it is now in range with the function inRange(), if it is then initialize itself with the data from nearby sensors 
                that are ON. If it recieves a CantSense signal, it checks if at least one of its neighboors is still ON, else it turns OFF itself.
    \item OFF : does nothing but waits for a CanSense signal sent by a neighboor and turns IDLE in the case it has received one (this means that 
                a nearby sensor has turned ON).
\end{itemize}
    So sensors can communicate with the devices adjacent to them (Neighboorhood), as represented in the figure \ref{fig:neighboors} below, 
    and exchange with them signals named CanSense and CantSense which state respectively whenever the agent gets in or goes out of the 
    communicating sensor's range. This check is done through the function inRange() that also serves as a switch between the states of the 
    sensor, as already shown by the figure \ref{fig:statemachine} above.
    The messages that the sensors exchange with their Neighboorhood are
\begin{itemize} 
    \item CanSense : message sent by a sensor switching from IDLE to ON triggered by a positive result from InRange() function
    \item CantSense : message sent by a sensor switching from ON to IDLE triggered by a negative result from InRange() function
\end{itemize}
    \begin{figure}[h!]
        \centering
        \includegraphics[width=0.2\textwidth]{Immagini/2sensor.png}
        \caption{The neighboors of a sensors are the one immediately adiacent, represented as purple in this image}
        \label{fig:neighboors}
    \end{figure}
    By defing the range of the sensors equal to their spacing on the grid it follows that only a maximum of 4 sensors can be turned on. 
    This fact is shown in the following picture that illustrates the different cases
    \begin{figure}[h!]
        \centering
        \includegraphics[width=0.23\textwidth]{Immagini/4sensor.png}
        \caption{}
        \label{fig:number}
    \end{figure}
    \begin{itemize}
        \item blue : 1 sensors ON, happens only at the conrners of the grid
        \item yellow : 2 sensors ON 
        \item orange : 3 sensors ON 
        \item red : 4 sensors ON 
    \end{itemize}
    Whenever the target is in range of a sensor at given timestep, the device takes a measurement.
    The model choosen for our sensor is a Radar, and as such the non-linear measurement function
     associated to it is the cartesian to polar transformation at timestep $k$, as shown below
    \begin{align*}
        &z(k)=h(x(k))+v(k)\\
        &\begin{bmatrix}
            \rho(k)\\ \theta (k)(k)
        \end{bmatrix}=  
        \begin{bmatrix}
            \sqrt{x_{1}(k)^2+x_{2}(k)^2}\\ atan2(x_{2}(1)/x_{1}(k))
        \end{bmatrix} +
        \begin{bmatrix}
            v_{1}(k)\\v_{2}(k)
        \end{bmatrix}
    \end{align*}
    where $h(x)$ is the polar to cartesian cordinates transform that takes in $x(k)$ that is the state (of which the first 2 elements are the cartesian
    cordinates relative to the sensor), $z(k)$ is the measure and $v(k)$ is the noise associated to the measurement's operation. The measurement noise $w(k)$ is associated 
    to a diagonal power spectral density matrix $R$.
    \begin{equation*}
        R=\begin{bmatrix}
            \sigma^{2}_{\rho}&0\\
            0&\sigma^{2}_{\theta (k)}
        \end{bmatrix}
    \end{equation*}
    \\
   The matrix $H^{k}=(\nabla_{x} h(x))_{|x=x(k)}$ used in the linearized model with $v(k)=0$, necessary in the IMM filter at each timestep $k$,
   computes to 
    \begin{equation*}
        H^{k}= \begin{bmatrix}
            \frac{x_{1}}{\sqrt{x_{1}^{2}+x_{2}^{2}}} & \frac{x_{2}}{\sqrt{x_{1}^{2}+x_{2}^{2}}}& 0 \dots\\
            \frac{-x_{2}}{x_{1}^{2}+x_{2}^{2}}  & \frac{x_{1}}{x_{1}^{2}+x_{2}^{2}}& 0 \dots\\
        \end{bmatrix}_{|x(k)}
    \end{equation*}
    Where $0\dots$ is a vector of zeroes for all the other states that do not influence the measurement function.

    \section*{Model used}
    As mentioned already, the agent we want to track has a variable-model dynamic that can switch between different elements in a set 
    of models that we denote as $\mathbbm{M}$. We will consider 2 families of such sets that we will call: Random Accellerated Walk $\mathbbm{M}_{1}$ 
    and Random Unicycle Turning $\mathbbm{M}_{2}$. Every element of said families is a discrete Markovian process, as all are influenced by a white 
    noise on their inputs.
    \subsection*{Random Accellerated Walk}
    For the Random Accellerated Walk we consider the set $\mathbbm{M}_{1}$ to be 5 elements large. 
    Here the elements are described
    \begin{center}
        \begin{tabular}{||c||c |c |}%{|width=\columnwidth|}
            \hline
             Random Walk  \\
            \hline\hline
             Mode & Behaviour  \\ [0.5ex]
            \hline\hline
            Mode 1 & Constant Speed \\
            \hline
            Mode 2  & Positive Acceleration in x  \\
            \hline
            Mode 3  & Negative Acceleration in x  \\
            \hline
            Mode 4  & Positive Acceleration in y  \\
            \hline
            Mode 5  & Negative Acceleration in y   \\ [1ex]
            \hline
        \end{tabular}
    \end{center}

    Every member of the set has the same structure 
    to describe their dynamics, in state space this their shared linear model
    \begin{equation}
        x(k+1)= Ax(k) + B(s_{k})u + Gw(k)
    \end{equation}
    where $A$ is the state matrix, $B(s_{k})$ the input matrix function of the mode/index $s_{k}$ that indicates the element picked of $\mathbbm{M}_{1}$, 
    $u$ is the input that stays constant at all timesteps $k$ and in all modes $s_{k}$, $G$ the noise matrix and $w(k)$ the process noise at timestep
     $k$ with associated $Q_{1}$ diagonal power spectral density matrix.
     \begin{equation*}
        Q_{1}=\begin{bmatrix}
            \sigma^{2}_{a_{x}}&0\\
            0&\sigma^{2}_{a_{y}}
        \end{bmatrix}
    \end{equation*}
     Below we show the constant matrices and how the state is structured
    \[ x=\begin{bmatrix} x \\ y \\ \dot{x} \\ \dot{y} \\ \end{bmatrix}  A=\begin{bmatrix}
        1 & 0 & \delta & 0      \\
        0 & 1 & 0      & \delta \\
        0 & 0 & 1      & 0      \\
        0 & 0 & 0      & 1      \\
    \end{bmatrix}
    G=\begin{bmatrix}
        \frac{\delta^{2}}{2} & 0          \\
        0          & \frac{\delta^{2}}{2} \\
        \delta     & 0          \\
        0          & \delta     \\
    \end{bmatrix}
\]
Where $x$ and $y$ are the cartesian coordinates in the absolute reference frame and $\delta$ is the duration of each timestep $k$.
To model different behaviours of the agent/elements in the set $\mathbbm{M}_{1}$ we use switching matrices $B(s_{k})$ while keeping the vector $u$ 
constant. The input $u$ here is a vector of acceleration in $x$ and $y$ that the noise $w(k)$ will influence.
We hypothesize that the input is always known in magnitude and constant. Here is the set $B(s_{k})$ of input matrices.
    \begin{equation*}%[width=\columnwidth]
        \resizebox{.9 \columnwidth}{!}{
        $B(s_{k})=\begin{Bmatrix}
            \begin{bmatrix}
                0 & 0 \\
                0          & 0 \\
                0     & 0 \\
                0          & 0 \\
            \end{bmatrix}
            \begin{bmatrix}
                \frac{\delta^{2}}{2} & 0 \\
                0          & 0 \\
                \delta     & 0 \\
                0          & 0 \\
            \end{bmatrix}
            \begin{bmatrix}
                -\frac{\delta^{2}}{2} & 0 \\
                0          & 0 \\
                -\delta     & 0 \\
                0          & 0 \\
            \end{bmatrix}
            \begin{bmatrix}
                0 & 0          \\
                0 & \frac{\delta^{2}}{2} \\
                0 & 0          \\
                0 & \delta     \\
            \end{bmatrix}
            \begin{bmatrix}
                0 & 0          \\
                0 & -\frac{\delta^{2}}{2} \\
                0 & 0          \\
                0 & -\delta     \\
            \end{bmatrix}
        \end{Bmatrix} $ 
        }
    \end{equation*}
    \\
    It is to note that the matrix $G$ is a merge between the second and the fourth matrices found in the set $B(s_{k})$ as we hyphotesized that 
     the noise will act randomly in direction and magnitude at every time-step.
\\
The jump between behaviours is modeled by a Markov chain that has a constant stochastic transition matrix $T$.
In the simulations the matrix is fixed at
\begin{equation*}
    T=\begin{bmatrix}
        p_{0}&p&p&p&p\\
        b&q_{0}&2q&q&2q\\
        b&2q&q_{0}&2q&q\\
        b&q&2q&q_{0}&2q\\
        b&2q&q&2q&q_{0}\\
    \end{bmatrix}
\end{equation*}
Where $p_{0}$, $q_{0}$ and $b$ are fixed while $p$ and $q$ are computed so that the matrix is stochastic.
\subsection*{Random Unicycle Turning}
In the case of the Random Unicycle Turning we also consider the set $\mathbbm{M}_{2}$ to be 5 elements large, but the states are changed.
    \begin{center}
        \begin{tabular}{||c||c |c |}%{|width=\columnwidth|}
            \hline
             Unycicle  \\
            \hline\hline
            Mode & Behaviour  \\ [0.5ex]
            \hline\hline
            Mode 1 & Constant Tangential Velocity and Angle \\
            \hline
            Mode 2  & Positive Angular Wheel Acceleration  \\
            \hline
            Mode 3  & Negative Angular Wheel Acceleration \\
            \hline
            Mode 4  & Positive Yaw Rate  \\
            \hline
            Mode 5  & Negative Yaw Rate   \\ [1ex]
            \hline
        \end{tabular}
    \end{center}
Here all the elements in the set $\mathbbm{M}_{2}$ are non-linear models $x(k+1)=f(x(k),u(k),w(k),s_{k})$, but if we can still organize them in such a way
    \begin{equation}
        x(k+1)= A(x(k))x(k) + B(s_{k},x(k))u(k) + G(x(k))w(k)
    \end{equation}
By defining
    \begin{equation*}      
     \resizebox{.99\columnwidth}{!}{ $ x=\begin{bmatrix} x(k) \\ y(k) \\ v_{t}(k) \\ \alpha(k) \\ \end{bmatrix}  
        A(x(k))=\begin{bmatrix}
            1 & 0 & \delta cos(\dot{\alpha (k)}) & 0      \\
            0 & 1 & 0      & \delta sin(\dot{\alpha (k)}) \\
            0 & 0 & 1      & 0      \\
            0 & 0 & 0      & 1      \\
        \end{bmatrix}
         G(x(k))=\begin{bmatrix}
            \frac{\delta^{2}}{2} cos(\alpha (k))r & 0  \\
            \frac{\delta^{2}}{2} sin(\alpha (k))r & 0 \\
            \delta r    & 0          \\
            0 & \delta     \\
        \end{bmatrix}
    $ } \end{equation*}
and 
\begin{equation*}%[width=\columnwidth]
    \resizebox{.99 \columnwidth}{!}{
    $B(s_{k},k)=\begin{Bmatrix}
        \begin{bmatrix}
            0 & 0 \\
            0          & 0 \\
            0     & 0 \\
            0          & 0 \\
        \end{bmatrix}
        \begin{bmatrix}
            \frac{\delta^{2}}{2} cos(\alpha (k))r & 0 \\
            \frac{\delta^{2}}{2} sin(\alpha (k))r & 0 \\
            \delta r    & 0 \\
            0          & 0 \\
        \end{bmatrix}
        \begin{bmatrix}
            -\frac{\delta^{2}}{2} cos(\alpha (k))r & 0 \\
            -\frac{\delta^{2}}{2} sin(\alpha (k))r & 0 \\
            -\delta r    & 0 \\
            0          & 0 \\
        \end{bmatrix}
        \begin{bmatrix}
            0 & 0          \\
            0 & 0 \\
            0 & 0          \\
            0 & \delta     \\
        \end{bmatrix}
        \begin{bmatrix}
            0 & 0          \\
            0 & 0 \\
            0 & 0          \\
            0 & -\delta     \\
        \end{bmatrix}
    \end{Bmatrix} $ 
    }
\end{equation*}
where $\delta$ is the length of the timestep $k$, $r$ the radius of the unicycle's wheel, $x(k)$ and $y(k)$ absolute cartesian cordinates of the unicycle, 
$v_{t}(k)$ tangential velocity and $\alpha$ yaw angle.
The input $u$ is a vector of the angular acceleration of the wheel $\omega$ and yaw rate $\Omega$ with
\begin{equation*}
    Q_{2}=\begin{bmatrix}
        \sigma^{2}_{\omega}&0\\
        0&\sigma^{2}_{\Omega}
    \end{bmatrix}
\end{equation*}
Just as in $\mathbbm{M}_{1}$, $G$ is build on the hypothesis that the process noise $w(k)$ influences both inputs at any timestep $k$.
\\
The stochastic transition matrix in this case will be 
\begin{equation*}
    T=\begin{bmatrix}
        p_{0}&p&p&p&p\\
        q&q_{0}&q&0&0\\
        q&q&q_{0}&0&0\\
        q&0&0&q_{0}&q\\
        q&0&0&q&q_{0}
    \end{bmatrix}
\end{equation*}
where $p_{0}$ and $q_{0}$ are fixed while $p$ and $q$ are computed to make the matrix stochastic.

\section*{IMM}
Being the agent's dynamic costantly switching between the models in the set choosen, a single kalman filter won't give us acceptable results while 
tracking and we have to rely on the Interacting Multiple Models algorithm (IMM). In essence the algorithm let various estimation filters work in parallel
 (EKF in our case), and outputs a mixture of the filters' estimate based on the probability of each of the models used in the filter to be correct.
 \\
The hyphotheses we have to make in order to use the IMM are that the sequence of the true mode at timestep $k$, $s_{k}$, is a Markovian process, i.e. the mode evolves to the 
memoryless random process $P\{s_{k+1}^{j}|s_{k}^{i}\}\pi_{ji}$ $\forall\ j,i$ and that the model set $\mathbbm{M}$ is the correct one and is time-invariant.
In our case those hypotheses are known to be true.
\\
 The design parameters of the IMM are the model set $\mathbbm{M}$, the process and measurement noise spectral density matrices $Q$ and $R$, the initial 
 state and covariance $\hat{x}_{0|0}$ and $P_{0|0}$ and the transition matrix $T$ containing all the $\pi_{ji}$.
 The algorithm can be subdivided in 4 subsections, :
 \begin{itemize}
     \item Model Conditioned reinitialization $\forall m_{i},m_{j}\in \mathbbm{M}$
     \begin{align*}
                &\mu^{(i)}_{k|k-1}=\sum_{j}\pi_{ji}\mu^{(j)}_{k-1}\\
                &\mu^{(j|i)}_{k-1}=\pi_{ji}\mu^{(j)}_{k-1}/\mu^{(i)}_{k|k-1}\\
                &\bar{x}^{(i)}_{k-1|k-1}=\sum_{j}\hat{x}^{(j)}_{k-1|k-1}\mu^{j|i}_{k-1}\\
                &\bar{P}^{(i)}_{k-1|k-1}=\sum_{j}[P^{(j)}_{k-1|k-1}+(\bar{x}^{(i)}_{k-1|k-1}\\
                &-\hat{x}^{(j)}_{k-1|k-1})(\bar{x}^{(i)}_{k-1|k-1}-\hat{x}^{(j)}_{k-1|k-1})']\mu_{k-1}^{j|i}
    \end{align*}
        Here we take all the model probabilities computed at the previous step and mix them together with the 
        transition matrix to then use the result to combine both the previous step state and covariance estimation.
     \item Model Conditioned filtering, in our case EKF $\forall m_{i}\in \mathbbm{M}$
        \begin{align*}
            &\\
            &\\
            &\\
            &\\
            &\\
            &\\
        \end{align*}
     \item Model Probability update $\forall m_{i},m_{j}\in \mathbbm{M}$
     \item Estimate fusion
 \end{itemize}
\section*{Consensus}
    Right having computed the IMM's estimate for every ON sensor, we use a consensus algorithm to try to lower the 
    estimation error even more. The consensus will happen at a variable rate and only between the ON sensors.
    The set of active sensors inside the grid is dynamic, as vertices keep getting added and popped. However no
     more than 4 sensors will be ON at any point of time, see \ref{fig:number}, and they will all be adjacent to each other, 
     this let us model the graph of the active sensors as fully-connected, since the distance between them is short 
     and we imagine them to be directly linked.
     \\
     This modeling let us use a Weighted Least Squared estimation of the best measure between all the ON sensors, since this operation 
     gives us a consensus in a single timestep, which is what we need with both a dynamic graph and a dynamic system.
    So for our system we get 
    \begin{align*}
        &P_{cons}(k)=(H^{k^{T}}P^{k^{-1}}H^{k})^{-1}\\
        &x_{cons}(k)=P_{cons}H^{k^{T}}P^{k^{-1}}Z^{k}
    \end{align*}
    where $P^{k}$ is the block diagonal matrix built with all the covariance matrices from the IMM's output, $Z^{k}$ 
    is the measurement vector built by stacking all the state predictions from the IMM's output and $H^{k}$ is the matrix build by 
    stacking all the $H_{i}$ for $z_{i}=H_{i}x+\epsilon_{i}$, luckily in our case all $H_{i}$ are identity matrices.\\
     It has to be noted that the WLS can be seen as 2 parallel linear consensus algorithms, running one on top of the other.
    \\
    We also tentatively tried to use the same consensus algorithm on the prediction vector of model probabilities $\mu_{k}$ using 
    the collection of all $\mu^{j|i}_{k-1}$ in matrix form instead of the covariance matrix for the weighting matrix, but 
    the resulting matrix was too close to singularity and the simulation was having numerical problems so this road 
    was abandoned, instead we just computed the mean between the various $\mu_{k}$. 
    \section*{Result}
    The performance evaluation of the system are evaluted by computing the RMS of the predicted trajectory eith the respect to the actual one
    choosing different rate of performind the WSL. The final result are listed in the table below
    \begin{center}
        \begin{tabular}{ |c||c|c|c|  }
            \hline
            \multicolumn{4}{|c|}{consensus20} \\
            \hline
            IMM  & Mean of Imm's mean    & Max of Imm's mean     & max of IMM's max  \\ [0.5ex]
            \hline
            R1,Q1           & 0.1078                & 0.2578                & 0.3960                 \\
                \hline
                R1,Q2           & 0.1094                & 0.2694             & 0.4671                      \\
                \hline
                R2,Q1           & 0.0505                &  0.1210           & 0.2491                         \\
                \hline
                R2,Q2           & 0.0514                & 0.1313             & 0.2549                   \\
            \hline
            \multicolumn{4}{|c|}{consensus20} \\
            \hline
            W/o Cons  & Mean of Imm's mean    & Max of Imm's mean     & max of IMM's max  \\ 
            \hline
            R1,Q1           & 0.1609                & 0.1762                & 2.0937                 \\
            \hline
            R1,Q2           & 0.1625                & 0.1907             & 1.0347                     \\
            \hline
            R2,Q1           & 0.0799               &  0.0877           & 0.4310                         \\
            \hline
            R2,Q2           & 0.0815                & 0.0926            & 0.4445                   \\
        \hline
           \end{tabular}
        \end{center}

    \subsection*{}

\end{document}

### 2020-02-02 Latex/draft.tex
gdsgds

@@
     \begin{itemize}
-        \item blue : 1 sensors ON, happens only at the conrners of the grid
+        \item blue : 1 sensors ON
         \item yellow : 2 sensors ON 
@@
     \end{itemize}
+    Note that the blue case happens only at the borders and corners of the grid.
+    \\
     Whenever the target is in range of a sensor at given timestep, the device takes a measurement.
@@
 \section*{IMM}
-Being the agent's dynamic costantly switching between the models in the set choosen, a single kalman filter won't give us acceptable results while 
+Being the agent's dynamic costantly switching between the models in the set chosen, a single kalman filter won't give us acceptable results while 
 tracking and we have to rely on the Interacting Multiple Models algorithm (IMM). In essence the algorithm let various estimation filters work in parallel
@@
 The hyphotheses we have to make in order to use the IMM are that the sequence of the true mode at timestep $k$, $s_{k}$, is a Markovian process, i.e. the mode evolves to the 
-memoryless random process $P\{s_{k+1}^{j}|s_{k}^{i}\}\pi_{ji}$ $\forall\ j,i$ and that the model set $\mathbbm{M}$ is the correct one and is time-invariant.
+memoryless random process $P\{s_{k+1}^{(j)}|s_{k}^{(j)}\}\pi_{ji}$ $\forall\ j,i$ and that the model set $\mathbbm{M}$ is the correct one and is time-invariant.
 In our case those hypotheses are known to be true.
 \\
- The design parameters of the IMM are the model set $\mathbbm{M}$, the process and measurement noise spectral density matrices $Q$ and $R$, the initial 
- state and covariance $\hat{x}_{0|0}$ and $P_{0|0}$ and the transition matrix $T$ containing all the $\pi_{ji}$.
+ The design parameters of the IMM are the model set $\mathbbm{M}$, the process and measurement noise spectral density 
+ matrices $Q$ and $R$ for each model and sensor, the initial state and covariance $\hat{x}_{0|0}$ and $P_{0|0}$ 
+ and the transition matrix $T$ containing all the $\pi_{ji}$.
  The algorithm can be subdivided in 4 subsections, :
@@
                 &\bar{P}^{(i)}_{k-1|k-1}=\sum_{j}[P^{(j)}_{k-1|k-1}+(\bar{x}^{(i)}_{k-1|k-1}\\
-                &-\hat{x}^{(j)}_{k-1|k-1})(\bar{x}^{(i)}_{k-1|k-1}-\hat{x}^{(j)}_{k-1|k-1})']\mu_{k-1}^{j|i}
+                &-\hat{x}^{(j)}_{k-1|k-1})(\bar{x}^{(i)}_{k-1|k-1}-\hat{x}^{(j)}_{k-1|k-1})^{T}]\mu_{k-1}^{j|i}
     \end{align*}
-        Here we take all the model probabilities computed at the previous step and mix them together with the 
+        Here we take all the output model probabilities computed at the previous iteration of the IMM and mix them together with the 
         transition matrix to then use the result to combine both the previous step state and covariance estimation.
@@
         \begin{align*}
-            &\\
-            &\\
-            &\\
-            &\\
-            &\\
-            &\\
+            &\hat{x}^{(i)}_{k|k-1}=f^{(i)}_{k}(\bar{x}^{(i)}_{k-1|k-1})\\
+            &P^{(i)}_{k|k-1}=F^{(i)}_{k-1}\bar{P}^{(i)}_{k-1|k-1}F^{(i)^{T}}_{k-1}+G^{(i)}_{k-1}Q_{k-1}^{(i)}G^{(i)^{T}}_{k-1}\\
+            &\bar{z}^{(i)}_{k}=z_{k}-h(\hat{x}^{(i)}_{k|k-1})\\
+            &S^{(i)}_{k}=H^{(i)}_{k}P^{(i)}_{k|k-1}H^{(i)^{T}}_{k}+R^{(i)}_{k}\\
+            &W^{(i)}_{k}=P^{(i)}_{k|k-1}H^{(i)^{T}}_{k}S^{(i)^{-1}}_{k}\\
+            &\hat{x}^{(i)}_{k|k}=\hat{x}^{(i)}_{k|k-1}+W^{(i)}_{k}\bar{z}^{(i)}_{k}\\
+            &P^{(i)}_{k|k}=P^{(i)}_{k|k-1}-W^{(i)}_{k}S^{(i)}_{k}W^{(i)^{T}}_{k}
         \end{align*}
      \item Model Probability update $\forall m_{i},m_{j}\in \mathbbm{M}$
+        \begin{align*}
+            &L^{(i)}_{k}=\mathcal{N}(\bar{z}^{(i)}_{k},0,S^{(i)}_{k})\\
+            &\mu^{(i)}_{k}=\frac{\mu^{(i)}_{k|k-1}L^{(i)}_{k}}{\sum_{j}\mu^{(j)}_{k|k-1}L^{(j)}_{k}}
+        \end{align*}
      \item Estimate fusion
+        \begin{align*}
+         &\hat{x}_{k|k}=\sum_{i}x^{(i)}_{k|k}\mu^{(i)}_{k}\\
+         &P_{k|k}=\sum_{i}[P^{(i)}_{k|k}+(\hat{x}_{k|k}-\hat{x}^{(i)}_{k|k})(\hat{x}_{k|k}-\hat{x}^{(i)}_{k|k})^{T}]\mu_{k}^{i}
+     \end{align*}
  \end{itemize}

### 2020-02-02 Latex/draft.tex
Finished I guess

@@
 The purpouse of this project is to analyze and evaluate the performance of an IMM algorithm's implementation in a distributed environment for
-multiple-model dynamics tracking as the tracked agent switches between linked models of movement by the means of a Markov chain. The goal 
+multiple-model dynamics tracking. The tracked agent switches between linked models of movement by the means of a Markov chain. The goal
 is to evaluate the best trade-off between error on estimated position and real position and number of messages regarding consensus involved in the tracking.
@@
 \\
-    \subsection*{Sensor's model}
+\section*{Sensor's model}
+\label{sensor}
 The sensors chosen are radars measuring the polar cordinates relative to themselves at which the agent is collocated at the timestep, and
@@
 \begin{align*}
-        &z(k)=h(x(k))+v(k)\\
-        &\begin{bmatrix}
-            \rho(k)\\ \theta (k)(k)
+     & z(k)=h(x(k))+v(k)          \\
+     & \begin{bmatrix}
+        \rho(k) \\ \theta (k)(k)
     \end{bmatrix}=
     \begin{bmatrix}
-            \sqrt{x_{1}(k)^2+x_{2}(k)^2}\\ atan2(x_{2}(1)/x_{1}(k))
+        \sqrt{x_{1}(k)^2+x_{2}(k)^2} \\ atan2(x_{2}(1)/x_{1}(k))
     \end{bmatrix} +
     \begin{bmatrix}
-            v_{1}(k)\\v_{2}(k)
+        v_{1}(k) \\v_{2}(k)
     \end{bmatrix}
@@
     R=\begin{bmatrix}
-            \sigma^{2}_{\rho}&0\\
-            0&\sigma^{2}_{\theta (k)}
+        \sigma^{2}_{\rho} & 0                       \\
+        0                 & \sigma^{2}_{\theta (k)}
     \end{bmatrix}
@@
     H^{k}= \begin{bmatrix}
-            \frac{x_{1}}{\sqrt{x_{1}^{2}+x_{2}^{2}}} & \frac{x_{2}}{\sqrt{x_{1}^{2}+x_{2}^{2}}}& 0 \dots\\
-            \frac{-x_{2}}{x_{1}^{2}+x_{2}^{2}}  & \frac{x_{1}}{x_{1}^{2}+x_{2}^{2}}& 0 \dots\\
-        \end{bmatrix}_{|x(k)}
+        \frac{x_{1}}{\sqrt{x_{1}^{2}+x_{2}^{2}}} & \frac{x_{2}}{\sqrt{x_{1}^{2}+x_{2}^{2}}} & 0 \dots \\
+        \frac{-x_{2}}{x_{1}^{2}+x_{2}^{2}}       & \frac{x_{1}}{x_{1}^{2}+x_{2}^{2}}        & 0 \dots \\
+    \end{bmatrix}_{|x=x(k)}
 \end{equation*}
@@
 As mentioned already, the agent we want to track has a variable-model dynamic that can switch between different elements in a set
-    of models that we denote as $\mathbbm{M}$. We will consider 2 families of such sets that we will call: Random Accellerated Walk $\mathbbm{M}_{1}$ 
+of models that we denote as $\mathbbm{M}$. We will consider 2 families of such sets that we will call: Random Accelerated Walk $\mathbbm{M}_{1}$
 and Random Unicycle Turning $\mathbbm{M}_{2}$. Every element of said families is a discrete Markovian process, as all are influenced by a white
 noise on their inputs.
-    \subsection*{Random Accellerated Walk}
-    For the Random Accellerated Walk we consider the set $\mathbbm{M}_{1}$ to be 5 elements large. 
+\subsection*{Random Accelerated Walk}
+For the Random Accelerated Walk we consider the set $\mathbbm{M}_{1}$ to be 5 elements large.
 Here the elements are described
@@
 \end{equation}
-    where $A$ is the state matrix, $B(s_{k})$ the input matrix function of the mode/index $s_{k}$ that indicates the element picked of $\mathbbm{M}_{1}$, 
+where $A$ is the state matrix, $B(s_{k})$ the input matrix function of the mode/index $s_{k}$ that indicates the element picked of $\mathbbm{M}_{1}$ at timestep $k$,
 $u$ is the input that stays constant at all timesteps $k$ and in all modes $s_{k}$, $G$ the noise matrix and $w(k)$ the process noise at timestep
@@
     Q_{1}=\begin{bmatrix}
-            \sigma^{2}_{a_{x}}&0\\
-            0&\sigma^{2}_{a_{y}}
+        \sigma^{2}_{a_{x}} & 0                  \\
+        0                  & \sigma^{2}_{a_{y}}
     \end{bmatrix}
@@
     T=\begin{bmatrix}
-        p_{0}&p&p&p&p\\
-        b&q_{0}&2q&q&2q\\
-        b&2q&q_{0}&2q&q\\
-        b&q&2q&q_{0}&2q\\
-        b&2q&q&2q&q_{0}\\
+        p_{0} & p     & p     & p     & p     \\
+        b     & q_{0} & 2q    & q     & 2q    \\
+        b     & 2q    & q_{0} & 2q    & q     \\
+        b     & q     & 2q    & q_{0} & 2q    \\
+        b     & 2q    & q     & 2q    & q_{0} \\
     \end{bmatrix}
@@
 Here all the elements in the set $\mathbbm{M}_{2}$ are non-linear models $x(k+1)=f(x(k),u(k),w(k),s_{k})$, but if we can still organize them in such a way
-    \begin{equation}
+\begin{equation*}
     x(k+1)= A(x(k))x(k) + B(s_{k},x(k))u(k) + G(x(k))w(k)
-    \end{equation}
+\end{equation*}
 By defining
@@
     Q_{2}=\begin{bmatrix}
-        \sigma^{2}_{\omega}&0\\
-        0&\sigma^{2}_{\Omega}
+        \sigma^{2}_{\omega} & 0                   \\
+        0                   & \sigma^{2}_{\Omega}
     \end{bmatrix}
@@
     T=\begin{bmatrix}
-        p_{0}&p&p&p&p\\
-        q&q_{0}&q&0&0\\
-        q&q&q_{0}&0&0\\
-        q&0&0&q_{0}&q\\
-        q&0&0&q&q_{0}
+        p_{0} & p     & p     & p     & p     \\
+        q     & q_{0} & q     & 0     & 0     \\
+        q     & q     & q_{0} & 0     & 0     \\
+        q     & 0     & 0     & q_{0} & q     \\
+        q     & 0     & 0     & q     & q_{0}
     \end{bmatrix}
@@
 \section*{IMM}
-Being the agent's dynamic costantly switching between the models in the set chosen, a single kalman filter won't give us acceptable results while 
+Being the agent's dynamic costantly switching between the models in the set chosen, a single Kalman filter won't give us acceptable results while
 tracking and we have to rely on the Interacting Multiple Models algorithm (IMM). In essence the algorithm let various estimation filters work in parallel
@@
 and the transition matrix $T$ containing all the $\pi_{ji}$.
+\\
+Following is a short recapof the algorithm, to see it in much more detail refer to %\cite%
+\\
 The algorithm can be subdivided in 4 subsections, :
@@
           \begin{align*}
-                &\mu^{(i)}_{k|k-1}=\sum_{j}\pi_{ji}\mu^{(j)}_{k-1}\\
-                &\mu^{(j|i)}_{k-1}=\pi_{ji}\mu^{(j)}_{k-1}/\mu^{(i)}_{k|k-1}\\
-                &\bar{x}^{(i)}_{k-1|k-1}=\sum_{j}\hat{x}^{(j)}_{k-1|k-1}\mu^{j|i}_{k-1}\\
-                &\bar{P}^{(i)}_{k-1|k-1}=\sum_{j}[P^{(j)}_{k-1|k-1}+(\bar{x}^{(i)}_{k-1|k-1}\\
-                &-\hat{x}^{(j)}_{k-1|k-1})(\bar{x}^{(i)}_{k-1|k-1}-\hat{x}^{(j)}_{k-1|k-1})^{T}]\mu_{k-1}^{j|i}
+               & \mu^{(i)}_{k|k-1}=\sum_{j}\pi_{ji}\mu^{(j)}_{k-1}                                              \\
+               & \mu^{(j|i)}_{k-1}=\pi_{ji}\mu^{(j)}_{k-1}/\mu^{(i)}_{k|k-1}                                    \\
+               & \bar{x}^{(i)}_{k-1|k-1}=\sum_{j}\hat{x}^{(j)}_{k-1|k-1}\mu^{j|i}_{k-1}                         \\
+               & \bar{P}^{(i)}_{k-1|k-1}=\sum_{j}[P^{(j)}_{k-1|k-1}+(\bar{x}^{(i)}_{k-1|k-1}                    \\
+               & -\hat{x}^{(j)}_{k-1|k-1})(\bar{x}^{(i)}_{k-1|k-1}-\hat{x}^{(j)}_{k-1|k-1})^{T}]\mu_{k-1}^{j|i}
           \end{align*}
           Here we take all the output model probabilities computed at the previous iteration of the IMM and mix them together with the
-        transition matrix to then use the result to combine both the previous step state and covariance estimation.
-     \item Model Conditioned filtering, in our case EKF $\forall m_{i}\in \mathbbm{M}$
+          transition matrix to then use the result to combine both the previous step state and covariance estimation. It is to 
+          notice that the transpose of the matrix formed by the collection of $\mu^{(j|i)}_{k-1}$ is stochastic, this makes sense
+          since it works as a normalized transition matrix while computing $\bar{P}^{(i)}_{k-1|k-1}$ and $\bar{x}^{(i)}_{k-1|k-1}$.
+    \item Model Conditioned filtering $\forall m_{i}\in \mathbbm{M}$
           \begin{align*}
-            &\hat{x}^{(i)}_{k|k-1}=f^{(i)}_{k}(\bar{x}^{(i)}_{k-1|k-1})\\
-            &P^{(i)}_{k|k-1}=F^{(i)}_{k-1}\bar{P}^{(i)}_{k-1|k-1}F^{(i)^{T}}_{k-1}+G^{(i)}_{k-1}Q_{k-1}^{(i)}G^{(i)^{T}}_{k-1}\\
-            &\bar{z}^{(i)}_{k}=z_{k}-h(\hat{x}^{(i)}_{k|k-1})\\
-            &S^{(i)}_{k}=H^{(i)}_{k}P^{(i)}_{k|k-1}H^{(i)^{T}}_{k}+R^{(i)}_{k}\\
-            &W^{(i)}_{k}=P^{(i)}_{k|k-1}H^{(i)^{T}}_{k}S^{(i)^{-1}}_{k}\\
-            &\hat{x}^{(i)}_{k|k}=\hat{x}^{(i)}_{k|k-1}+W^{(i)}_{k}\bar{z}^{(i)}_{k}\\
-            &P^{(i)}_{k|k}=P^{(i)}_{k|k-1}-W^{(i)}_{k}S^{(i)}_{k}W^{(i)^{T}}_{k}
+               & \hat{x}^{(i)}_{k|k-1}=f^{(i)}_{k}(\bar{x}^{(i)}_{k-1|k-1},u)                                                        \\
+               & P^{(i)}_{k|k-1}=F^{(i)}_{k-1}\bar{P}^{(i)}_{k-1|k-1}F^{(i)^{T}}_{k-1}+G^{(i)}_{k-1}Q_{k-1}^{(i)}G^{(i)^{T}}_{k-1} \\
+               & \bar{z}^{(i)}_{k}=z_{k}-h(\hat{x}^{(i)}_{k|k-1})                                                                  \\
+               & S^{(i)}_{k}=H^{(i)}_{k}P^{(i)}_{k|k-1}H^{(i)^{T}}_{k}+R^{(i)}_{k}                                                 \\
+               & W^{(i)}_{k}=P^{(i)}_{k|k-1}H^{(i)^{T}}_{k}S^{(i)^{-1}}_{k}                                                        \\
+               & \hat{x}^{(i)}_{k|k}=\hat{x}^{(i)}_{k|k-1}+W^{(i)}_{k}\bar{z}^{(i)}_{k}                                            \\
+               & P^{(i)}_{k|k}=P^{(i)}_{k|k-1}-W^{(i)}_{k}S^{(i)}_{k}W^{(i)^{T}}_{k}
           \end{align*}
+          This part of the algorithm is the one that includes all the estimation filters running in parallel. In the case 
+          of $\mathbbm{M}_{1}$ we use a Kalman filter with a non-linear $h(x)$, so $f^{(i)}_{k}(x,u)$ is just the linear model 
+          $(i)$ inside $\mathbbm{M}_{1}$ while $F^{(i)}_{k-1}$ is $A$ and $G^{(i)}_{k-1}$ is $G$ specified in the model. In 
+          $\mathbbm{M}_{2}$ case an Extended Kalman Filter is used since $f^{(i)}_{k}(x,u)$ is non-linear for every model $(i)$, 
+          so here $F^{(i)}_{k-1}$ is the Jacobian of the non-linear function without noise evaluated in $\bar{x}^{(i)}_{k-1|k-1},\ u$ while 
+          $G^{(i)}_{k-1}$ is $\nabla_{w}f^{(i)}_{k}(x,u)$ evaluated in the same point with noise$=0$. Both power spectral density 
+          matrices $Q$ and $R$ are constant by assumption. The matrix $H^{(i)}_{k}$ will be model $(i)$ agnostic, computed 
+          as already discussed in section \ref{sensor} and evaluated in $\hat{x}^{(i)}_{k|k-1}$ (each different sensor will 
+          calculate its relative position from that coordinate).
     \item Model Probability update $\forall m_{i},m_{j}\in \mathbbm{M}$
           \begin{align*}
-            &L^{(i)}_{k}=\mathcal{N}(\bar{z}^{(i)}_{k},0,S^{(i)}_{k})\\
-            &\mu^{(i)}_{k}=\frac{\mu^{(i)}_{k|k-1}L^{(i)}_{k}}{\sum_{j}\mu^{(j)}_{k|k-1}L^{(j)}_{k}}
+               & L^{(i)}_{k}=\mathcal{N}(\bar{z}^{(i)}_{k},0,S^{(i)}_{k})                                \\
+               & \mu^{(i)}_{k}=\frac{\mu^{(i)}_{k|k-1}L^{(i)}_{k}}{\sum_{j}\mu^{(j)}_{k|k-1}L^{(j)}_{k}}
           \end{align*}
+          Here we compute what is the actual probability of the model $m_{i}\in\mathbbm{M}$ to have guided the dynamic of 
+          our agent at timestep $k$. To do so we assume that the the probability distribution of the error $\bar{z}_{k}$ should be 
+          a Gaussian with $0$ mean and as covariance the innovation covariance $S^{(i)}_{k}$ given by the filter $(i)$ at timestep
+           $k$, and we compute the $L^{(i)}_{k}$ probability density function in $\bar{z}^{(i)}_{k}$. Using this result we re-normalize the previously 
+           computed $\mu^{(i)}_{k|k-1}$ to give us the output vector of model probabilities $\mu_{k}$.
+           \\
+           In this step a lower bound on the likelihood is implemented since a likelihood vector of $0$ breaks the algorithm.
     \item Estimate fusion
           \begin{align*}
-         &\hat{x}_{k|k}=\sum_{i}x^{(i)}_{k|k}\mu^{(i)}_{k}\\
-         &P_{k|k}=\sum_{i}[P^{(i)}_{k|k}+(\hat{x}_{k|k}-\hat{x}^{(i)}_{k|k})(\hat{x}_{k|k}-\hat{x}^{(i)}_{k|k})^{T}]\mu_{k}^{i}
+               & \hat{x}_{k|k}=\sum_{i}x^{(i)}_{k|k}\mu^{(i)}_{k}                                                                      \\
+               & P_{k|k}=\sum_{i}[P^{(i)}_{k|k}+(\hat{x}_{k|k}-\hat{x}^{(i)}_{k|k})(\hat{x}_{k|k}-\hat{x}^{(i)}_{k|k})^{T}]\mu_{k}^{i}
           \end{align*}
+          Using the vector $\mu_{k}$ computed at the previous step we mix all of the predictions computed by the filters to get 
+          the outputs. This last step is only for the sake of the output, the algorithm forms a loop without it.
 \end{itemize}
 \section*{Consensus}
-    Right having computed the IMM's estimate for every ON sensor, we use a consensus algorithm to try to lower the 
+Right after having computed the IMM's estimate for every ON sensor, we use a consensus algorithm to try to lower the
 estimation error even more. The consensus will happen at a variable rate and only between the ON sensors.
@@
 \begin{align*}
-        &P_{cons}(k)=(H^{k^{T}}P^{k^{-1}}H^{k})^{-1}\\
-        &x_{cons}(k)=P_{cons}H^{k^{T}}P^{k^{-1}}Z^{k}
+     & P_{cons}(k)=(H^{k^{T}}P^{k^{-1}}H^{k})^{-1}  \\
+     & x_{cons}(k)=P_{cons}H^{k^{T}}P^{k^{-1}}Z^{k}
 \end{align*}
@@
 It has to be noted that the WLS can be seen as 2 parallel linear consensus algorithms, running one on top of the other.
+The consensus is computed both on the output of the IMM filter and all the outputs of its internal Kalman filters.
 \\
@@
 was abandoned, instead we just computed the mean between the various $\mu_{k}$.
-    \section*{Result}
-    The performance evaluation of the system are evaluted by computing the RMS of the predicted trajectory eith the respect to the actual one
-    choosing different rate of performind the WSL. The final result are listed in the table below
+\newpage
+\section*{Results}
+Here we present the results of our implementation of the algorithm and sensors. The agent was left wandering inside the set virtual room 
+and measured at each timestep the estimation error that the algorithm gave. The room is set to be a square with a $100m$ side with a $10\times 10$ 
+grid of sensors with range$=10$. 
+\\
+The simulations were performed in a loop according to the Montecarlo's Method. We set a number of iterations for any specific case to 
+$n_{monte}=100$ and each iteration stop wheter the agent leaves the room limits or a number of timesteps $n_{k}=1000$ is reached. The starting
+ position and starting model are randomized at each iteration.
+The performance indexes that we evaluated are:
+\begin{itemize}
+    \item The Root Mean Square of the means of the errors at each Montecarlo's iteration
+    \item The Root Mean Square of the maximum error at every Montecarlo's iteration
+    \item The Maximum error between all Montecarlo's iterations
+\end{itemize}
+We evaluated both model sets $\mathbbm{M}_{1}$ and $\mathbbm{M}_{2}$ for different consensus rate (how many timestep between each consensus), 
+different $R$s and $Q$s and we considered both the errors given by the Consensus and by each individual sensor's IMM. 
+\\
+The timestep $\delta$ is set at $0.05s$, the radius of the wheel $r$ at $0.5m$ while the inputs are
+\begin{align*}
+    u_{1}=\begin{bmatrix}
+        5\frac{m}{s^{2}} \\5\frac{m}{s^{2}}
+    \end{bmatrix}\ \ \ \ 
+    u_{2}=\begin{bmatrix}
+        3\frac{rad}{s^{2}} \\6\frac{rad}{s}
+    \end{bmatrix}
+\end{align*}
+The power spectral density matrices considered are $R1=diag(0.1,(\frac{2\pi}{180})^{2})$ and $R2=diag(0.01,(\frac{2\pi}{360})^{2})$ for all the sensors, 
+and while $Q2=diag(1,1)$ is shared by $\mathbbm{M}_{1}$ and $\mathbbm{M}_{2}$, $Q1=diag(0.2,0.2)$ for $\mathbbm{M}_{2}$ and $Q1=diag(0.1,0.1)$ for $\mathbbm{M}_{1}$.
+\\
+The first case is $\mathbbm{M}_{1}$, the second $\mathbbm{M}_{2}$. Here are reported all the results of the simulations, all in meters.
+%%%%%%%%%%%% SENSOR %%%%%%%%%%%%%%%%%%%
+
 \begin{center}
+    \resizebox{.99 \columnwidth}{!}{ $
             \begin{tabular}{ |c||c|c|c|  }
                 \hline
-            \multicolumn{4}{|c|}{consensus20} \\
+                \multicolumn{4}{|c|}{Sensor}                 \\
                 \hline
-            IMM  & Mean of Imm's mean    & Max of Imm's mean     & max of IMM's max  \\ [0.5ex]
+                Measure & RMS of Means & RMS of Maxes & Max of Maxes \\ [0.5ex]
+                \hline
+                R1,Q1   & 0.3985        & 1.2407       & 1.7790      \\
+                \hline
+                % R1,Q2           & 0.1132                &  0.2847           & 0.6577                      \\
+                % \hline
+                R2,Q1   & 0.1574        & 0.5454       & 0.7139      \\
+                % \hline
+                % R2,Q2           & 0.0539                & 0.1454             & 0.2334                   \\
+                \hline
+            \end{tabular} $}
+\end{center}
+This table is needed to compare the simulations results, because the power spectral density matrices $R$ regard the polar coordinates, while here
+ we have the errors in cartesian. If the algorithm gives an error greater in all cases than what is given by the sensors, 
+then it is useless.
+
+\begin{center}
+    \resizebox{.99 \columnwidth}{!}{ $
+            \begin{tabular}{ |c||c|c|c|  }
+                \hline
+                \multicolumn{4}{|c|}{case 1: consensus rate = 20}      \\
+                \hline
+                Consensus & RMS of Means & RMS of Maxes & Max of Maxes \\ [0.5ex]
                 \hline
@@
                 \hline
-            \multicolumn{4}{|c|}{consensus20} \\
+                \multicolumn{4}{|c|}{}                                 \\
                 \hline
-            W/o Cons  & Mean of Imm's mean    & Max of Imm's mean     & max of IMM's max  \\ 
+                Individual IMM  & RMS of Means & RMS of Maxes & Max of Maxes \\
                 \hline
@@
                 \hline
-           \end{tabular}
+            \end{tabular} $}
 \end{center}
 
-    \subsection*{}
+%%%%%%% rate 10 %%%%%
+
+\begin{center}
+    \resizebox{.99 \columnwidth}{!}{ $
+            \begin{tabular}{ |c||c|c|c|  }
+                \hline
+                \multicolumn{4}{|c|}{case 1: consensus rate = 10}      \\
+                \hline
+                Consensus & RMS of Means & RMS of Maxes & Max of Maxes \\ [0.5ex]
+                \hline
+                R1,Q1     & 0.1110        & 0.2831       & 0.4460      \\
+                \hline
+                R1,Q2     & 0.1129        & 0.2940       & 0.5227      \\
+                \hline
+                R2,Q1     & 0.0516        & 0.1406       & 0.2226      \\
+                \hline
+                R2,Q2     & 0.0519        & 0.1331       & 0.2429      \\
+                \hline
+                \multicolumn{4}{|c|}{}                                 \\
+                \hline
+                Individual IMM  & RMS of Means & RMS of Maxes & Max of Maxes \\
+                \hline
+                R1,Q1     & 0.1455        & 0.1678       & 0.9         \\
+                \hline
+                R1,Q2     & 0.1478        & 0.1926       & 1.5835      \\
+                \hline
+                R2,Q1     & 0.0751        & 0.0853       & 0.4441      \\
+                \hline
+                R2,Q2     & 0.0756        & 0.0824       & 0.4522      \\
+                \hline
+            \end{tabular} $}
+\end{center}
+
+%%%%%%% rate 5 %%%%%
+\begin{center}
+    \resizebox{.99 \columnwidth}{!}{ $
+            \begin{tabular}{ |c||c|c|c|  }
+                \hline
+                \multicolumn{4}{|c|}{case 1: consensus rate = 5}       \\
+                \hline
+                Consensus & RMS of Means & RMS of Maxes & Max of Maxes \\ [0.5ex]
+                \hline
+                R1,Q1     & 0.1158        & 0.3516       & 1.2838      \\
+                \hline
+                R1,Q2     & 0.1192        & 0.3245       & 0.5018      \\
+                \hline
+                R2,Q1     & 0.0553        & 0.1649       & 0.3532      \\
+                \hline
+                R2,Q2     & 0.0542        & 0.1649       & 0.2246      \\
+                \hline
+                \multicolumn{4}{|c|}{}                                 \\
+                \hline
+                Individual IMM  & RMS of Means & RMS of Maxes & Max of Maxes \\
+                \hline
+                R1,Q1     & 0.1302        & 0.2460       & 1.808       \\
+                \hline
+                R1,Q2     & 0.1359        & 0.1700       & 1.7787      \\
+                \hline
+                R2,Q1     & 0.0666        & 0.0762       & 0.762       \\
+                \hline
+                R2,Q2     & 0.0661        & 0.0738       & 0.4450      \\
+                \hline
+            \end{tabular} $}
+\end{center}
+
+%%%%%%% rate 2 %%%%%
+\begin{center}
+    \resizebox{.99 \columnwidth}{!}{ $
+            \begin{tabular}{ |c||c|c|c|  }
+                \hline
+                \multicolumn{4}{|c|}{case 1: consensus rate = 2}       \\
+                \hline
+                Consensus & RMS of Means & RMS of Maxes & Max of Maxes \\ [0.5ex]
+                \hline
+                R1,Q1     & 0.1158        & 0.3516       & 1.2838      \\
+                \hline
+                % R1,Q2           & 0.1094                & 0.2694             & 0.4671                      \\
+                % \hline
+                R2,Q1     & 0.0598        & 0.1925       & 0.2654      \\
+                % \hline
+                % R2,Q2           & 0.0514                & 0.1313             & 0.2549                   \\
+                \hline
+                \multicolumn{4}{|c|}{}                                 \\
+                \hline
+                Individual IMM  & RMS of Means & RMS of Maxes & Max of Maxes \\
+                \hline
+                R1,Q1     & 0.1320        & 0.2460       & 1.808       \\
+                \hline
+                % R1,Q2           & 0.1625                & 0.1907             & 1.0347                     \\
+                % \hline
+                R2,Q1     & 0.0617        & 0.0741       & 0.4368      \\
+                % \hline
+                % R2,Q2           & 0.0815                & 0.0926            & 0.4445                   \\
+                \hline
+            \end{tabular} $}
+\end{center}
+
+%%%%%%% rate 1 %%%%%
+\begin{center}
+    \resizebox{.99 \columnwidth}{!}{ $
+            \begin{tabular}{ |c||c|c|c|  }
+                \hline
+                \multicolumn{4}{|c|}{case 1: consensus rate = 1}       \\
+                \hline
+                Consensus & RMS of Means & RMS of Maxes & Max of Maxes \\ [0.5ex]
+                \hline
+                R1,Q1     & 0.4265        & 1.6287       & 4.5672      \\
+                \hline
+                % R1,Q2         & 0.0757                & 0.204             & 0.2612                        \\
+                % \hline
+                R2,Q1     & 0.0757        & 0.204        & 0.2612      \\
+                % \hline
+                % R2,Q2           & 0.0514                & 0.1313             & 0.2549                   \\
+                \hline
+                \multicolumn{4}{|c|}{}                                 \\
+                \hline
+                Individual IMM  & RMS of Means & RMS of Maxes & Max of Maxes \\
+                \hline
+                R1,Q1     & 0.3755        & 0.8706       & 5.9070      \\
+                % \hline
+                % R1,Q2           & 0.1625                & 0.1907             & 1.0347                     \\
+                \hline
+                R2,Q1     & 0.0766        & 0.1128       & 0.4872      \\
+                % \hline
+                % R2,Q2           & 0.0815                & 0.0926            & 0.4445                   \\
+                \hline
+            \end{tabular} $}
+\end{center}
+
+%%%%%%% no cons %%%%%
+\begin{center}
+    \resizebox{.99 \columnwidth}{!}{ $
+            \begin{tabular}{ |c||c|c|c|  }
+                \hline
+                \multicolumn{4}{|c|}{case 1: consensus rate = 2}      \\
+                \hline
+                Individual IMM & RMS of Means & RMS of Maxes & Max of Maxes \\
+                \hline
+                R1,Q1    & 0.1790        & 0.2278       & 1.7442      \\
+                \hline
+                R1,Q2    & 0.1800        & 0.2782       & 6.4459      \\
+                \hline
+                R2,Q1    & 0.3961        & 0.0930       & 0.0850      \\
+                \hline
+                R2,Q2    & 0.0864        & 0.0973       & 0.7242      \\
+                \hline
+            \end{tabular} $}
+\end{center}
+
+%%%%%%%%%%%%%%%%%%%%%% 20 %%%%%%%%%%%%%%%%%
+\begin{center}
+    \resizebox{.99 \columnwidth}{!}{ $
+            \begin{tabular}{ |c||c|c|c|  }
+                \hline
+                \multicolumn{4}{|c|}{case 2: consensus rate = 20}      \\
+                \hline
+                Consensus & RMS of Means & RMS of Maxes & Max of Maxes \\ [0.5ex]
+                \hline
+                R1,Q1     & 0.1167        & 0.3027       & 0.7750      \\
+                \hline
+                R1,Q2     & 0.1132        & 0.2847       & 0.6577      \\
+                \hline
+                R2,Q1     & 0.0512        & 0.1325       & 0.2315      \\
+                \hline
+                R2,Q2     & 0.0539        & 0.1454       & 0.2334      \\
+                \hline
+                \multicolumn{4}{|c|}{}                                 \\
+                \hline
+                Individual IMM  & RMS of Means & RMS of Maxes & Max of Maxes \\
+                \hline
+                R1,Q1     & 0.0771        & 0.0903       & 0.4918      \\
+                \hline
+                R1,Q2     & 0.1664        & 0.2726       & 1.0990      \\
+                \hline
+                R2,Q1     & 0.0771        & 0.0903       & 0.4918      \\
+                \hline
+                R2,Q2     & 0.0804        & 0.0947       & 0.4190      \\
+                \hline
+            \end{tabular} $}
+\end{center}
+
+%%%%%%%%%%%%%%%%% 10 %%%%%%%%%%%%%%%%%
+\begin{center}
+    \resizebox{.99 \columnwidth}{!}{ $
+            \begin{tabular}{ |c||c|c|c|  }
+                \hline
+                \multicolumn{4}{|c|}{case 2: consensus rate = 10}      \\
+                \hline
+                Consensus & RMS of Means & RMS of Maxes & Max of Maxes \\ [0.5ex]
+                \hline
+                R1,Q1     & 0.1228        & 0.3438       & 0.5992      \\
+                \hline
+                R1,Q2     & 0.1214        & 0.3291       & 0.7441      \\
+                \hline
+                R2,Q1     & 0.0535        & 0.1536       & 0.2525      \\
+                \hline
+                R2,Q2     & 0.0539        & 0.1439       & 0.2396      \\
+                \hline
+                \multicolumn{4}{|c|}{}                                 \\
+                \hline
+                Individual IMM  & RMS of Means & RMS of Maxes & Max of Maxes \\
+                \hline
+                R1,Q1     & 0.1566        & 0.1938       & 0.8766      \\
+                \hline
+                R1,Q2     & 0.1577        & 0.2278       & 1.4168      \\
+                \hline
+                R2,Q1     & 0.0742        & 0.0906       & 0.3968      \\
+                \hline
+                R2,Q2     & 0.0759        & 0.0935       & 0.4782      \\
+                \hline
+            \end{tabular} $}
+\end{center}
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%% 555555 %%%%%%%%%%%%%%%%
+\begin{center}
+    \resizebox{.99 \columnwidth}{!}{ $
+            \begin{tabular}{ |c||c|c|c|  }
+                \hline
+                \multicolumn{4}{|c|}{case 2: consensus rate = 5}       \\
+                \hline
+                Consensus & RMS of Means & RMS of Maxes & Max of Maxes \\ [0.5ex]
+                \hline
+                R1,Q1     & 0.1984        & 0.7467       & 2.3522      \\
+                \hline
+                R1,Q2     & 0.1925        & 0.5871       & 2.2983      \\
+                \hline
+                R2,Q1     & 0.0604        & 0.1829       & 0.4389      \\
+                \hline
+                R2,Q2     & 0.0628        & 0.1873       & 0.2912      \\
+                \hline
+                \multicolumn{4}{|c|}{}                                 \\
+                \hline
+                Individual IMM  & RMS of Means & RMS of Maxes & Max of Maxes \\
+                \hline
+                R1,Q1     & 0.2135        & 0.7295       & 2.4394      \\
+                \hline
+                R1,Q2     & 0.2116        & 0.5412       & 2.7371      \\
+                \hline
+                R2,Q1     & 0.0722        & 0.1012       & 0.4599      \\
+                \hline
+                R2,Q2     & 0.0742        & 0.1077       & 0.5699      \\
+                \hline
+            \end{tabular} $}
+\end{center}
+
+%%%%%%%%%%%%%%%%%%%%%%%%%       2          %%%%%%%%%%%%%%%%%%%%
+
+\begin{center}
+    \resizebox{.99 \columnwidth}{!}{ $
+            \begin{tabular}{ |c||c|c|c|  }
+                \hline
+                \multicolumn{4}{|c|}{case 2: consensus rate = 2}       \\
+                \hline
+                Consensus & RMS of Means & RMS of Maxes & Max of Maxes \\ [0.5ex]
+                \hline
+                R1,Q1     & 0.6709        & 3.2770       & 8.4954      \\
+                \hline
+                % R1,Q2           & 0.1132                &  0.2847           & 0.6577                      \\
+                % \hline
+                R2,Q1     & 0.1392        & 0.6907       & 2.0562      \\
+                % \hline
+                % R2,Q2           & 0.0539                & 0.1454             & 0.2334                   \\
+                \hline
+                \multicolumn{4}{|c|}{}                                 \\
+                \hline
+                Individual IMM  & RMS of Means & RMS of Maxes & Max of Maxes \\
+                \hline
+                R1,Q1     & 0.07629       & 2.5799       & 9.3296      \\
+                % \hline
+                % R1,Q2        & 0.1664                & 0.2726                & 1.0990              \\
+                \hline
+                R2,Q1     & 0.1585        & 0.5868       & 2.1211      \\
+                %     \hline
+                %     R2,Q2           & 0.0804                & 0.0947            & 0.4190                   \\
+                % \hline
+            \end{tabular} $}
+\end{center}
+
+%%%%%%%%%%%%%%%%%%%% 1 1 1 %%%%%%%%%%%%%%%%%%%%%%%%%
+
+\begin{center}
+    \resizebox{.99 \columnwidth}{!}{ $
+    \begin{tabular}{ |c||c|c|c|  }
+        \hline
+        \multicolumn{4}{|c|}{case 2: consensus rate = 1} \\
+        \hline
+        Consensus & RMS of Means & RMS of Maxes & Max of Maxes \\  [0.5ex]
+        \hline
+        R1,Q1    &      1.3654 & 5.5341 & 16.2066             \\
+            \hline
+             R2,Q1            & 0.3883                & 2.3273               & 5.1490                      \\
+             \hline
+        %     R2,Q1            & 0.0512                & 0.1325             & 0.2315                      \\
+        %     \hline
+        %     R2,Q2           & 0.0539                & 0.1454             & 0.2334                   \\
+        % \hline
+        \multicolumn{4}{|c|}{} \\
+        \hline
+        Individual IMM & RMS of Means & RMS of Maxes & Max of Maxes \\ 
+        \hline
+        R1,Q1      & 1.4520 & 5.6335 & 16.4740          \\
+         \hline
+        % R1,Q2        & 0.1664                & 0.2726                & 1.0990              \\
+        % \hline
+         R2,Q1         & 0.3867                & 1.3242             & 5.3175                         \\
+        \hline
+        % R2,Q2           & 0.0804                & 0.0947            & 0.4190                   \\
+    \hline
+       \end{tabular} $}
+    \end{center}
+
+%%%%% NO cons %%%%%%%%%%%%%%%%
+
+\begin{center}
+    \resizebox{.99 \columnwidth}{!}{ $
+            \begin{tabular}{ |c||c|c|c|  }
+                \hline
+                \multicolumn{4}{|c|}{case 2: no consensus}                             \\
+                \hline
+                Individual IMM & RMS of Means & RMS of Maxes & Max of Maxes \\
+                \hline
+                R1,Q1    & 0.1784        & 0.2516       & 1.5541      \\
+                \hline
+                R1,Q2    & 0.1795        & 0.2145       & 0.9872      \\
+                \hline
+                R2,Q1    & 0.0845        & 0.0962       & 0.6888      \\
+                \hline
+                R2,Q2    & 0.0843        & 0.1090       & 0.9289      \\
+                \hline
+            \end{tabular} $}
+\end{center}
+
+What we gather from these tables is that, specifically in the case of the unicycle $\mathbbm{M}_{2}$ (that is a more complex model set), 
+a consensus computed at a high frequency (rate=1, rate=2) gives disastrous results with any magnitude of noise. This is probably caused by 
+the nature of the IMM algorithm that gets impeded by the consensus which homogenizes the internal Kalman filters input to a point which 
+the IMM can't compute their probabilities efficiently. In fact we see a much better results with lower frequency such as rate=10 and rate=20.
+We also tried the case in which we do not compute any consensus and we let individual sensors work alone and, while we see good results, 
+it doesn't seem to be the best compromise.
+\\
+In the case of the Random Walk with a rate=2 we have good results with low $R$, but the algorithm is really sensible to changes to this 
+parameter and performs really bad with $R1$.
+\\
+While we see that with both model sets the case with rate=20 gives very good results, but we also notice that the maximum of both the individual 
+IMMs and of the consensus can get pretty high so if we have an application where the frequency of estimation must be high and we can't 
+have a big overshoot, then this rate can fail.
+All things considered the best compromise may be the rate=10, which always gives good results and has double the frequency of rate=20.
+\\
+Following are some graphs of the best and worst cases computed by the simulations. More graphs and a video of the algorithm working can 
+be found at ...
 

### 2020-02-02 Latex/draft.tex
Onlyimages missing

@@
 \begin{itemize}
-    \item ON: at each time-step checks if it is still in range with the function inRange(), takes a measurement, computes the IMM algorithm and
-          at a tunable rate computes the consensus with the other nearby ON sensors. If it's not in range anymore then turns IDLE.
-    \item IDLE : checks if it is now in range with the function inRange(), if it is then initialize itself with the data from nearby sensors
+    \item ON: at each time-step checks if the agents is still in range with the function inRange(), takes a measurement, computes the IMM algorithm and
+          at a tunable rate computes the consensus with the other nearby ON sensors. If the agent is not in range anymore then turns IDLE.
+    \item IDLE : checks if the agent is now in range with the function inRange(), if it is then initialize itself with the data from nearby sensors
           that are ON. If it recieves a CantSense signal, it checks if at least one of its neighboors is still ON, else it turns OFF itself.
@@
 Whenever the target is in range of a sensor at given timestep, the device takes a measurement.
-The model choosen for our sensor is a Radar, and as such the non-linear measurement function
+The model chosen for our sensor is that of a radar, and as such the non-linear measurement function
 associated to it is the cartesian to polar transformation at timestep $k$, as shown below
@@
 where $h(x)$ is the polar to cartesian cordinates transform that takes in $x(k)$ that is the state (of which the first 2 elements are the cartesian
-cordinates relative to the sensor), $z(k)$ is the measure and $v(k)$ is the noise associated to the measurement's operation. The measurement noise $w(k)$ is associated
+cordinates relative to the sensor), $z(k)$ is the measure and $v(k)$ is the noise associated to the measurement's operation. The measurement noise $v(k)$ is associated
 to a diagonal power spectral density matrix $R$.
@@
 of models that we denote as $\mathbbm{M}$. We will consider 2 families of such sets that we will call: Random Accelerated Walk $\mathbbm{M}_{1}$
-and Random Unicycle Turning $\mathbbm{M}_{2}$. Every element of said families is a discrete Markovian process, as all are influenced by a white
+and Random Unicycle Turning $\mathbbm{M}_{2}$. Every element of said families is a discrete Markovian process, as all are influenced by
 noise on their inputs.
@@
 \end{center}
-
 Every member of the set has the same structure
 to describe their dynamics, in state space this their shared linear model
-\begin{equation}
+\begin{equation*}
     x(k+1)= Ax(k) + B(s_{k})u + Gw(k)
-\end{equation}
+\end{equation*}
 where $A$ is the state matrix, $B(s_{k})$ the input matrix function of the mode/index $s_{k}$ that indicates the element picked of $\mathbbm{M}_{1}$ at timestep $k$,
@@
 Being the agent's dynamic costantly switching between the models in the set chosen, a single Kalman filter won't give us acceptable results while
-tracking and we have to rely on the Interacting Multiple Models algorithm (IMM). In essence the algorithm let various estimation filters work in parallel
-(EKF in our case), and outputs a mixture of the filters' estimate based on the probability of each of the models used in the filter to be correct.
+tracking and we have to rely on the Interacting Multiple Models algorithm (IMM).
+In essence the algorithm let various estimation filters work in parallel, and outputs a mixture of the filters' estimate based on the probability of each of the models used in the filter to be correct.
 \\
@@
 \\
-Following is a short recapof the algorithm, to see it in much more detail refer to %\cite%
+Following is a short recap of the algorithm, to see it in much more detail refer to CITA QUA
 \\
@@
            \\
-           In this step a lower bound on the likelihood is implemented since a likelihood vector of $0$ breaks the algorithm.
+           In this step two adjustment are needed: the first one is the choice to use a logaritmic pdf instead of a normal one due 
+           to the fact that it gives better numerical results and lower bound on the likelihood is implemented since a likelihood 
+           vector of $0$ breaks the algorithm.
     \item Estimate fusion
@@
           Using the vector $\mu_{k}$ computed at the previous step we mix all of the predictions computed by the filters to get 
-          the outputs. This last step is only for the sake of the output, the algorithm forms a loop without it.
+          the outputs. This last step is only for the sake of the output, the algorithm forms a loop without it as the starting step of 
+          the next iteration uses the outputs of the filters at the steps before this one.
 \end{itemize}
@@
 The consensus is computed both on the output of the IMM filter and all the outputs of its internal Kalman filters. 
+The same WLS algorithm is used to initialize IDLE sensors that turn ON using data from nearby ON sensors.
 \\
@@
 was abandoned, instead we just computed the mean between the various $\mu_{k}$.
-\newpage
 \section*{Results}
-Here we present the results of our implementation of the algorithm and sensors. The agent was left wandering inside the set virtual room 
-and measured at each timestep the estimation error that the algorithm gave. The room is set to be a square with a $100m$ side with a $10\times 10$ 
-grid of sensors with range$=10$. 
+Here we present the results of our implementation of the algorithm and sensors' grid. The agent was left wandering inside the set virtual room 
+and at each timestep the estimation error of the algorithm was measured. The room is set to be a square with a $100m$ side with a $10\times 10$ 
+grid of sensors with range$=10m$. 
 \\
@@
 We evaluated both model sets $\mathbbm{M}_{1}$ and $\mathbbm{M}_{2}$ for different consensus rate (how many timestep between each consensus), 
-different $R$s and $Q$s and we considered both the errors given by the Consensus and by each individual sensor's IMM. 
+different $R$ and $Q$ and we considered both the errors given by the Consensus and by each individual sensor's IMM. We've also run simulations 
+with noconsensus at all.
 \\
@@
 The power spectral density matrices considered are $R1=diag(0.1,(\frac{2\pi}{180})^{2})$ and $R2=diag(0.01,(\frac{2\pi}{360})^{2})$ for all the sensors, 
-and while $Q2=diag(1,1)$ is shared by $\mathbbm{M}_{1}$ and $\mathbbm{M}_{2}$, $Q1=diag(0.2,0.2)$ for $\mathbbm{M}_{2}$ and $Q1=diag(0.1,0.1)$ for $\mathbbm{M}_{1}$.
+and while $Q2=diag(1,1)$ is shared by $\mathbbm{M}_{1}$ and $\mathbbm{M}_{2}$, $Q1=diag(0.2,0.2)$ for $\mathbbm{M}_{2}$ and $Q1=diag(0.1,0.1)$ for 
+$\mathbbm{M}_{1}$. The Transition matrices were initializated as follows
+\begin{align*}
+    &T_{1}=\begin{bmatrix}
+        0.6&0.1&0.1&0.1&0.1\\
+        0.2&0.5&0.12&0.06&0.06\\
+        0.2&0.12&0.5&0.12&0.06\\
+        0.2&0.06&0.12&0.5&0.12\\
+        0.2&0.12&0.06&0.12&0.5\\
+    \end{bmatrix}\\
+    &T_{2}=\begin{bmatrix}
+        0.8&0.05&0.05&0.05&0.05\\
+        0.25&0.5&0.25&0&0\\
+        0.25&0.25&0.5&0&0\\
+        0.25&0&0&0.5&0.25\\
+        0.25&0&0&0.25&0.5\\
+    \end{bmatrix}
+\end{align*}
 \\
@@
 have a big overshoot, then this rate can fail.
-All things considered the best compromise may be the rate=10, which always gives good results and has double the frequency of rate=20.
+All things considered the best trade-off may be the rate=10, which always gives good results and has double the frequency of rate=20.
 \\

### 2020-02-02 Progetto2.m

@@ -98,10 +98,6 @@ switch caso
         Transmat(4,:)=[q 0 0 q1 q];
         Transmat(5,:)=[q 0 0 q q1];
         %initial 2D position, velocity and acceleration
-        x0=zeros(nx,1);
-        x0([1,2])=[-1;-1]+2.*rand(2,1);
-        x0(3)=0.3;
-        x0(4)=pi/3;
         %radius, called like this for reasons
         ABG=0.5;
         %Power spectra density of process noise

### 2020-02-02 Progetto2.m
Cancelled all unused functions

@@ -9,11 +9,11 @@ caso=2;
 %delta time
 delta=0.05;
 %at which rate do we do the consensus ?
-rate=10000;
+rate=10;
 %Maximum number of iteration
-nstop=1000;
+nstop=10;
 %iterations montecarlo
-nmonte=100;
+nmonte=1;
 %Plot
 videon = 0;
 ploton =0;

### 2020-02-02 Latex/draft.tex

@@
 \usepackage{bookmark}
-\usepackage{natbib}
+%\usepackage{natbib}
 \usepackage{geometry}
@@
 \begin{center}
-    \begin{tabular}{||c||c |c |}%{|width=\columnwidth|}
+    \begin{tabular}{||c||c|c|}%{|width=\columnwidth|}
         \hline
@@
 \\
-Following is a short recap of the algorithm, to see it in much more detail refer to CITA QUA
+Following is a short recap of the algorithm, to see it in much more detail refer to \textit{Interacting Multiple Model Methods in Target Tracking}  \cite{bar-shalomInteractingMultipleModel}
 \\
@@
                 %     R2,Q2           & 0.0804                & 0.0947            & 0.4190                   \\
-                % \hline
+                 \hline
             \end{tabular} $}
@@
 What we gather from these tables is that, specifically in the case of the unicycle $\mathbbm{M}_{2}$ (that is a more complex model set), 
-a consensus computed at a high frequency (rate=1, rate=2) gives disastrous results with any magnitude of noise. This is probably caused by 
-the nature of the IMM algorithm that gets impeded by the consensus which homogenizes the internal Kalman filters input to a point which 
+a consensus computed at a high frequency (rate=1, rate=2) gives disastrous results with any magnitude of noise.
+This is probably caused by the nature of the IMM algorithm that gets impeded by the consensus which homogenizes the internal Kalman filters input to a point which 
 the IMM can't compute their probabilities efficiently. In fact we see a much better results with lower frequency such as rate=10 and rate=20.
@@
 \\
+\begin{figure}[h!]
+    \centering
+    \includegraphics[width=0.50\textwidth]{Immagini/RMSIMMC2_20R2Q1.png}
+    \caption{Case 1 at rate 1 : R2Q1}
+    \label{fig:number}
+\end{figure}
+\begin{figure}[h!]
+    \centering
+    \includegraphics[width=0.50\textwidth]{Immagini/maxIMMC2_20R2Q1.png}
+    \caption{Case 1 at rate 1 : Maximum with R2Q1}
+    \label{fig:number}
+\end{figure}
+\begin{figure}[h!]
+    \centering
+    \includegraphics[width=0.50\textwidth]{Immagini/RMSIMMC2_1R1Q1.png}
+    \caption{Case 2 at rate 1 : R1Q1}
+    \label{fig:number}
+\end{figure}
+\begin{figure}[h!]
+    \centering
+    \includegraphics[width=0.50\textwidth]{Immagini/maxIMMC2_1R2Q1.png}
+    \caption{Case 2 at rate 1 : Maximum with R2Q1}
+    \label{fig:number}
+\end{figure}
+\begin{figure}[h!]
+    \centering
+    \includegraphics[width=0.50\textwidth]{Immagini/RMSIMMC2_10R2Q1.png}
+    \caption{Case 2 at rate 10 : R2Q1}
+    \label{fig:number}
+\end{figure}
+\begin{figure}[h!]
+    \centering
+    \includegraphics[width=0.50\textwidth]{Immagini/RMSnoconsC2R1Q2.png}
+    \caption{Case 2 no consensus : R2Q1}
+    \label{fig:number}
+\end{figure}
+\begin{figure}[h!]
+    \centering
+    \includegraphics[width=0.50\textwidth]{Immagini/RMSIMMC1_10R2Q1.png}
+    \caption{Case 1 at rate 10 : R2Q1}
+    \label{fig:number}
+\end{figure}
+\begin{figure}[h!]
+    \centering
+    \includegraphics[width=0.50\textwidth]{Immagini/IndvErroC1_10R2Q1.png}
+    \caption{Case 1 at rate 10 : Individual Error R2Q1}
+    \label{fig:number}
+\end{figure}
+\begin{figure}[h!]
+    \centering
+    \includegraphics[width=0.50\textwidth]{Immagini/RMSnoconsC1R2Q1.png}
+    \caption{Case 1 no consensus : R2Q1}
+    \label{fig:number}
+\end{figure}
+\begin{figure}[h!]
+    \centering
+    \includegraphics[width=0.50\textwidth]{Immagini/Trajectory.png}
+    \caption{A Typical Trajectory}
+    \label{fig:number}
+\end{figure}
+
 Following are some graphs of the best and worst cases computed by the simulations. More graphs and a video of the algorithm working can 
-be found at ...
+be found at \href{https://github.com/PaioPaio/IMM-Sensors-Network/tree/no_speed_jumps/Graphs}{the project's GitHub}
 
+\bibliography{bib} 
+\bibliographystyle{ieeetr}
 \end{document}

### 2020-02-03 Progetto2.m
Movie in right section
Ho solo spostato qualche video nella cartella Graph

@@ -7,13 +7,13 @@ clc; clear all; close all;
 
 caso=2;
 %delta time
-delta=0.9;
+delta=0.05;
 %at which rate do we do the consensus ?
 rate=10;
 %Maximum number of iteration
-nstop=200;
+nstop=1000;
 %iterations montecarlo
-nmonte=1;
+nmonte=100;
 %Plot
 videon = 0;
 ploton =0;
